---
title: "Recoding DigIQ Items"
output: html_document
date: "2025-03-12"
---

```{r setup, include=FALSE}

read.csv <- ("DigIQ2r1_mockdataset.csv")

```


# Recoding Skills items

```{r Skill items recode, include=FALSE}

###Making numeric variables

df <- df |>
  mutate(SInfo1N = as.numeric(SInfo1),
         SInfo3_V2N = as.numeric(SInfo3_V2),
         SInfo4N = as.numeric(SInfo4),
         SInfo5N = as.numeric(SInfo5),
         SInfo6N = as.numeric(SInfo6),
         SInfo7N = as.numeric(SInfo7),
         SCom1_V2N = as.numeric(SCom1_V2),
         SCom2N = as.numeric(SCom2),
         SCom3N = as.numeric(SCom3),
         SCom4_V2N = as.numeric(SCom4_V2),
         SCom5N = as.numeric(SCom5),
         SCrea2N = as.numeric(SCrea2),
         SCrea3N = as.numeric(SCrea3),
         SCrea4N = as.numeric(SCrea4),
         SCrea5N = as.numeric(SCrea5),
         SSafDev1N = as.numeric(SSafDev1),
         SSafDev2N = as.numeric(SSafDev2),
         SPriv1N = as.numeric(SPriv1),
         SPriv2N = as.numeric(SPriv2),
         SPriv3N = as.numeric(SPriv3),
         SPriv4N = as.numeric(SPriv4),
         SHealth1N = as.numeric(SHealth1),
         SHealth2_V2N = as.numeric(SHealth2_V2),
         SHealth3_V2N = as.numeric(SHealth3_V2),
         SEnv1N = as.numeric(SEnv1),
         SEnv2N = as.numeric(SEnv2),
         SEnv3N = as.numeric(SEnv3),
         SProbl1N = as.numeric(SProbl1),
         SProbl2N = as.numeric(SProbl2),
         Strans1N = as.numeric(Strans1),
         Strans2N = as.numeric(Strans2),
         Strans3N = as.numeric(Strans3),
         Strans4N = as.numeric(Strans4),
         Strans5N = as.numeric(Strans5),
         SAI1N = as.numeric(SAI1),
         SAI2N = as.numeric(SAI2),
         SGAI1N = as.numeric(SGAI1),
         SGAI2N = as.numeric(SGAI2),
         SGAI3N = as.numeric(SGAI3))

###Recoding the variables so that 'don't know' and 'don't want to answer' are set as missing.
df <- df |> 
    mutate(across(c("GetHelp_V2N", "SInfo1N", "SInfo3_V2N", "SInfo4N", "SInfo5N", "SInfo6N", "SInfo7N", "SCom1_V2N", "SCom2N", "SCom3N", "SCom4_V2N", "SCom5N", "SCrea2N", "SCrea3N", "SCrea4N", "SCrea5N", "SSafDev1N", "SSafDev2N", "SPriv1N", "SPriv2N", "SPriv3N", "SPriv4N", "SHealth1N", "SHealth2_V2N", "SHealth3_V2N", "SEnv1N", "SEnv2N", "SEnv3N", "SProbl1N", "SProbl2N", "Strans1N", "Strans2N", "Strans3N", "Strans4N", "Strans5N", "SAI1N", "SAI2N", "SGAI1N", "SGAI2N", "SGAI3N"), ~ replace(., . == 66 | . == 99, NA)))

```


# Recoding Knowledge items

The knowledge questions need to be recoded into correct and incorrect.
We recode all knowledge items into new factors with R the end with
levels correct, incorrect, don't know, and don't understand.

```{r recode knowledge items, echo=FALSE, comment=NA, message=FALSE}
#Recoding function for TRUE items
recode_values_true <- function(x) {
  recode_factor(as.factor(x),
                '1' = "Correct",
                '2' = "Incorrect",
                '3' = "Don't know",
                '66' = "Don't understand")
}

#applying the function
df <- df |>
  mutate(across(c(KInfo3, KCom1, KCrea1, KCrea2, KSafDev2, KSafDev_new, KPriv2, KPriv3_V2, KHealth2, KHealth3, KEnv1, KEnv2, Ktrans1, KAI1, KAI3, KAI4, KGAI3, KGAI4, KGAI5), recode_values_true, .names = "{.col}R"))

#Recoding function for FALSE items
recode_values_false <- function(x) {
  recode_factor(as.factor(x),
                '1' = "Incorrect",
                '2' = "Correct",
                '3' = "Don't know",
                '66' = "Don't understand")
}

#applying the function
df <- df |>
  mutate(across(c(KInfo1, KInfo2, KCom3, KCrea3, KPriv1, KHealth1, KEnv3, Ktrans2, Ktrans3, KAI2, KGAI1, KGAI2), recode_values_false, .names = "{.col}R"))

##We also create numeric versions, with RC at the end, in which correct = 1, and incorrect, don't know, and don't understand =0. !!! NA doesn't work this way!! So added this as an extra line!

#Creating numeric versions of the knowledge items
## The code below automatically adds 'RC' to the names of the new variables
df <- df |>
  mutate(across(
    c(KInfo1R, KInfo2R, KInfo3R, KCom1R, KCom3R, KCrea1R, KCrea2R, KCrea3R,
      KSafDev2R, KPriv1R, KPriv2R, KPriv3_V2R, KHealth1R, KHealth2R, 
      KHealth3R, KEnv1R, KEnv2R, KEnv3R, Ktrans1R, Ktrans2R, Ktrans3R,  KAI1R, KAI2R, KAI3R, KAI4R, KGAI1R, KGAI2R, KGAI3R, KGAI4R, KGAI5R),
    ~ as.numeric(ifelse(. == "Correct", 1, 0)),
    .names = "{.col}C"
  ))


```

# Combining subscales

Creating the subscales for the different dimensions (as variables in 'df'):
- MeanStratInfo
- MeanCritInfo
- MeanNet
- MeanCrea
- MeanSaf
- MeanHealth
- MeanGreen
- MeanTrans
- MeanProbl
- MeanAI
- MeangenAI

Calculating the total knowledge score (no splitting for dimensions):
- MeanKnowledge


```{r creating subscales, echo=FALSE}

##First make means for all skill scores

StratInfo=data.frame(df$SInfo1N, df$SInfo3_V2N, df$SInfo4N)
df$MeanStratInfo <-rowMeans(StratInfo)

CritInfo=data.frame(df$SInfo5N, df$SInfo6N, df$SInfo7N)
df$MeanCritInfo <-rowMeans(CritInfo)

Net=data.frame(df$SCom1_V2N, df$SCom2N, df$SCom4_V2N, df$SCom5N)
df$MeanNet <-rowMeans(Net)

Crea=data.frame(df$SCrea2N, df$SCrea3N, df$SCrea4N, df$SCrea5N)
df$MeanCrea <-rowMeans(Crea)

Saf=data.frame(df$SSafDev1N, df$SSafDev2N ,df$SPriv1N, df$SPriv2N, df$SPriv3N, df$SPriv4N, df$SCom3N)
df$MeanSaf <-rowMeans(Saf)

Health=data.frame(df$SHealth1N, df$SHealth2_V2N, df$SHealth3_V2N)
df$MeanHealth <-rowMeans(Health)

Green=data.frame(df$SEnv1N, df$SEnv2N, df$SEnv3N)
df$MeanGreen <-rowMeans(Green)

Trans=data.frame(df$Strans1N, df$Strans2N, df$Strans3N, df$Strans4N, df$Strans5N)
df$MeanTrans <- rowMeans(Trans)

Probl=data.frame(df$SProbl1N, df$SProbl2N)
df$MeanProbl <-rowMeans(Probl)

AI=data.frame(df$SAI1N, df$SAI2N)
df$MeanAI <-rowMeans(AI)

genAI=data.frame(df$SGAI1N, df$SGAI2N, df$SGAI3N)
df$MeangenAI <-rowMeans(genAI)

#Make knowledge score
df$MeanKnowledge <- (df$KInfo1RC + df$KInfo2RC+ df$KInfo3RC 
                     + df$KCom1RC  +  df$KCom3RC 
                     + df$KCrea1RC  + df$KCrea2RC  +  df$KCrea3RC  
                     + df$KSafDev2RC 
                     + df$KPriv1RC  + df$KPriv2RC  + df$KPriv3_V2RC 
                     + df$KHealth1RC  + df$KHealth2RC  + df$KHealth3RC 
                     + df$KEnv1RC  + df$KEnv2RC + df$KEnv3RC 
                     + df$Ktrans1RC + df$Ktrans2RC + df$Ktrans3RC
                     + df$KAI1RC  + df$KAI2RC  + df$KAI3RC  
                     + df$KGAI1RC + df$KGAI2RC + df$KGAI3RC + df$KGAI4RC + df$KGAI5RC)





```

## Calculating (weighted) mean scores

```{r weighted means}


#Look at weighted and unweighted means for each subskill
###Weighted mean Strat Info
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanStratInfoW = survey_mean(MeanStratInfo, na.rm = TRUE))
###Unweighted mean Strat Info
mean(df$MeanStratInfo, na.rm = TRUE)

###Weighted mean CritInfo
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanCritInfoW= survey_mean(MeanCritInfo, na.rm = TRUE))
###Unweighted mean CritINnfo
mean(df$MeanCritInfo, na.rm = TRUE)

###Weighted mean Netiquette
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanNetW = survey_mean(MeanNet, na.rm = TRUE))
###Unweighted mean Netiquette
mean(df$MeanNet, na.rm = TRUE)

###Weighted mean Crea
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanCreaW = survey_mean(MeanCrea, na.rm = TRUE))
###Unweighted mean Crea
mean(df$MeanCrea, na.rm = TRUE)

###Weighted mean Safety
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanSafW = survey_mean(MeanSaf, na.rm = TRUE))
###Unweighted mean Safety
mean(df$MeanSaf, na.rm = TRUE)

###Weighted mean Health
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanHealthW = survey_mean(MeanHealth, na.rm = TRUE))
###Unweighted mean Health
mean(df$MeanHealth, na.rm = TRUE)

###Weighted mean Green
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanGreenW = survey_mean(MeanGreen, na.rm = TRUE))
###Unweighted mean Green
mean(df$MeanGreen, na.rm = TRUE)

###Weighted mean Transactional
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanProblW = survey_mean(MeanTrans, na.rm = TRUE))
###Unweighted mean Problem
mean(df$MeanTrans, na.rm = TRUE)

###Weighted mean problem
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanProblW = survey_mean(MeanProbl, na.rm = TRUE))
###Unweighted mean Problem
mean(df$MeanProbl, na.rm = TRUE)

###Weighted mean AI
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanAIW = survey_mean(MeanAI, na.rm = TRUE))
###Unweighted mean AI
mean(df$MeanAI, na.rm = TRUE)

###Weighted mean genAI
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(MeanAIW = survey_mean(MeangenAI, na.rm = TRUE))
###Unweighted mean AI
mean(df$MeangenAI, na.rm = TRUE)

###Weighted mean knowledge
df |>
  as_survey(weights = c(weging_GAMO_R)) |>
  summarize(meanKnowledgeW = survey_mean(MeanKnowledge, na.rm = TRUE))
###Unweighted mean knowledge
mean(df$MeanKnowledge, na.rm = TRUE)



```

