---
title: "{{< iconify ph lightbulb-fill >}} Digital Problem Solving"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

**Digital Problem Solving** skills involve knowing where to find help with digital challenges and understanding how to improve digital competencies.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```

## {{< iconify ph lightning-fill >}} Problem Solving Skills


ADD TEXT BEFORE TABSET


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dprob-wave1-overall-2}
# Digital Problem Solving Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SProbl1, SProbl2),
  title = "Digital Problem Solving Skills",
  questions = c("SProbl1", "SProbl2"),
  question_labels = c("I know where or from whom I can get help to improve my digital skills", "I know where or from whom I can get help if I'm unable to do something on the internet"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-age-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-age-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-gender-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-gender-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-edu-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-edu-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-mig-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-mig-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dprob-wave2-overall-2}
# Digital Problem Solving Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SProbl1, SProbl2),
  title = "Digital Problem Solving Skills",
  questions = c("SProbl1", "SProbl2"),
  question_labels = c("I know where or from whom I can get help to improve my digital skills", "I know where or from whom I can get help if I'm unable to do something on the internet"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-age-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-age-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-gender-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-gender-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-edu-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-edu-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-mig-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-mig-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl2"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-overall-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-overall-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SProbl2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-age-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-age-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-gender-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-gender-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-edu-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-edu-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-mig-item1-2}
# I know where or from whom I can get help to improve my digital skills
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-mig-item2-2}
# I know where or from whom I can get help if I'm unable to do something on the internet
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph clipboard-text >}} Problem Solving Performance


ADD TEXT BEFORE TABSET


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-ps-wave1-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SourceHelp_1, SourceHelp_2, SourceHelp_3, SourceHelp_4, SourceHelp_5, SourceHelp_6, SourceHelp_7, SourceHelp_8, SourceHelp_9),
  title = "",
  questions = c("SourceHelp_1", "SourceHelp_2", "SourceHelp_3", "SourceHelp_4", "SourceHelp_5", "SourceHelp_6", "SourceHelp_7", "SourceHelp_8", "SourceHelp_9"),
  question_labels = c("I don't need help", "I don't know anyone", "Family", "Friends", "Colleagues/classmates", "Neighbors/acquaintances", "Help desk", "Library", "Telecom/online helpdesk"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave1-age-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave1-age-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave1-age-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave1-age-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave1-age-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave1-age-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave1-age-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave1-age-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave1-age-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave1-gender-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave1-gender-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave1-gender-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave1-gender-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave1-gender-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave1-gender-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave1-gender-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave1-gender-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave1-gender-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave1-edu-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave1-edu-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave1-edu-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave1-edu-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave1-edu-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave1-edu-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave1-edu-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave1-edu-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave1-edu-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave1-mig-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave1-mig-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave1-mig-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave1-mig-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave1-mig-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave1-mig-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave1-mig-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave1-mig-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave1-mig-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_9"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-ps-wave2-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SourceHelp_1, SourceHelp_2, SourceHelp_3, SourceHelp_4, SourceHelp_5, SourceHelp_6, SourceHelp_7, SourceHelp_8, SourceHelp_9),
  title = "",
  questions = c("SourceHelp_1", "SourceHelp_2", "SourceHelp_3", "SourceHelp_4", "SourceHelp_5", "SourceHelp_6", "SourceHelp_7", "SourceHelp_8", "SourceHelp_9"),
  question_labels = c("I don't need help", "I don't know anyone", "Family", "Friends", "Colleagues/classmates", "Neighbors/acquaintances", "Help desk", "Library", "Telecom/online helpdesk"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave2-age-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave2-age-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave2-age-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave2-age-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave2-age-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave2-age-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave2-age-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave2-age-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave2-age-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave2-gender-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave2-gender-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave2-gender-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave2-gender-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave2-gender-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave2-gender-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave2-gender-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave2-gender-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave2-gender-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave2-edu-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave2-edu-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave2-edu-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave2-edu-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave2-edu-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave2-edu-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave2-edu-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave2-edu-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave2-edu-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave2-mig-item1-2}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave2-mig-item2-2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave2-mig-item3-2}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave2-mig-item4-2}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave2-mig-item5-2}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave2-mig-item6-2}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave2-mig-item7-2}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave2-mig-item8-2}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-wave2-mig-item9-2}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SourceHelp_9"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-overall-item1-2}
# I don't need help
result <- create_timeline(
  data = data,
  title = "I don't need help",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-overall-item2-2}
# I don't know anyone
result <- create_timeline(
  data = data,
  title = "I don't know anyone",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-overall-item3-2}
# Family
result <- create_timeline(
  data = data,
  title = "Family",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-overall-item4-2}
# Friends
result <- create_timeline(
  data = data,
  title = "Friends",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-overall-item5-2}
# Colleagues/classmates
result <- create_timeline(
  data = data,
  title = "Colleagues/classmates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-overall-item6-2}
# Neighbors/acquaintances
result <- create_timeline(
  data = data,
  title = "Neighbors/acquaintances",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-overall-item7-2}
# Help desk
result <- create_timeline(
  data = data,
  title = "Help desk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-overall-item8-2}
# Library
result <- create_timeline(
  data = data,
  title = "Library",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-overtime-overall-item9-2}
# Telecom/online helpdesk
result <- create_timeline(
  data = data,
  title = "Telecom/online helpdesk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-age-item1-2}
# I don't need help
result <- create_timeline(
  data = data,
  title = "I don't need help",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-age-item2-2}
# I don't know anyone
result <- create_timeline(
  data = data,
  title = "I don't know anyone",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-age-item3-2}
# Family
result <- create_timeline(
  data = data,
  title = "Family",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-age-item4-2}
# Friends
result <- create_timeline(
  data = data,
  title = "Friends",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-age-item5-2}
# Colleagues/classmates
result <- create_timeline(
  data = data,
  title = "Colleagues/classmates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-age-item6-2}
# Neighbors/acquaintances
result <- create_timeline(
  data = data,
  title = "Neighbors/acquaintances",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-age-item7-2}
# Help desk
result <- create_timeline(
  data = data,
  title = "Help desk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-age-item8-2}
# Library
result <- create_timeline(
  data = data,
  title = "Library",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-overtime-age-item9-2}
# Telecom/online helpdesk
result <- create_timeline(
  data = data,
  title = "Telecom/online helpdesk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-gender-item1-2}
# I don't need help
result <- create_timeline(
  data = data,
  title = "I don't need help",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-gender-item2-2}
# I don't know anyone
result <- create_timeline(
  data = data,
  title = "I don't know anyone",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-gender-item3-2}
# Family
result <- create_timeline(
  data = data,
  title = "Family",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-gender-item4-2}
# Friends
result <- create_timeline(
  data = data,
  title = "Friends",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-gender-item5-2}
# Colleagues/classmates
result <- create_timeline(
  data = data,
  title = "Colleagues/classmates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-gender-item6-2}
# Neighbors/acquaintances
result <- create_timeline(
  data = data,
  title = "Neighbors/acquaintances",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-gender-item7-2}
# Help desk
result <- create_timeline(
  data = data,
  title = "Help desk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-gender-item8-2}
# Library
result <- create_timeline(
  data = data,
  title = "Library",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-overtime-gender-item9-2}
# Telecom/online helpdesk
result <- create_timeline(
  data = data,
  title = "Telecom/online helpdesk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-edu-item1-2}
# I don't need help
result <- create_timeline(
  data = data,
  title = "I don't need help",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-edu-item2-2}
# I don't know anyone
result <- create_timeline(
  data = data,
  title = "I don't know anyone",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-edu-item3-2}
# Family
result <- create_timeline(
  data = data,
  title = "Family",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-edu-item4-2}
# Friends
result <- create_timeline(
  data = data,
  title = "Friends",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-edu-item5-2}
# Colleagues/classmates
result <- create_timeline(
  data = data,
  title = "Colleagues/classmates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-edu-item6-2}
# Neighbors/acquaintances
result <- create_timeline(
  data = data,
  title = "Neighbors/acquaintances",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-edu-item7-2}
# Help desk
result <- create_timeline(
  data = data,
  title = "Help desk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-edu-item8-2}
# Library
result <- create_timeline(
  data = data,
  title = "Library",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-overtime-edu-item9-2}
# Telecom/online helpdesk
result <- create_timeline(
  data = data,
  title = "Telecom/online helpdesk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-mig-item1-2}
# I don't need help
result <- create_timeline(
  data = data,
  title = "I don't need help",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-mig-item2-2}
# I don't know anyone
result <- create_timeline(
  data = data,
  title = "I don't know anyone",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-mig-item3-2}
# Family
result <- create_timeline(
  data = data,
  title = "Family",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-mig-item4-2}
# Friends
result <- create_timeline(
  data = data,
  title = "Friends",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-mig-item5-2}
# Colleagues/classmates
result <- create_timeline(
  data = data,
  title = "Colleagues/classmates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-mig-item6-2}
# Neighbors/acquaintances
result <- create_timeline(
  data = data,
  title = "Neighbors/acquaintances",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-mig-item7-2}
# Help desk
result <- create_timeline(
  data = data,
  title = "Help desk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-mig-item8-2}
# Library
result <- create_timeline(
  data = data,
  title = "Library",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-ps-overtime-mig-item9-2}
# Telecom/online helpdesk
result <- create_timeline(
  data = data,
  title = "Telecom/online helpdesk",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

