---
title: "{{< iconify ph star-fill >}} Highlights"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

<div style='text-align: justify;'>
### Wave 1 Key Findings
Here are the key findings from Wave 1 of the Digital Competence study.

1. {{< iconify ph device-mobile-camera-fill >}} **People generally feel digitally skilled, and this largely corresponds with their knowledge, but not always with their performance.**
   For some skills, such as online health and well-being, or netiquette, there are discrepancies between people's high scores on trust in their own skills and low scores on performance and behavior.
   These findings may indicate that Dutch people have blind spots regarding (some) digital skills and are unaware of what is possible online and where they actually lack skills.

2. {{< iconify ph sparkles-fill >}} **Skills and knowledge in the field of (gen)AI are low.**
   Children, the elderly, and low-educated Dutch people score low on knowledge about the privacy, validity, and reliability of genAI and the personalization of news and entertainment by AI, and are not well-equipped to create prompts that leverage the benefits of genAI.
   People perform poorly in recognizing and using genAI, and, aside from social media, don't always know which apps or websites use AI to tailor content to them.

3. {{< iconify ph users-three-fill >}} **Differences among Dutch people can be distinguished based on age and education level, not on migration background.**
   Children (10<U+2013>14 years old), the elderly (66+), and the less educated score lower on digital skills and knowledge.
</div>

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

```

