---
title: "{{< iconify ph book-open-fill >}} Knowledge"
format: html
---


```{=html}
<script>document.body.classList.add('has-pagination-top');</script>
<nav class='pagination-nav pagination-top' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <span class='pagination-prefix'>Page </span>
      <input type='number' class='pagination-input' id='page-input-top' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'> / 3</span>
    </div>
    <a href='knowledge_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["knowledge.html","knowledge_p2.html","knowledge_p3.html"];
  const pageInput = document.getElementById('page-input-top');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```



```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Knowledge** section measures what participants *know* about the digital world: how it works, what risks it involves, and how different technologies affect everyday life. These items test factual understanding across topics such as information reliability, communication and privacy, online safety, AI, and generative AI. Respondents indicate whether each statement is true or false (or if they don’t know), allowing us to assess their level of digital literacy and awareness beyond self-perceived skills.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph magnifying-glass >}} Strategic Information


**Strategic Information Skills** assess the ability to effectively search for and locate information online. This includes choosing good keywords, using search functions, and finding answers to questions on the internet.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don't know, please choose 'I don't know'. You don't have to guess. If you don't understand the question, please choose 'I don't understand the question.' Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```
[{{< iconify ph cards >}} See all Strategic Information results](strategic_information.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r kinfo-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KInfo1RC, KInfo2RC),
  title = "",
  questions = c("KInfo1RC", "KInfo2RC"),
  question_labels = c("The first search result is always the best information source. (False Statement)", "Everyone gets the same information when they search for the same things online. (False Statement)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave1-age-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave1-age-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KInfo2RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave1-gender-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave1-gender-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KInfo2RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave1-edu-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave1-edu-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KInfo2RC"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave1-mig-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave1-mig-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KInfo2RC"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r kinfo-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KInfo1RC, KInfo2RC),
  title = "",
  questions = c("KInfo1RC", "KInfo2RC"),
  question_labels = c("The first search result is always the best information source. (False Statement)", "Everyone gets the same information when they search for the same things online. (False Statement)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave2-age-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave2-age-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KInfo2RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave2-gender-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave2-gender-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KInfo2RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave2-edu-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave2-edu-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KInfo2RC"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-wave2-mig-item1}
# The first search result is always the best information source. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, KInfo1RC),
  title = "The first search result is always the best information source. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-wave2-mig-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KInfo2RC"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-overtime-overall-item1}
# The first search result is always the best information source. (False Statement)
result <- create_timeline(
  data = data,
  title = "The first search result is always the best information source. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-overtime-overall-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_timeline(
  data = data,
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-overtime-age-item1}
# The first search result is always the best information source. (False Statement)
result <- create_timeline(
  data = data,
  title = "The first search result is always the best information source. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-overtime-age-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_timeline(
  data = data,
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-overtime-gender-item1}
# The first search result is always the best information source. (False Statement)
result <- create_timeline(
  data = data,
  title = "The first search result is always the best information source. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-overtime-gender-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_timeline(
  data = data,
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-overtime-edu-item1}
# The first search result is always the best information source. (False Statement)
result <- create_timeline(
  data = data,
  title = "The first search result is always the best information source. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-overtime-edu-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_timeline(
  data = data,
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r kinfo-overtime-mig-item1}
# The first search result is always the best information source. (False Statement)
result <- create_timeline(
  data = data,
  title = "The first search result is always the best information source. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r kinfo-overtime-mig-item2}
# Everyone gets the same information when they search for the same things online. (False Statement)
result <- create_timeline(
  data = data,
  title = "Everyone gets the same information when they search for the same things online. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph detective-fill >}} Critical Information


**Critical Information Skills** measure the ability to evaluate online information: checking whether information is true, assessing website reliability, and understanding the purpose of online content (to inform, influence, entertain, or sell).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don't know, please choose 'I don't know'. You don't have to guess. If you don't understand the question, please choose 'I don't understand the question.' Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```
[{{< iconify ph cards >}} See all Critical Information results](critical_information.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r critinfo-wave1-overall}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  questions = "KInfo3RC",
  question_labels = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r critinfo-wave1-age}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KInfo3RC"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r critinfo-wave1-gender}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KInfo3RC"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r critinfo-wave1-edu}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KInfo3RC"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r critinfo-wave1-mig}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KInfo3RC"
)

result
```


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r critinfo-wave2-overall}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  questions = "KInfo3RC",
  question_labels = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r critinfo-wave2-age}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KInfo3RC"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r critinfo-wave2-gender}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KInfo3RC"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r critinfo-wave2-edu}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KInfo3RC"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r critinfo-wave2-mig}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KInfo3RC"
)

result
```


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r critinfo-overtime-overall}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r critinfo-overtime-age}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC",
  group_var = "AgeGroup"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r critinfo-overtime-gender}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC",
  group_var = "geslacht"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r critinfo-overtime-edu}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC",
  group_var = "Education"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r critinfo-overtime-mig}
# Some people make money by spreading fake news on the internet. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "Some people make money by spreading fake news on the internet. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC",
  group_var = "MigrationBackground"
)

result
```


:::


:::

## {{< iconify ph chats-fill >}} Netiquette


**Netiquette** refers to proper online communication etiquette: knowing when to ask permission before sharing, choosing the right communication tool, understanding what not to share online, and using emoticons appropriately.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don't know, please choose 'I don't know'. You don't have to guess. If you don't understand the question, please choose 'I don't understand the question.' Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```
[{{< iconify ph cards >}} See all Netiquette results](netiquette.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r knet-wave1-overall}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  questions = "KCom3RC",
  question_labels = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r knet-wave1-age}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r knet-wave1-gender}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r knet-wave1-edu}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r knet-wave1-mig}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KCom3RC"
)

result
```


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r knet-wave2-overall}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  questions = "KCom3RC",
  question_labels = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r knet-wave2-age}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r knet-wave2-gender}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r knet-wave2-edu}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r knet-wave2-mig}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KCom3RC"
)

result
```


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r knet-overtime-overall}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KCom3RC"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r knet-overtime-age}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "AgeGroup"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r knet-overtime-gender}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "geslacht"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r knet-overtime-edu}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "Education"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r knet-overtime-mig}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "MigrationBackground"
)

result
```


:::


:::



```{=html}
<nav class='pagination-nav pagination-bottom' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <span class='pagination-prefix'></span>
      <input type='number' class='pagination-input' id='page-input-bottom' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'> / 3</span>
    </div>
    <a href='knowledge_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["knowledge.html","knowledge_p2.html","knowledge_p3.html"];
  const pageInput = document.getElementById('page-input-bottom');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```

