---
title: "{{< iconify ph chats-fill >}} Netiquette"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

**Netiquette Competence** refers to proper online communication etiquette: knowing when to ask permission before sharing, choosing the right communication tool, understanding what not to share online, and using emoticons appropriately.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```

## {{< iconify ph lightning-fill >}} Netiquette Skills


**Skills** measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Skills results](skills.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r nskills-wave1-overall-2}
# Netiquette Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Netiquette Skills",
  questions = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  question_labels = c("I know when I should ask for permission to share something online", "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)", "I know which things I should not share online", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-age-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-age-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-age-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-age-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-gender-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-gender-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-gender-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-gender-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-edu-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-edu-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-edu-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-edu-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-mig-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-mig-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-mig-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-mig-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r nskills-wave2-overall-2}
# Netiquette Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Netiquette Skills",
  questions = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  question_labels = c("I know when I should ask for permission to share something online", "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)", "I know which things I should not share online", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-age-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-age-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-age-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-age-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-gender-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-gender-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-gender-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-gender-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-edu-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-edu-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-edu-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-edu-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-mig-item1-2}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-mig-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-mig-item3-2}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-mig-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom5"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-overall-item1-2}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-overall-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-overall-item3-2}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-overall-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-age-item1-2}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-age-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-age-item3-2}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-age-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-gender-item1-2}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-gender-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-gender-item3-2}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-gender-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-edu-item1-2}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-edu-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-edu-item3-2}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-edu-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-mig-item1-2}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-mig-item2-2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-mig-item3-2}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-mig-item4-2}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph book-open-fill >}} Netiquette Knowledge


**Knowledge** measures what participants *know* about the digital world. These items test factual understanding by having respondents indicate whether statements are true or false.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don't know, please choose 'I don't know'. You don't have to guess. If you don't understand the question, please choose 'I don't understand the question.' Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```
[{{< iconify ph cards >}} See all Knowledge results](knowledge.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r knet-wave1-overall-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  questions = "KCom3RC",
  question_labels = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r knet-wave1-age-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r knet-wave1-gender-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r knet-wave1-edu-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r knet-wave1-mig-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KCom3RC"
)

result
```


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r knet-wave2-overall-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  questions = "KCom3RC",
  question_labels = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r knet-wave2-age-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r knet-wave2-gender-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r knet-wave2-edu-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KCom3RC"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r knet-wave2-mig-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KCom3RC"
)

result
```


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r knet-overtime-overall-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KCom3RC"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r knet-overtime-age-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "AgeGroup"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r knet-overtime-gender-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "geslacht"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r knet-overtime-edu-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "Education"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r knet-overtime-mig-2}
# Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)
result <- create_timeline(
  data = data,
  title = "Negative comments hurt people less when you say them online than when you say them to their face. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "MigrationBackground"
)

result
```


:::


:::

