---
title: "{{< iconify ph clipboard-text >}} Performance"
format: html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(4, 6, "performance", "top")
```



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
dashboardr::.page_config(accessibility = TRUE, modals = TRUE, crosstab_prefix = "performance")
```

The **Performance** section measures participants' practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information, recognizing AI-generated images, protecting their devices, or using AI tools effectively. The items cover eleven areas of digital competence, from strategic and critical information skills to AI and generative AI skills, providing an overall picture of how well individuals can navigate today's digital environment.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::create_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph heart-fill >}} Digital Health


**Digital Health & Wellbeing** skills relate to managing healthy digital habits.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Do you sometimes try to limit the time you spend using digital media in one of the following ways? Select every answer that applies.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-health-wave1-overall}
# 
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  x_vars = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7", "PDHWS1_8"),
  x_var_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach", "None of these actions"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-age-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-age-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-age-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-age-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-age-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-age-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-age-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-age-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-gender-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-gender-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-gender-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-gender-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-gender-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-gender-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-gender-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-gender-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-edu-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-edu-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-edu-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-edu-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-edu-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-edu-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-edu-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-edu-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-mig-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-mig-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-mig-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-mig-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-mig-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-mig-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-mig-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-mig-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_8"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-health-wave2-overall}
# 
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  x_vars = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7", "PDHWS1_8"),
  x_var_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach", "None of these actions"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-age-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-age-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-age-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-age-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-age-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-age-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-age-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-age-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-gender-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-gender-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-gender-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-gender-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-gender-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-gender-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-gender-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-gender-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-edu-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-edu-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-edu-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-edu-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-edu-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-edu-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-edu-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-edu-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-mig-item1}
# Create digital detox moments
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-mig-item2}
# Have rules limiting digital media
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-mig-item3}
# Use screen-time limiter
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-mig-item4}
# Temporarily switch off Internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-mig-item5}
# Delete apps/programs
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-mig-item6}
# Turn off notifications
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-mig-item7}
# Reduce time without special approach
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-mig-item8}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_8"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-overall-item1}
# Create digital detox moments
result <- viz_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-overall-item2}
# Have rules limiting digital media
result <- viz_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-overall-item3}
# Use screen-time limiter
result <- viz_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-overall-item4}
# Temporarily switch off Internet
result <- viz_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-overall-item5}
# Delete apps/programs
result <- viz_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-overall-item6}
# Turn off notifications
result <- viz_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-overall-item7}
# Reduce time without special approach
result <- viz_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-overall-item8}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-age-item1}
# Create digital detox moments
result <- viz_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-age-item2}
# Have rules limiting digital media
result <- viz_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-age-item3}
# Use screen-time limiter
result <- viz_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-age-item4}
# Temporarily switch off Internet
result <- viz_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-age-item5}
# Delete apps/programs
result <- viz_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-age-item6}
# Turn off notifications
result <- viz_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-age-item7}
# Reduce time without special approach
result <- viz_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-age-item8}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_8",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-gender-item1}
# Create digital detox moments
result <- viz_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-gender-item2}
# Have rules limiting digital media
result <- viz_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-gender-item3}
# Use screen-time limiter
result <- viz_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-gender-item4}
# Temporarily switch off Internet
result <- viz_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-gender-item5}
# Delete apps/programs
result <- viz_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-gender-item6}
# Turn off notifications
result <- viz_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-gender-item7}
# Reduce time without special approach
result <- viz_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-gender-item8}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_8",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-edu-item1}
# Create digital detox moments
result <- viz_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-edu-item2}
# Have rules limiting digital media
result <- viz_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-edu-item3}
# Use screen-time limiter
result <- viz_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-edu-item4}
# Temporarily switch off Internet
result <- viz_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-edu-item5}
# Delete apps/programs
result <- viz_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-edu-item6}
# Turn off notifications
result <- viz_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-edu-item7}
# Reduce time without special approach
result <- viz_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-edu-item8}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_8",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-mig-item1}
# Create digital detox moments
result <- viz_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-mig-item2}
# Have rules limiting digital media
result <- viz_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-mig-item3}
# Use screen-time limiter
result <- viz_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-mig-item4}
# Temporarily switch off Internet
result <- viz_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-mig-item5}
# Delete apps/programs
result <- viz_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-mig-item6}
# Turn off notifications
result <- viz_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-mig-item7}
# Reduce time without special approach
result <- viz_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_7",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-mig-item8}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PDHWS1_8",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph recycle-fill >}} Green Digital


**Sustainable/Green Digital Competence** focuses on environmentally conscious technology use: reducing energy consumption, buying sustainable devices, recycling electronics, and understanding the environmental impact of digital activities.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Which of the following activities do you sometimes do?", preset = "question")
```
[{{< iconify ph cards >}} See all Green Digital results](green_digital.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-green-wave1-overall}
# 
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  x_vars = c("PSGDS1_1", "PSGDS1_2", "PSGDS1_3", "PSGDS1_4", "PSGDS1_5", "PSGDS1_6", "PSGDS1_7", "PSGDS1_8", "PSGDS1_9"),
  x_var_labels = c("Clean mailbox", "Use sustainable search engines", "Avoid unnecessary Cloud storage", "Turn down screen brightness", "Use sleep mode", "Close unused phone apps", "Recycle devices", "Repair before replacing", "None of these actions"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave1-age-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave1-age-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave1-age-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave1-age-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave1-age-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave1-age-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave1-age-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave1-age-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave1-age-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave1-gender-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave1-gender-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave1-gender-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave1-gender-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave1-gender-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave1-gender-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave1-gender-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave1-gender-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave1-gender-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave1-edu-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave1-edu-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave1-edu-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave1-edu-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave1-edu-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave1-edu-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave1-edu-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave1-edu-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave1-edu-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_9"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave1-mig-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave1-mig-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave1-mig-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave1-mig-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave1-mig-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave1-mig-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave1-mig-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave1-mig-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave1-mig-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_9"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-green-wave2-overall}
# 
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  x_vars = c("PSGDS1_1", "PSGDS1_2", "PSGDS1_3", "PSGDS1_4", "PSGDS1_5", "PSGDS1_6", "PSGDS1_7", "PSGDS1_8", "PSGDS1_9"),
  x_var_labels = c("Clean mailbox", "Use sustainable search engines", "Avoid unnecessary Cloud storage", "Turn down screen brightness", "Use sleep mode", "Close unused phone apps", "Recycle devices", "Repair before replacing", "None of these actions"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave2-age-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave2-age-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave2-age-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave2-age-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave2-age-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave2-age-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave2-age-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave2-age-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave2-age-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSGDS1_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave2-gender-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave2-gender-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave2-gender-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave2-gender-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave2-gender-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave2-gender-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave2-gender-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave2-gender-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave2-gender-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSGDS1_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave2-edu-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave2-edu-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave2-edu-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave2-edu-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave2-edu-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave2-edu-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave2-edu-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave2-edu-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave2-edu-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSGDS1_9"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave2-mig-item1}
# Clean mailbox
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave2-mig-item2}
# Use sustainable search engines
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave2-mig-item3}
# Avoid unnecessary Cloud storage
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave2-mig-item4}
# Turn down screen brightness
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave2-mig-item5}
# Use sleep mode
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave2-mig-item6}
# Close unused phone apps
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave2-mig-item7}
# Recycle devices
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave2-mig-item8}
# Repair before replacing
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-wave2-mig-item9}
# None of these actions
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSGDS1_9"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-overall-item1}
# Clean mailbox
result <- viz_timeline(
  data = data,
  title = "Clean mailbox",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-overall-item2}
# Use sustainable search engines
result <- viz_timeline(
  data = data,
  title = "Use sustainable search engines",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-overall-item3}
# Avoid unnecessary Cloud storage
result <- viz_timeline(
  data = data,
  title = "Avoid unnecessary Cloud storage",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-overall-item4}
# Turn down screen brightness
result <- viz_timeline(
  data = data,
  title = "Turn down screen brightness",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-overall-item5}
# Use sleep mode
result <- viz_timeline(
  data = data,
  title = "Use sleep mode",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-overall-item6}
# Close unused phone apps
result <- viz_timeline(
  data = data,
  title = "Close unused phone apps",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-overall-item7}
# Recycle devices
result <- viz_timeline(
  data = data,
  title = "Recycle devices",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-overall-item8}
# Repair before replacing
result <- viz_timeline(
  data = data,
  title = "Repair before replacing",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-overtime-overall-item9}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_9"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-age-item1}
# Clean mailbox
result <- viz_timeline(
  data = data,
  title = "Clean mailbox",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-age-item2}
# Use sustainable search engines
result <- viz_timeline(
  data = data,
  title = "Use sustainable search engines",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-age-item3}
# Avoid unnecessary Cloud storage
result <- viz_timeline(
  data = data,
  title = "Avoid unnecessary Cloud storage",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-age-item4}
# Turn down screen brightness
result <- viz_timeline(
  data = data,
  title = "Turn down screen brightness",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-age-item5}
# Use sleep mode
result <- viz_timeline(
  data = data,
  title = "Use sleep mode",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-age-item6}
# Close unused phone apps
result <- viz_timeline(
  data = data,
  title = "Close unused phone apps",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-age-item7}
# Recycle devices
result <- viz_timeline(
  data = data,
  title = "Recycle devices",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-age-item8}
# Repair before replacing
result <- viz_timeline(
  data = data,
  title = "Repair before replacing",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_8",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-overtime-age-item9}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_9",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-gender-item1}
# Clean mailbox
result <- viz_timeline(
  data = data,
  title = "Clean mailbox",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-gender-item2}
# Use sustainable search engines
result <- viz_timeline(
  data = data,
  title = "Use sustainable search engines",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-gender-item3}
# Avoid unnecessary Cloud storage
result <- viz_timeline(
  data = data,
  title = "Avoid unnecessary Cloud storage",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-gender-item4}
# Turn down screen brightness
result <- viz_timeline(
  data = data,
  title = "Turn down screen brightness",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-gender-item5}
# Use sleep mode
result <- viz_timeline(
  data = data,
  title = "Use sleep mode",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-gender-item6}
# Close unused phone apps
result <- viz_timeline(
  data = data,
  title = "Close unused phone apps",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-gender-item7}
# Recycle devices
result <- viz_timeline(
  data = data,
  title = "Recycle devices",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-gender-item8}
# Repair before replacing
result <- viz_timeline(
  data = data,
  title = "Repair before replacing",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_8",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-overtime-gender-item9}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_9",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-edu-item1}
# Clean mailbox
result <- viz_timeline(
  data = data,
  title = "Clean mailbox",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-edu-item2}
# Use sustainable search engines
result <- viz_timeline(
  data = data,
  title = "Use sustainable search engines",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-edu-item3}
# Avoid unnecessary Cloud storage
result <- viz_timeline(
  data = data,
  title = "Avoid unnecessary Cloud storage",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-edu-item4}
# Turn down screen brightness
result <- viz_timeline(
  data = data,
  title = "Turn down screen brightness",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-edu-item5}
# Use sleep mode
result <- viz_timeline(
  data = data,
  title = "Use sleep mode",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-edu-item6}
# Close unused phone apps
result <- viz_timeline(
  data = data,
  title = "Close unused phone apps",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-edu-item7}
# Recycle devices
result <- viz_timeline(
  data = data,
  title = "Recycle devices",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-edu-item8}
# Repair before replacing
result <- viz_timeline(
  data = data,
  title = "Repair before replacing",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_8",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-overtime-edu-item9}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_9",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-mig-item1}
# Clean mailbox
result <- viz_timeline(
  data = data,
  title = "Clean mailbox",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-mig-item2}
# Use sustainable search engines
result <- viz_timeline(
  data = data,
  title = "Use sustainable search engines",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-mig-item3}
# Avoid unnecessary Cloud storage
result <- viz_timeline(
  data = data,
  title = "Avoid unnecessary Cloud storage",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-mig-item4}
# Turn down screen brightness
result <- viz_timeline(
  data = data,
  title = "Turn down screen brightness",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-mig-item5}
# Use sleep mode
result <- viz_timeline(
  data = data,
  title = "Use sleep mode",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-mig-item6}
# Close unused phone apps
result <- viz_timeline(
  data = data,
  title = "Close unused phone apps",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-mig-item7}
# Recycle devices
result <- viz_timeline(
  data = data,
  title = "Recycle devices",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_7",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-mig-item8}
# Repair before replacing
result <- viz_timeline(
  data = data,
  title = "Repair before replacing",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_8",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-green-overtime-mig-item9}
# None of these actions
result <- viz_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSGDS1_9",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(4, 6, "performance", "bottom")
```

