---
title: "{{< iconify ph clipboard-text >}} Performance"
format: html
---


```{=html}
<script>document.body.classList.add('has-pagination-top');</script>
<nav class='pagination-nav pagination-top' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <a href='performance.html' class='pagination-btn pagination-prev' aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
    <div class='pagination-info'>
      <span class='pagination-prefix'>Page </span>
      <input type='number' class='pagination-input' id='page-input-top' min='1' max='4' value='2' aria-label='Current page'>
      <span class='pagination-separator'> / 4</span>
    </div>
    <a href='performance_p3.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["performance.html","performance_p2.html","performance_p3.html","performance_p4.html"];
  const pageInput = document.getElementById('page-input-top');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```



```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Performance** section measures participants' practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information, recognizing AI-generated images, protecting their devices, or using AI tools effectively. The items cover eleven areas of digital competence, from strategic and critical information skills to AI and generative AI skills, providing an overall picture of how well individuals can navigate today's digital environment.

```{r, echo=FALSE, results='asis'}
dashboardr::enable_modals()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph chats-fill >}} Netiquette


**Netiquette Competence** refers to proper online communication etiquette: knowing when to ask permission before sharing, choosing the right communication tool, understanding what not to share online, and using emoticons appropriately.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Who do you ask for help if you aren’t able to do something with online media or digital technology? (you can choose multiple answers)", preset = "question")
```
[{{< iconify ph cards >}} See all Netiquette results](netiquette.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-netiquette-wave1-overall}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  questions = "PNS1R",
  question_labels = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-netiquette-wave1-age}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PNS1R"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-netiquette-wave1-gender}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PNS1R"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-netiquette-wave1-edu}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PNS1R"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-netiquette-wave1-mig}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PNS1R"
)

result
```


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-netiquette-wave2-overall}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  questions = "PNS1R",
  question_labels = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-netiquette-wave2-age}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PNS1R"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-netiquette-wave2-gender}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PNS1R"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-netiquette-wave2-edu}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PNS1R"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-netiquette-wave2-mig}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PNS1R"
)

result
```


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-netiquette-overtime-overall}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_timeline(
  data = data,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PNS1R"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-netiquette-overtime-age}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_timeline(
  data = data,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PNS1R",
  group_var = "AgeGroup"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-netiquette-overtime-gender}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_timeline(
  data = data,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PNS1R",
  group_var = "geslacht"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-netiquette-overtime-edu}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_timeline(
  data = data,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PNS1R",
  group_var = "Education"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-netiquette-overtime-mig}
# Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)
result <- create_timeline(
  data = data,
  title = "Imagine, you find this picture of your friend/acquaintance on social media. For which picture, or pictures, would you ask permission from this friend/acquaintance to share it with others online? (multiple answers are possible)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PNS1R",
  group_var = "MigrationBackground"
)

result
```


:::


:::

## {{< iconify ph shield-check-fill >}} Safety


**Safety & Control of Information and Devices Competence** encompasses protecting devices and personal information: using security measures, managing privacy settings, identifying phishing, and controlling what information is shared online.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Which of the following safety precautions do you sometimes take for your digital/online media use? Select every answer that applies", preset = "question")
```
[{{< iconify ph cards >}} See all Safety results](safety.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-safety-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9", "PSCS3_10"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper", "Use passwords with ≥14 characters", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups", "None of the above"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-age-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-age-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-age-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-age-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-age-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-age-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-age-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-age-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-age-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-age-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-gender-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-gender-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-gender-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-gender-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-gender-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-gender-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-gender-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-gender-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-gender-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-gender-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-edu-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-edu-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-edu-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-edu-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-edu-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-edu-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-edu-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-edu-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-edu-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-edu-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-mig-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-mig-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-mig-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-mig-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-mig-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-mig-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-mig-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-mig-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-mig-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-mig-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_10"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-safety-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9", "PSCS3_10"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper", "Use passwords with ≥14 characters", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups", "None of the above"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-age-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-age-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-age-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-age-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-age-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-age-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-age-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-age-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-age-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-age-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-gender-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-gender-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-gender-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-gender-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-gender-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-gender-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-gender-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-gender-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-gender-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-gender-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-edu-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-edu-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-edu-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-edu-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-edu-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-edu-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-edu-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-edu-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-edu-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-edu-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-mig-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-mig-item2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-mig-item3}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-mig-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-mig-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-mig-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-mig-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-mig-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-mig-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-mig-item10}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_10"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-overall-item1}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-overall-item2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-overall-item3}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-overall-item4}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-overall-item5}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-overall-item6}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-overall-item7}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-overall-item8}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-overall-item9}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-overall-item10}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-age-item1}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-age-item2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-age-item3}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-age-item4}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-age-item5}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-age-item6}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-age-item7}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-age-item8}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-age-item9}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-age-item10}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-gender-item1}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-gender-item2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-gender-item3}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-gender-item4}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-gender-item5}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-gender-item6}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-gender-item7}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-gender-item8}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-gender-item9}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-gender-item10}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-edu-item1}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-edu-item2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-edu-item3}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-edu-item4}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-edu-item5}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-edu-item6}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-edu-item7}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-edu-item8}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-edu-item9}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-edu-item10}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-mig-item1}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-mig-item2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-mig-item3}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-mig-item4}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-mig-item5}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-mig-item6}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-mig-item7}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-mig-item8}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-mig-item9}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-mig-item10}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph heart-fill >}} Digital Health


**Digital Health & Wellbeing** skills relate to managing healthy digital habits.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Do you sometimes try to limit the time you spend using digital media in one of the following ways? Select every answer that applies.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-health-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7", "PDHWS1_8"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach", "None of these actions"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-age-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-age-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-age-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-age-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-age-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-age-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-age-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-age-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-gender-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-gender-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-gender-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-gender-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-gender-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-gender-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-gender-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-gender-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-edu-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-edu-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-edu-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-edu-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-edu-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-edu-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-edu-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-edu-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-mig-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-mig-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-mig-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-mig-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-mig-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-mig-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-mig-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave1-mig-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_8"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-health-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7", "PDHWS1_8"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach", "None of these actions"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-age-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-age-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-age-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-age-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-age-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-age-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-age-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-age-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-gender-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-gender-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-gender-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-gender-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-gender-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-gender-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-gender-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-gender-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-edu-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-edu-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-edu-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-edu-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-edu-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-edu-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-edu-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-edu-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-mig-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-mig-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-mig-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-mig-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-mig-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-mig-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-mig-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-wave2-mig-item8}
# None of these actions
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of these actions",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PDHWS1_8"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-overall-item1}
# Create digital detox moments
result <- create_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-overall-item2}
# Have rules limiting digital media
result <- create_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-overall-item3}
# Use screen-time limiter
result <- create_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-overall-item4}
# Temporarily switch off Internet
result <- create_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-overall-item5}
# Delete apps/programs
result <- create_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-overall-item6}
# Turn off notifications
result <- create_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-overall-item7}
# Reduce time without special approach
result <- create_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-overall-item8}
# None of these actions
result <- create_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_8"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-age-item1}
# Create digital detox moments
result <- create_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-age-item2}
# Have rules limiting digital media
result <- create_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-age-item3}
# Use screen-time limiter
result <- create_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-age-item4}
# Temporarily switch off Internet
result <- create_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-age-item5}
# Delete apps/programs
result <- create_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-age-item6}
# Turn off notifications
result <- create_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-age-item7}
# Reduce time without special approach
result <- create_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-age-item8}
# None of these actions
result <- create_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_8",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-gender-item1}
# Create digital detox moments
result <- create_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-gender-item2}
# Have rules limiting digital media
result <- create_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-gender-item3}
# Use screen-time limiter
result <- create_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-gender-item4}
# Temporarily switch off Internet
result <- create_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-gender-item5}
# Delete apps/programs
result <- create_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-gender-item6}
# Turn off notifications
result <- create_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-gender-item7}
# Reduce time without special approach
result <- create_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-gender-item8}
# None of these actions
result <- create_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_8",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-edu-item1}
# Create digital detox moments
result <- create_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-edu-item2}
# Have rules limiting digital media
result <- create_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-edu-item3}
# Use screen-time limiter
result <- create_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-edu-item4}
# Temporarily switch off Internet
result <- create_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-edu-item5}
# Delete apps/programs
result <- create_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-edu-item6}
# Turn off notifications
result <- create_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-edu-item7}
# Reduce time without special approach
result <- create_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-edu-item8}
# None of these actions
result <- create_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_8",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-mig-item1}
# Create digital detox moments
result <- create_timeline(
  data = data,
  title = "Create digital detox moments",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-mig-item2}
# Have rules limiting digital media
result <- create_timeline(
  data = data,
  title = "Have rules limiting digital media",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-mig-item3}
# Use screen-time limiter
result <- create_timeline(
  data = data,
  title = "Use screen-time limiter",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-mig-item4}
# Temporarily switch off Internet
result <- create_timeline(
  data = data,
  title = "Temporarily switch off Internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-mig-item5}
# Delete apps/programs
result <- create_timeline(
  data = data,
  title = "Delete apps/programs",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-mig-item6}
# Turn off notifications
result <- create_timeline(
  data = data,
  title = "Turn off notifications",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-mig-item7}
# Reduce time without special approach
result <- create_timeline(
  data = data,
  title = "Reduce time without special approach",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-health-overtime-mig-item8}
# None of these actions
result <- create_timeline(
  data = data,
  title = "None of these actions",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_8",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{=html}
<nav class='pagination-nav pagination-bottom' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <a href='performance.html' class='pagination-btn pagination-prev' aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
    <div class='pagination-info'>
      <span class='pagination-prefix'></span>
      <input type='number' class='pagination-input' id='page-input-bottom' min='1' max='4' value='2' aria-label='Current page'>
      <span class='pagination-separator'> / 4</span>
    </div>
    <a href='performance_p3.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["performance.html","performance_p2.html","performance_p3.html","performance_p4.html"];
  const pageInput = document.getElementById('page-input-bottom');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```

