---
title: "{{< iconify ph clipboard-text >}} Performance"
format: html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(3, 6, "performance", "top")
```



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
dashboardr::.page_config(accessibility = TRUE, modals = TRUE, crosstab_prefix = "performance")
```

The **Performance** section measures participants' practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information, recognizing AI-generated images, protecting their devices, or using AI tools effectively. The items cover eleven areas of digital competence, from strategic and critical information skills to AI and generative AI skills, providing an overall picture of how well individuals can navigate today's digital environment.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::create_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph shield-check-fill >}} Safety


**Safety & Control of Information and Devices Competence** encompasses protecting devices and personal information: using security measures, managing privacy settings, identifying phishing, and controlling what information is shared online.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote('Which of the following safety precautions do you sometimes take for your digital/online media use? Select every answer that applies', preset = 'question')
```
[{{< iconify ph cards >}} See all Safety results](safety.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-safety-wave1-overall}
# 
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  x_vars = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9", "PSCS3_10"),
  x_var_labels = c("Keep passwords in a password safe", "Save passwords on paper", "Use passwords with ≥14 characters", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups", "None of the above"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-age-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-age-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-age-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-age-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-age-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-age-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-age-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-age-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-age-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-age-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-gender-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-gender-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-gender-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-gender-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-gender-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-gender-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-gender-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-gender-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-gender-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-gender-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-edu-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-edu-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-edu-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-edu-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-edu-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-edu-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-edu-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-edu-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-edu-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-edu-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-mig-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-mig-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-mig-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-mig-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-mig-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-mig-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-mig-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-mig-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-mig-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave1-mig-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_10"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-safety-wave2-overall}
# 
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  x_vars = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9", "PSCS3_10"),
  x_var_labels = c("Keep passwords in a password safe", "Save passwords on paper", "Use passwords with ≥14 characters", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups", "None of the above"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-age-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-age-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-age-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-age-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-age-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-age-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-age-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-age-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-age-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-age-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-gender-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-gender-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-gender-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-gender-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-gender-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-gender-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-gender-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-gender-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-gender-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-gender-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-edu-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-edu-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-edu-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-edu-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-edu-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-edu-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-edu-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-edu-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-edu-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-edu-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-mig-item1}
# Keep passwords in a password safe
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-mig-item2}
# Save passwords on paper
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-mig-item3}
# Use passwords with ≥14 characters
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-mig-item4}
# Different passwords per account
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-mig-item5}
# Use passkey (finger/face)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-mig-item6}
# Two-step verification
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-mig-item7}
# Install software updates
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-mig-item8}
# Use adblocker
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-mig-item9}
# Make backups
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-wave2-mig-item10}
# None of the above
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_10"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-overall-item1}
# Keep passwords in a password safe
result <- viz_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-overall-item2}
# Save passwords on paper
result <- viz_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-overall-item3}
# Use passwords with ≥14 characters
result <- viz_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-overall-item4}
# Different passwords per account
result <- viz_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-overall-item5}
# Use passkey (finger/face)
result <- viz_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-overall-item6}
# Two-step verification
result <- viz_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-overall-item7}
# Install software updates
result <- viz_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-overall-item8}
# Use adblocker
result <- viz_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-overall-item9}
# Make backups
result <- viz_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_9"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-overall-item10}
# None of the above
result <- viz_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-age-item1}
# Keep passwords in a password safe
result <- viz_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-age-item2}
# Save passwords on paper
result <- viz_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-age-item3}
# Use passwords with ≥14 characters
result <- viz_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-age-item4}
# Different passwords per account
result <- viz_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-age-item5}
# Use passkey (finger/face)
result <- viz_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-age-item6}
# Two-step verification
result <- viz_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-age-item7}
# Install software updates
result <- viz_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-age-item8}
# Use adblocker
result <- viz_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_8",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-age-item9}
# Make backups
result <- viz_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_9",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-age-item10}
# None of the above
result <- viz_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_10",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-gender-item1}
# Keep passwords in a password safe
result <- viz_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-gender-item2}
# Save passwords on paper
result <- viz_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-gender-item3}
# Use passwords with ≥14 characters
result <- viz_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-gender-item4}
# Different passwords per account
result <- viz_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-gender-item5}
# Use passkey (finger/face)
result <- viz_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-gender-item6}
# Two-step verification
result <- viz_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-gender-item7}
# Install software updates
result <- viz_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-gender-item8}
# Use adblocker
result <- viz_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_8",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-gender-item9}
# Make backups
result <- viz_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_9",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-gender-item10}
# None of the above
result <- viz_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_10",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-edu-item1}
# Keep passwords in a password safe
result <- viz_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-edu-item2}
# Save passwords on paper
result <- viz_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-edu-item3}
# Use passwords with ≥14 characters
result <- viz_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-edu-item4}
# Different passwords per account
result <- viz_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-edu-item5}
# Use passkey (finger/face)
result <- viz_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-edu-item6}
# Two-step verification
result <- viz_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-edu-item7}
# Install software updates
result <- viz_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-edu-item8}
# Use adblocker
result <- viz_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_8",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-edu-item9}
# Make backups
result <- viz_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_9",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-edu-item10}
# None of the above
result <- viz_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_10",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-mig-item1}
# Keep passwords in a password safe
result <- viz_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-mig-item2}
# Save passwords on paper
result <- viz_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-mig-item3}
# Use passwords with ≥14 characters
result <- viz_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-mig-item4}
# Different passwords per account
result <- viz_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-mig-item5}
# Use passkey (finger/face)
result <- viz_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-mig-item6}
# Two-step verification
result <- viz_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-mig-item7}
# Install software updates
result <- viz_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_7",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-mig-item8}
# Use adblocker
result <- viz_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_8",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-mig-item9}
# Make backups
result <- viz_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_9",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 10


```{r perf-safety-overtime-mig-item10}
# None of the above
result <- viz_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS3_10",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph warning-fill >}} Phishing Recognition


**Safety & Control of Information and Devices Competence** encompasses protecting devices and personal information: using security measures, managing privacy settings, identifying phishing, and controlling what information is shared online.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote('<a href=\"#PSCS1R\" class=\"modal-link\">Read the following message</a> closely. What type of message do you think this is?', preset = 'question')
```
[{{< iconify ph cards >}} See all Safety results](safety.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-pscs1-wave1-overall}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Read the following message closely. What type of message do you think this is?",
  x_vars = "PSCS1R",
  x_var_labels = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-pscs1-wave1-age}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS1R"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-pscs1-wave1-gender}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS1R"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-pscs1-wave1-edu}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS1R"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-pscs1-wave1-mig}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS1R"
)

result
```


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-pscs1-wave2-overall}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Read the following message closely. What type of message do you think this is?",
  x_vars = "PSCS1R",
  x_var_labels = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-pscs1-wave2-age}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS1R"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-pscs1-wave2-gender}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS1R"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-pscs1-wave2-edu}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS1R"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-pscs1-wave2-mig}
# Read the following message closely. What type of message do you think this is?
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "Read the following message closely. What type of message do you think this is?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS1R"
)

result
```


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-pscs1-overtime-overall}
# Read the following message closely. What type of message do you think this is?
result <- viz_timeline(
  data = data,
  title = "Read the following message closely. What type of message do you think this is?",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  y_filter_label = "Percentage who selected/answered correctly",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  y_var = "PSCS1R"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-pscs1-overtime-age}
# Read the following message closely. What type of message do you think this is?
result <- viz_timeline(
  data = data,
  title = "Read the following message closely. What type of message do you think this is?",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS1R",
  group_var = "AgeGroup"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-pscs1-overtime-gender}
# Read the following message closely. What type of message do you think this is?
result <- viz_timeline(
  data = data,
  title = "Read the following message closely. What type of message do you think this is?",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS1R",
  group_var = "geslacht"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-pscs1-overtime-edu}
# Read the following message closely. What type of message do you think this is?
result <- viz_timeline(
  data = data,
  title = "Read the following message closely. What type of message do you think this is?",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS1R",
  group_var = "Education"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-pscs1-overtime-mig}
# Read the following message closely. What type of message do you think this is?
result <- viz_timeline(
  data = data,
  title = "Read the following message closely. What type of message do you think this is?",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_filter_label = NULL,
  weight_var = "weging_GAMO",
  y_var = "PSCS1R",
  group_var = "MigrationBackground"
)

result
```


:::


:::



```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(3, 6, "performance", "bottom")
```

