---
title: "{{< iconify ph shield-check-fill >}} Safety"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

**Safety & Control of Information and Devices Competence** encompasses protecting devices and personal information: using security measures, managing privacy settings, identifying phishing, and controlling what information is shared online.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```

## {{< iconify ph lightning-fill >}} Safety Skills


**Skills** measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information.
[{{< iconify ph cards >}} See all Skills results](skills.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r safety-wave1-overall-2}
# Safety and Control of Information and Devices Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Safety and Control of Information and Devices Skills",
  questions = c("SSafDev1", "SSafDev2", "SPriv1", "SPriv2", "SPriv3", "SPriv4", "SCom3"),
  question_labels = c("I know how to protect a device against access (e.g. a PIN code or fingerprint)", "I know how to protect devices against viruses", "I know how to adjust the privacy settings on a mobile phone or tablet", "I know how to change the location settings on a mobile phone or tablet", "I know how to identify suspicious e-mail messages that try to get my personal data", "I know how to delete the history of websites that I have visited before", "I know how to block messages from someone I don't want to hear from"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-age-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-age-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-age-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-age-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-age-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-age-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-age-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-gender-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-gender-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-gender-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-gender-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-gender-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-gender-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-gender-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-edu-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-edu-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-edu-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-edu-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-edu-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-edu-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-edu-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-mig-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-mig-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-mig-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-mig-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-mig-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-mig-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-mig-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom3"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r safety-wave2-overall-2}
# Safety and Control of Information and Devices Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Safety and Control of Information and Devices Skills",
  questions = c("SSafDev1", "SSafDev2", "SPriv1", "SPriv2", "SPriv3", "SPriv4", "SCom3"),
  question_labels = c("I know how to protect a device against access (e.g. a PIN code or fingerprint)", "I know how to protect devices against viruses", "I know how to adjust the privacy settings on a mobile phone or tablet", "I know how to change the location settings on a mobile phone or tablet", "I know how to identify suspicious e-mail messages that try to get my personal data", "I know how to delete the history of websites that I have visited before", "I know how to block messages from someone I don't want to hear from"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-age-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-age-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-age-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-age-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-age-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-age-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-age-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-gender-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-gender-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-gender-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-gender-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-gender-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-gender-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-gender-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-edu-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-edu-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-edu-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-edu-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-edu-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-edu-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-edu-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-mig-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-mig-item2-2}
# I know how to protect devices against viruses
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-mig-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-mig-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-mig-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-mig-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-mig-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom3"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-overall-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-overall-item2-2}
# I know how to protect devices against viruses
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-overall-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-overall-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-overall-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-overall-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-overall-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-age-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-age-item2-2}
# I know how to protect devices against viruses
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-age-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-age-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-age-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-age-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-age-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-gender-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-gender-item2-2}
# I know how to protect devices against viruses
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-gender-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-gender-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-gender-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-gender-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-gender-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-edu-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-edu-item2-2}
# I know how to protect devices against viruses
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-edu-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-edu-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-edu-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-edu-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-edu-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-mig-item1-2}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-mig-item2-2}
# I know how to protect devices against viruses
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-mig-item3-2}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-mig-item4-2}
# I know how to change the location settings on a mobile phone or tablet
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-mig-item5-2}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-mig-item6-2}
# I know how to delete the history of websites that I have visited before
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-mig-item7-2}
# I know how to block messages from someone I don't want to hear from
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph book-open-fill >}} Safety Knowledge


**Knowledge** measures what participants *know* about the digital world. These items test factual understanding by having respondents indicate whether statements are true or false.
[{{< iconify ph cards >}} See all Knowledge results](knowledge.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r ksafety-wave1-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  questions = c("KSafDev2RC", "KPriv1RC", "KPriv2RC"),
  question_labels = c("To keep your devices safer, you should always install updates immediately. (Correct Statement)", "It's best to have the same password for each account. (False Statement)", "What you do online is used by companies to advertise their products and services. (Correct Statement)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave1-age-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave1-age-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave1-age-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KPriv2RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave1-gender-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave1-gender-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave1-gender-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KPriv2RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave1-edu-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave1-edu-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave1-edu-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KPriv2RC"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave1-mig-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave1-mig-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave1-mig-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KPriv2RC"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r ksafety-wave2-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  questions = c("KSafDev2RC", "KPriv1RC", "KPriv2RC"),
  question_labels = c("To keep your devices safer, you should always install updates immediately. (Correct Statement)", "It's best to have the same password for each account. (False Statement)", "What you do online is used by companies to advertise their products and services. (Correct Statement)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave2-age-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave2-age-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave2-age-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "KPriv2RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave2-gender-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave2-gender-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave2-gender-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "KPriv2RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave2-edu-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave2-edu-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave2-edu-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "KPriv2RC"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-wave2-mig-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-wave2-mig-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "It's best to have the same password for each account. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-wave2-mig-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "KPriv2RC"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-overtime-overall-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-overtime-overall-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_timeline(
  data = data,
  title = "It's best to have the same password for each account. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-overtime-overall-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-overtime-age-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-overtime-age-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_timeline(
  data = data,
  title = "It's best to have the same password for each account. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-overtime-age-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-overtime-gender-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-overtime-gender-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_timeline(
  data = data,
  title = "It's best to have the same password for each account. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-overtime-gender-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-overtime-edu-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-overtime-edu-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_timeline(
  data = data,
  title = "It's best to have the same password for each account. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-overtime-edu-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ksafety-overtime-mig-item1-2}
# To keep your devices safer, you should always install updates immediately. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "To keep your devices safer, you should always install updates immediately. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ksafety-overtime-mig-item2-2}
# It's best to have the same password for each account. (False Statement)
result <- create_timeline(
  data = data,
  title = "It's best to have the same password for each account. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r ksafety-overtime-mig-item3-2}
# What you do online is used by companies to advertise their products and services. (Correct Statement)
result <- create_timeline(
  data = data,
  title = "What you do online is used by companies to advertise their products and services. (Correct Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph clipboard-text >}} Safety Performance


ADD TEXT BEFORE TABSET


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-safety-wave1-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9", "PSCS3_10"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper", "Use passwords with ≥14 characters", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups", "None of the above"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-age-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-age-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-age-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-age-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-age-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-age-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-age-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-age-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-age-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave1-age-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-gender-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-gender-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-gender-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-gender-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-gender-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-gender-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-gender-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-gender-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-gender-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave1-gender-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-edu-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-edu-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-edu-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-edu-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-edu-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-edu-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-edu-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-edu-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-edu-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave1-edu-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-mig-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-mig-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-mig-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-mig-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-mig-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-mig-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-mig-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-mig-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave1-mig-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave1-mig-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_10"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-safety-wave2-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9", "PSCS3_10"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper", "Use passwords with ≥14 characters", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups", "None of the above"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-age-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-age-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-age-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-age-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-age-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-age-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-age-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-age-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-age-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave2-age-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-gender-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-gender-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-gender-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-gender-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-gender-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-gender-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-gender-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-gender-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-gender-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave2-gender-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-edu-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-edu-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-edu-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-edu-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-edu-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-edu-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-edu-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-edu-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-edu-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave2-edu-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-mig-item1-2}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-mig-item2-2}
# Save passwords on paper
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Save passwords on paper",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-mig-item3-2}
# Use passwords with ≥14 characters
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passwords with ≥14 characters",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-mig-item4-2}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-mig-item5-2}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-mig-item6-2}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-mig-item7-2}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-mig-item8-2}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-wave2-mig-item9-2}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-wave2-mig-item10-2}
# None of the above
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "None of the above",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Selected", "Not selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PSCS3_10"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-overall-item1-2}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-overall-item2-2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-overall-item3-2}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-overall-item4-2}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-overall-item5-2}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-overall-item6-2}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-overall-item7-2}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-overall-item8-2}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-overall-item9-2}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9"
)

result
```


###### item10


```{r perf-safety-overtime-overall-item10-2}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-age-item1-2}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-age-item2-2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-age-item3-2}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-age-item4-2}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-age-item5-2}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-age-item6-2}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-age-item7-2}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-age-item8-2}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-age-item9-2}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "AgeGroup"
)

result
```


###### item10


```{r perf-safety-overtime-age-item10-2}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-gender-item1-2}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-gender-item2-2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-gender-item3-2}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-gender-item4-2}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-gender-item5-2}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-gender-item6-2}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-gender-item7-2}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-gender-item8-2}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-gender-item9-2}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "geslacht"
)

result
```


###### item10


```{r perf-safety-overtime-gender-item10-2}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-edu-item1-2}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-edu-item2-2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-edu-item3-2}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-edu-item4-2}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-edu-item5-2}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-edu-item6-2}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-edu-item7-2}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-edu-item8-2}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-edu-item9-2}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "Education"
)

result
```


###### item10


```{r perf-safety-overtime-edu-item10-2}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-mig-item1-2}
# Keep passwords in a password safe
result <- create_timeline(
  data = data,
  title = "Keep passwords in a password safe",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-mig-item2-2}
# Save passwords on paper
result <- create_timeline(
  data = data,
  title = "Save passwords on paper",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-mig-item3-2}
# Use passwords with ≥14 characters
result <- create_timeline(
  data = data,
  title = "Use passwords with ≥14 characters",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-mig-item4-2}
# Different passwords per account
result <- create_timeline(
  data = data,
  title = "Different passwords per account",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-mig-item5-2}
# Use passkey (finger/face)
result <- create_timeline(
  data = data,
  title = "Use passkey (finger/face)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-mig-item6-2}
# Two-step verification
result <- create_timeline(
  data = data,
  title = "Two-step verification",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-mig-item7-2}
# Install software updates
result <- create_timeline(
  data = data,
  title = "Install software updates",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-mig-item8-2}
# Use adblocker
result <- create_timeline(
  data = data,
  title = "Use adblocker",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 9


```{r perf-safety-overtime-mig-item9-2}
# Make backups
result <- create_timeline(
  data = data,
  title = "Make backups",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "MigrationBackground"
)

result
```


###### item10


```{r perf-safety-overtime-mig-item10-2}
# None of the above
result <- create_timeline(
  data = data,
  title = "None of the above",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_10",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

