---
title: "{{< iconify ph lightning-fill >}} Skills"
format: html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(2, 6, "skills", "top")
```



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
dashboardr::.page_config(accessibility = TRUE, crosstab_prefix = "skills")
```

The **Skills** section measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information, creating content, protecting their privacy, or recognizing when AI is being used. The questions cover different domains of digital competence, from information and communication skills to AI and generative AI skills, and together provide insight into participants’ everyday digital capabilities and confidence levels.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::create_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph chats-fill >}} Netiquette


**Netiquette Competence** refers to proper online communication etiquette: knowing when to ask permission before sharing, choosing the right communication tool, understanding what not to share online, and using emoticons appropriately.
[{{< iconify ph cards >}} See all Netiquette results](netiquette.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r nskills-wave1-overall}
# Netiquette Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Netiquette Skills",
  x_vars = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  x_var_labels = c("I know when I should ask for permission to share something online", "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)", "I know which things I should not share online", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-age-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-age-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-age-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-gender-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-gender-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-gender-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-edu-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-edu-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-edu-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-mig-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-mig-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-mig-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-mig-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r nskills-wave2-overall}
# Netiquette Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Netiquette Skills",
  x_vars = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  x_var_labels = c("I know when I should ask for permission to share something online", "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)", "I know which things I should not share online", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-age-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-age-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-age-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-gender-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-gender-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-gender-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-edu-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-edu-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-edu-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-mig-item1}
# I know when I should ask for permission to share something online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-mig-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-mig-item3}
# I know which things I should not share online
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-mig-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom5"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-overall-item1}
# I know when I should ask for permission to share something online
result <- viz_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-overall-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-overall-item3}
# I know which things I should not share online
result <- viz_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-overall-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-age-item1}
# I know when I should ask for permission to share something online
result <- viz_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom1_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-age-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-age-item3}
# I know which things I should not share online
result <- viz_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom4_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-gender-item1}
# I know when I should ask for permission to share something online
result <- viz_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom1_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-gender-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-gender-item3}
# I know which things I should not share online
result <- viz_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom4_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-edu-item1}
# I know when I should ask for permission to share something online
result <- viz_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom1_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-edu-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-edu-item3}
# I know which things I should not share online
result <- viz_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom4_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom5",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-mig-item1}
# I know when I should ask for permission to share something online
result <- viz_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom1_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-mig-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- viz_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-mig-item3}
# I know which things I should not share online
result <- viz_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom4_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-mig-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- viz_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom5",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph palette-fill >}} Digital Content Creation


**Digital Content Creation Competence** cover the ability to create and modify digital content: making presentations, combining different media, editing images/music/video, and understanding copyright rules around digital content.
[{{< iconify ph cards >}} See all Digital Content Creation results](digital_content_creation.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dccs-wave1-overall}
# Digital Content Creation Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Digital Content Creation Skills",
  x_vars = c("SCrea2", "SCrea3", "SCrea4", "SCrea5"),
  x_var_labels = c("I can make a presentation on the computer (for example in Powerpoint)", "I can make something that combines different digital media (for example a movie with music)", "I can change existing digital images, music and video", "I can make a photo or video more attractive (for example with a filter or Photoshop)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-age-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-age-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-gender-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-gender-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-edu-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-edu-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-mig-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-mig-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-mig-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-mig-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dccs-wave2-overall}
# Digital Content Creation Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Digital Content Creation Skills",
  x_vars = c("SCrea2", "SCrea3", "SCrea4", "SCrea5"),
  x_var_labels = c("I can make a presentation on the computer (for example in Powerpoint)", "I can make something that combines different digital media (for example a movie with music)", "I can change existing digital images, music and video", "I can make a photo or video more attractive (for example with a filter or Photoshop)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-age-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-age-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-gender-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-gender-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-edu-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-edu-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-mig-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-mig-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-mig-item3}
# I can change existing digital images, music and video
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-mig-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea5"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-overall-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-overall-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-overall-item3}
# I can change existing digital images, music and video
result <- viz_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-overall-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-age-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-age-item3}
# I can change existing digital images, music and video
result <- viz_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-gender-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-gender-item3}
# I can change existing digital images, music and video
result <- viz_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-edu-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-edu-item3}
# I can change existing digital images, music and video
result <- viz_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea5",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-mig-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- viz_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-mig-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- viz_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-mig-item3}
# I can change existing digital images, music and video
result <- viz_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-mig-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- viz_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCrea5",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(2, 6, "skills", "bottom")
```

