---
title: "{{< iconify ph lightning-fill >}} Skills"
format: html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(1, 6, "skills", "top")
```



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
dashboardr::.page_config(accessibility = TRUE, crosstab_prefix = "skills")
```

The **Skills** section measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information, creating content, protecting their privacy, or recognizing when AI is being used. The questions cover different domains of digital competence, from information and communication skills to AI and generative AI skills, and together provide insight into participants’ everyday digital capabilities and confidence levels.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::create_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph magnifying-glass >}} Strategic Information


**Strategic Information Competence** is the ability to effectively search for and locate information online. This includes choosing good keywords, using search functions, and finding answers to questions on the internet.
[{{< iconify ph cards >}} See all Strategic Information results](strategic_information.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r sis-wave1-overall}
# Strategic Information Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Strategic Information Skills",
  x_vars = c("SInfo1", "SInfo3_V2", "SInfo4"),
  x_var_labels = c("I know how to choose good keywords for online searches (for example with Google)", "I know how I can find answers to my questions on the internet", "I know how I can use search functions in search engines (for example with Google)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-age-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-age-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-age-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-gender-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-gender-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-gender-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-edu-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-edu-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-edu-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-mig-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-mig-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-mig-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo4"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r sis-wave2-overall}
# Strategic Information Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Strategic Information Skills",
  x_vars = c("SInfo1", "SInfo3_V2", "SInfo4"),
  x_var_labels = c("I know how to choose good keywords for online searches (for example with Google)", "I know how I can find answers to my questions on the internet", "I know how I can use search functions in search engines (for example with Google)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-age-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-age-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-age-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-gender-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-gender-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-gender-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-edu-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-edu-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-edu-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-mig-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-mig-item2}
# I know how I can find answers to my questions on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-mig-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo4"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-overall-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-overall-item2}
# I know how I can find answers to my questions on the internet
result <- viz_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-overall-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-age-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-age-item2}
# I know how I can find answers to my questions on the internet
result <- viz_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo3_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-age-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo4",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-gender-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-gender-item2}
# I know how I can find answers to my questions on the internet
result <- viz_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo3_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-gender-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo4",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-edu-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-edu-item2}
# I know how I can find answers to my questions on the internet
result <- viz_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo3_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-edu-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo4",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-mig-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-mig-item2}
# I know how I can find answers to my questions on the internet
result <- viz_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo3_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-mig-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- viz_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo4",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph detective-fill >}} Critical Information


**Critical Information Competence** is the ability to evaluate online information: checking whether information is true, assessing website reliability, and understanding the purpose of online content (to inform, influence, entertain, or sell).
[{{< iconify ph cards >}} See all Critical Information results](critical_information.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r cis-wave1-overall}
# Critical Information Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Critical Information Skills",
  x_vars = c("SInfo5", "SInfo6", "SInfo7"),
  x_var_labels = c("I know how I can check if the information I find on the internet is true", "I know how I can check if a website is reliable", "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-age-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-age-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-gender-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-gender-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-edu-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-edu-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-mig-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-mig-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-mig-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo7"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r cis-wave2-overall}
# Critical Information Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Critical Information Skills",
  x_vars = c("SInfo5", "SInfo6", "SInfo7"),
  x_var_labels = c("I know how I can check if the information I find on the internet is true", "I know how I can check if a website is reliable", "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-age-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-age-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-gender-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-gender-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-edu-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-edu-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-mig-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-mig-item2}
# I know how I can check if a website is reliable
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-mig-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo7"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-overall-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-overall-item2}
# I know how I can check if a website is reliable
result <- viz_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-overall-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-age-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-age-item2}
# I know how I can check if a website is reliable
result <- viz_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo7",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-gender-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-gender-item2}
# I know how I can check if a website is reliable
result <- viz_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo7",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-edu-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-edu-item2}
# I know how I can check if a website is reliable
result <- viz_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo7",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-mig-item1}
# I know how I can check if the information I find on the internet is true
result <- viz_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-mig-item2}
# I know how I can check if a website is reliable
result <- viz_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-mig-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- viz_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SInfo7",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(1, 6, "skills", "bottom")
```

