---
title: "{{< iconify ph lightning-fill >}} Skills"
format: html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(3, 6, "skills", "top")
```



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
dashboardr::.page_config(accessibility = TRUE, crosstab_prefix = "skills")
```

The **Skills** section measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information, creating content, protecting their privacy, or recognizing when AI is being used. The questions cover different domains of digital competence, from information and communication skills to AI and generative AI skills, and together provide insight into participants’ everyday digital capabilities and confidence levels.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::create_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph shield-check-fill >}} Safety


**Safety & Control of Information and Devices Competence** encompasses protecting devices and personal information: using security measures, managing privacy settings, identifying phishing, and controlling what information is shared online.
[{{< iconify ph cards >}} See all Safety results](safety.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r safety-wave1-overall}
# Safety and Control of Information and Devices Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Safety and Control of Information and Devices Skills",
  x_vars = c("SSafDev1", "SSafDev2", "SPriv1", "SPriv2", "SPriv3", "SPriv4", "SCom3"),
  x_var_labels = c("I know how to protect a device against access (e.g. a PIN code or fingerprint)", "I know how to protect devices against viruses", "I know how to adjust the privacy settings on a mobile phone or tablet", "I know how to change the location settings on a mobile phone or tablet", "I know how to identify suspicious e-mail messages that try to get my personal data", "I know how to delete the history of websites that I have visited before", "I know how to block messages from someone I don't want to hear from"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-age-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-age-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-age-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-age-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-age-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-age-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-age-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-gender-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-gender-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-gender-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-gender-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-gender-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-gender-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-gender-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-edu-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-edu-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-edu-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-edu-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-edu-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-edu-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-edu-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-mig-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-mig-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-mig-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-mig-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-mig-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-mig-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-mig-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom3"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r safety-wave2-overall}
# Safety and Control of Information and Devices Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Safety and Control of Information and Devices Skills",
  x_vars = c("SSafDev1", "SSafDev2", "SPriv1", "SPriv2", "SPriv3", "SPriv4", "SCom3"),
  x_var_labels = c("I know how to protect a device against access (e.g. a PIN code or fingerprint)", "I know how to protect devices against viruses", "I know how to adjust the privacy settings on a mobile phone or tablet", "I know how to change the location settings on a mobile phone or tablet", "I know how to identify suspicious e-mail messages that try to get my personal data", "I know how to delete the history of websites that I have visited before", "I know how to block messages from someone I don't want to hear from"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-age-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-age-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-age-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-age-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-age-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-age-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-age-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-gender-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-gender-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-gender-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-gender-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-gender-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-gender-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-gender-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-edu-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-edu-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-edu-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-edu-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-edu-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-edu-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-edu-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-mig-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-mig-item2}
# I know how to protect devices against viruses
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to protect devices against viruses",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-mig-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-mig-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to change the location settings on a mobile phone or tablet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-mig-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-mig-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to delete the history of websites that I have visited before",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-mig-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to block messages from someone I don't want to hear from",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom3"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-overall-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-overall-item2}
# I know how to protect devices against viruses
result <- viz_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-overall-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-overall-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-overall-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-overall-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-overall-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-age-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-age-item2}
# I know how to protect devices against viruses
result <- viz_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-age-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-age-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-age-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-age-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-age-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom3",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-gender-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-gender-item2}
# I know how to protect devices against viruses
result <- viz_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-gender-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-gender-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-gender-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-gender-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-gender-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom3",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-edu-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-edu-item2}
# I know how to protect devices against viruses
result <- viz_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-edu-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-edu-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-edu-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-edu-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-edu-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom3",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-mig-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint)
result <- viz_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-mig-item2}
# I know how to protect devices against viruses
result <- viz_timeline(
  data = data,
  title = "I know how to protect devices against viruses",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SSafDev2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-mig-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-mig-item4}
# I know how to change the location settings on a mobile phone or tablet
result <- viz_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-mig-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data
result <- viz_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-mig-item6}
# I know how to delete the history of websites that I have visited before
result <- viz_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SPriv4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-mig-item7}
# I know how to block messages from someone I don't want to hear from
result <- viz_timeline(
  data = data,
  title = "I know how to block messages from someone I don't want to hear from",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SCom3",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph heart-fill >}} Digital Health


**Digital Health & Wellbeing** skills relate to managing healthy digital habits.
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dhealth-wave1-overall}
# Digital Health and Wellbeing Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Digital Health and Wellbeing Skills",
  x_vars = c("SHealth1", "SHealth2_V2", "SHealth3_V2"),
  x_var_labels = c("I know how to control how much time I spend on the internet", "I know how to make sure my phone doesn't distract me", "I know how I can stop using my phone and computer for a while, if I want to"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-age-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-age-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-age-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-gender-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-gender-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-gender-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-edu-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-edu-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-edu-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-mig-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-mig-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-mig-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SHealth3_V2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dhealth-wave2-overall}
# Digital Health and Wellbeing Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Digital Health and Wellbeing Skills",
  x_vars = c("SHealth1", "SHealth2_V2", "SHealth3_V2"),
  x_var_labels = c("I know how to control how much time I spend on the internet", "I know how to make sure my phone doesn't distract me", "I know how I can stop using my phone and computer for a while, if I want to"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-age-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-age-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-age-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-gender-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-gender-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-gender-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-edu-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-edu-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-edu-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-mig-item1}
# I know how to control how much time I spend on the internet
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to control how much time I spend on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-mig-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to make sure my phone doesn't distract me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-mig-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SHealth3_V2"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-overall-item1}
# I know how to control how much time I spend on the internet
result <- viz_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-overall-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_timeline(
  data = data,
  title = "I know how to make sure my phone doesn't distract me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-overall-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-age-item1}
# I know how to control how much time I spend on the internet
result <- viz_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-age-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_timeline(
  data = data,
  title = "I know how to make sure my phone doesn't distract me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth2_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-age-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth3_V2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-gender-item1}
# I know how to control how much time I spend on the internet
result <- viz_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-gender-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_timeline(
  data = data,
  title = "I know how to make sure my phone doesn't distract me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth2_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-gender-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth3_V2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-edu-item1}
# I know how to control how much time I spend on the internet
result <- viz_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-edu-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_timeline(
  data = data,
  title = "I know how to make sure my phone doesn't distract me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth2_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-edu-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth3_V2",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-mig-item1}
# I know how to control how much time I spend on the internet
result <- viz_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-mig-item2}
# I know how to make sure my phone doesn't distract me
result <- viz_timeline(
  data = data,
  title = "I know how to make sure my phone doesn't distract me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth2_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-mig-item3}
# I know how I can stop using my phone and computer for a while, if I want to
result <- viz_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SHealth3_V2",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(3, 6, "skills", "bottom")
```

