---
title: "{{< iconify ph lightning-fill >}} Skills"
format: html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(5, 6, "skills", "top")
```



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
dashboardr::.page_config(accessibility = TRUE, crosstab_prefix = "skills")
```

The **Skills** section measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information, creating content, protecting their privacy, or recognizing when AI is being used. The questions cover different domains of digital competence, from information and communication skills to AI and generative AI skills, and together provide insight into participants’ everyday digital capabilities and confidence levels.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- dashboardr::.convert_haven(data) %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::create_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph wallet-fill >}} Transactional


**Transactional Competence** covers the ability to handle official online matters: managing government services, digital payments, healthcare arrangements, and document uploads.
[{{< iconify ph cards >}} See all Transactional results](transactional.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r trans-wave1-overall}
# Transactional Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Transactional Skills",
  x_vars = c("Strans1", "Strans2", "Strans3", "Strans4", "Strans5"),
  x_var_labels = c("I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)", "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)", "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)", "I know how to apply for a DigID and how to use it", "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-age-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-age-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-age-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-age-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-age-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-gender-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-gender-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-gender-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-gender-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-gender-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-edu-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-edu-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-edu-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-edu-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-edu-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-mig-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-mig-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-mig-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-mig-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-mig-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r trans-wave2-overall}
# Transactional Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Transactional Skills",
  x_vars = c("Strans1", "Strans2", "Strans3", "Strans4", "Strans5"),
  x_var_labels = c("I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)", "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)", "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)", "I know how to apply for a DigID and how to use it", "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-age-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-age-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-age-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-age-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-age-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-gender-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-gender-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-gender-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-gender-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-gender-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-edu-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-edu-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-edu-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-edu-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-edu-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-mig-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-mig-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-mig-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-mig-item4}
# I know how to apply for a DigID and how to use it
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-mig-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans5"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-overall-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-overall-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-overall-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-overall-item4}
# I know how to apply for a DigID and how to use it
result <- viz_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-overall-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-age-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-age-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-age-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-age-item4}
# I know how to apply for a DigID and how to use it
result <- viz_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-age-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-gender-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-gender-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-gender-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-gender-item4}
# I know how to apply for a DigID and how to use it
result <- viz_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-gender-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-edu-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-edu-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-edu-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-edu-item4}
# I know how to apply for a DigID and how to use it
result <- viz_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-edu-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans5",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-mig-item1}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- viz_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-mig-item2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- viz_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-mig-item3}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- viz_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-mig-item4}
# I know how to apply for a DigID and how to use it
result <- viz_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-mig-item5}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- viz_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "Strans5",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph robot-fill >}} AI


**AI Competence** covers the ability to recognize when websites and apps use artificial intelligence to personalize content and recommendations.
[{{< iconify ph cards >}} See all AI results](ai.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r ai-wave1-overall}
# AI Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "AI Skills",
  x_vars = c("SAI1", "SAI2"),
  x_var_labels = c("I recognize when a website or app uses AI to adjust the content to me", "I recognize when specific content is recommended to me by AI"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave1-age-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave1-age-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SAI2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave1-gender-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave1-gender-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SAI2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave1-edu-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave1-edu-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SAI2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave1-mig-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave1-mig-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SAI2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r ai-wave2-overall}
# AI Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "AI Skills",
  x_vars = c("SAI1", "SAI2"),
  x_var_labels = c("I recognize when a website or app uses AI to adjust the content to me", "I recognize when specific content is recommended to me by AI"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave2-age-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave2-age-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SAI2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave2-gender-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave2-gender-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SAI2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave2-edu-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave2-edu-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SAI2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-wave2-mig-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-wave2-mig-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I recognize when specific content is recommended to me by AI",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SAI2"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-overtime-overall-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_timeline(
  data = data,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-overtime-overall-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_timeline(
  data = data,
  title = "I recognize when specific content is recommended to me by AI",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-overtime-age-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_timeline(
  data = data,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-overtime-age-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_timeline(
  data = data,
  title = "I recognize when specific content is recommended to me by AI",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-overtime-gender-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_timeline(
  data = data,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-overtime-gender-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_timeline(
  data = data,
  title = "I recognize when specific content is recommended to me by AI",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-overtime-edu-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_timeline(
  data = data,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-overtime-edu-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_timeline(
  data = data,
  title = "I recognize when specific content is recommended to me by AI",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI2",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ai-overtime-mig-item1}
# I recognize when a website or app uses AI to adjust the content to me
result <- viz_timeline(
  data = data,
  title = "I recognize when a website or app uses AI to adjust the content to me",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ai-overtime-mig-item2}
# I recognize when specific content is recommended to me by AI
result <- viz_timeline(
  data = data,
  title = "I recognize when specific content is recommended to me by AI",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SAI2",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
dashboardr::create_pagination_nav(5, 6, "skills", "bottom")
```

