---
title: "{{< iconify ph lightning-fill >}} Skills"
format: html
---


```{=html}
<script>document.body.classList.add('has-pagination-top');</script>
<nav class='pagination-nav pagination-top' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <span class='pagination-prefix'>Page </span>
      <input type='number' class='pagination-input' id='page-input-top' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'> / 3</span>
    </div>
    <a href='skills_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["skills.html","skills_p2.html","skills_p3.html"];
  const pageInput = document.getElementById('page-input-top');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```



```{r}
#| include: false
library(dashboardr)
```

The **Skills** section measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information, creating content, protecting their privacy, or recognizing when AI is being used. The questions cover different domains of digital competence, from information and communication skills to AI and generative AI skills, and together provide insight into participants’ everyday digital capabilities and confidence levels.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```


<details>
<summary>For all skills questions, we used the following wording</summary>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```

</details>

## {{< iconify ph magnifying-glass >}} Strategic Information


**Strategic Information Competence** is the ability to effectively search for and locate information online. This includes choosing good keywords, using search functions, and finding answers to questions on the internet.
[{{< iconify ph cards >}} See all Strategic Information results](strategic_information.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r sis-wave1-overall}
# Strategic Information Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Strategic Information Skills",
  questions = c("SInfo1", "SInfo3_V2", "SInfo4"),
  question_labels = c("I know how to choose good keywords for online searches (for example with Google)", "I know how I can find answers to my questions on the internet", "I know how I can use search functions in search engines (for example with Google)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-age-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-age-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-age-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-gender-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-gender-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-gender-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-edu-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-edu-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-edu-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-mig-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-mig-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-mig-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo4"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r sis-wave2-overall}
# Strategic Information Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Strategic Information Skills",
  questions = c("SInfo1", "SInfo3_V2", "SInfo4"),
  question_labels = c("I know how to choose good keywords for online searches (for example with Google)", "I know how I can find answers to my questions on the internet", "I know how I can use search functions in search engines (for example with Google)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-age-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-age-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-age-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-gender-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-gender-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-gender-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-edu-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-edu-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-edu-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-mig-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-mig-item2}
# I know how I can find answers to my questions on the internet
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can find answers to my questions on the internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-mig-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can use search functions in search engines (for example with Google)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo4"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-overall-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-overall-item2}
# I know how I can find answers to my questions on the internet
result <- create_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-overall-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-age-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-age-item2}
# I know how I can find answers to my questions on the internet
result <- create_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-age-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo4",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-gender-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-gender-item2}
# I know how I can find answers to my questions on the internet
result <- create_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-gender-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo4",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-edu-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-edu-item2}
# I know how I can find answers to my questions on the internet
result <- create_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-edu-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo4",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-mig-item1}
# I know how to choose good keywords for online searches (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how to choose good keywords for online searches (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-mig-item2}
# I know how I can find answers to my questions on the internet
result <- create_timeline(
  data = data,
  title = "I know how I can find answers to my questions on the internet",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-mig-item3}
# I know how I can use search functions in search engines (for example with Google)
result <- create_timeline(
  data = data,
  title = "I know how I can use search functions in search engines (for example with Google)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo4",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph detective-fill >}} Critical Information


**Critical Information Competence** is the ability to evaluate online information: checking whether information is true, assessing website reliability, and understanding the purpose of online content (to inform, influence, entertain, or sell).
[{{< iconify ph cards >}} See all Critical Information results](critical_information.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r cis-wave1-overall}
# Critical Information Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Critical Information Skills",
  questions = c("SInfo5", "SInfo6", "SInfo7"),
  question_labels = c("I know how I can check if the information I find on the internet is true", "I know how I can check if a website is reliable", "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-age-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-age-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-gender-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-gender-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-edu-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-edu-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-mig-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-mig-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-mig-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo7"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r cis-wave2-overall}
# Critical Information Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Critical Information Skills",
  questions = c("SInfo5", "SInfo6", "SInfo7"),
  question_labels = c("I know how I can check if the information I find on the internet is true", "I know how I can check if a website is reliable", "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-age-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-age-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-gender-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-gender-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-edu-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-edu-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-mig-item1}
# I know how I can check if the information I find on the internet is true
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if the information I find on the internet is true",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-mig-item2}
# I know how I can check if a website is reliable
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can check if a website is reliable",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-mig-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SInfo7"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-overall-item1}
# I know how I can check if the information I find on the internet is true
result <- create_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-overall-item2}
# I know how I can check if a website is reliable
result <- create_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-overall-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-age-item1}
# I know how I can check if the information I find on the internet is true
result <- create_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-age-item2}
# I know how I can check if a website is reliable
result <- create_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo7",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-gender-item1}
# I know how I can check if the information I find on the internet is true
result <- create_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-gender-item2}
# I know how I can check if a website is reliable
result <- create_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo7",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-edu-item1}
# I know how I can check if the information I find on the internet is true
result <- create_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-edu-item2}
# I know how I can check if a website is reliable
result <- create_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo7",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-mig-item1}
# I know how I can check if the information I find on the internet is true
result <- create_timeline(
  data = data,
  title = "I know how I can check if the information I find on the internet is true",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo5",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-mig-item2}
# I know how I can check if a website is reliable
result <- create_timeline(
  data = data,
  title = "I know how I can check if a website is reliable",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo6",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-mig-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)
result <- create_timeline(
  data = data,
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SInfo7",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph chats-fill >}} Netiquette


**Netiquette Competence** refers to proper online communication etiquette: knowing when to ask permission before sharing, choosing the right communication tool, understanding what not to share online, and using emoticons appropriately.
[{{< iconify ph cards >}} See all Netiquette results](netiquette.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r nskills-wave1-overall}
# Netiquette Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Netiquette Skills",
  questions = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  question_labels = c("I know when I should ask for permission to share something online", "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)", "I know which things I should not share online", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-age-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-age-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-age-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-gender-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-gender-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-gender-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-edu-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-edu-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-edu-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-mig-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-mig-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-mig-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-mig-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r nskills-wave2-overall}
# Netiquette Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Netiquette Skills",
  questions = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  question_labels = c("I know when I should ask for permission to share something online", "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)", "I know which things I should not share online", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-age-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-age-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-age-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-gender-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-gender-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-gender-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-edu-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-edu-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-edu-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-mig-item1}
# I know when I should ask for permission to share something online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when I should ask for permission to share something online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-mig-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-mig-item3}
# I know which things I should not share online
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know which things I should not share online",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-mig-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCom5"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-overall-item1}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-overall-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-overall-item3}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-overall-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-age-item1}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-age-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-age-item3}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-gender-item1}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-gender-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-gender-item3}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-edu-item1}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-edu-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-edu-item3}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-mig-item1}
# I know when I should ask for permission to share something online
result <- create_timeline(
  data = data,
  title = "I know when I should ask for permission to share something online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-mig-item2}
# I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)
result <- create_timeline(
  data = data,
  title = "I know which communication tool best fits which situation (for example: call, send a WhatsApp-message, send an e-mail)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-mig-item3}
# I know which things I should not share online
result <- create_timeline(
  data = data,
  title = "I know which things I should not share online",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-mig-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)
result <- create_timeline(
  data = data,
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph palette-fill >}} Digital Content Creation


**Digital Content Creation Competence** cover the ability to create and modify digital content: making presentations, combining different media, editing images/music/video, and understanding copyright rules around digital content.
[{{< iconify ph cards >}} See all Digital Content Creation results](digital_content_creation.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dccs-wave1-overall}
# Digital Content Creation Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Digital Content Creation Skills",
  questions = c("SCrea2", "SCrea3", "SCrea4", "SCrea5"),
  question_labels = c("I can make a presentation on the computer (for example in Powerpoint)", "I can make something that combines different digital media (for example a movie with music)", "I can change existing digital images, music and video", "I can make a photo or video more attractive (for example with a filter or Photoshop)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-age-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-age-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-gender-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-gender-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-edu-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-edu-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-mig-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-mig-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-mig-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-mig-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dccs-wave2-overall}
# Digital Content Creation Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Digital Content Creation Skills",
  questions = c("SCrea2", "SCrea3", "SCrea4", "SCrea5"),
  question_labels = c("I can make a presentation on the computer (for example in Powerpoint)", "I can make something that combines different digital media (for example a movie with music)", "I can change existing digital images, music and video", "I can make a photo or video more attractive (for example with a filter or Photoshop)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-age-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-age-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-gender-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-gender-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-edu-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-edu-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-mig-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-mig-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make something that combines different digital media (for example a movie with music)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-mig-item3}
# I can change existing digital images, music and video
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can change existing digital images, music and video",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-mig-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SCrea5"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-overall-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-overall-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-overall-item3}
# I can change existing digital images, music and video
result <- create_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-overall-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-age-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-age-item3}
# I can change existing digital images, music and video
result <- create_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-gender-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-gender-item3}
# I can change existing digital images, music and video
result <- create_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-edu-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-edu-item3}
# I can change existing digital images, music and video
result <- create_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea5",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-mig-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_timeline(
  data = data,
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-mig-item2}
# I can make something that combines different digital media (for example a movie with music)
result <- create_timeline(
  data = data,
  title = "I can make something that combines different digital media (for example a movie with music)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-mig-item3}
# I can change existing digital images, music and video
result <- create_timeline(
  data = data,
  title = "I can change existing digital images, music and video",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-mig-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop)
result <- create_timeline(
  data = data,
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCrea5",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{=html}
<nav class='pagination-nav pagination-bottom' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <span class='pagination-prefix'></span>
      <input type='number' class='pagination-input' id='page-input-bottom' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'> / 3</span>
    </div>
    <a href='skills_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["skills.html","skills_p2.html","skills_p3.html"];
  const pageInput = document.getElementById('page-input-bottom');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```

