---
title: "{{< iconify ph wallet-fill >}} Transactional"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

**Transactional Competence** covers the ability to handle official online matters: managing government services, digital payments, healthcare arrangements, and document uploads.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```

## {{< iconify ph lightning-fill >}} Transactional Skills


**Skills** measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information.
[{{< iconify ph cards >}} See all Skills results](skills.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r trans-wave1-overall-2}
# Transactional Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Transactional Skills",
  questions = c("Strans1", "Strans2", "Strans3", "Strans4", "Strans5"),
  question_labels = c("I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)", "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)", "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)", "I know how to apply for a DigID and how to use it", "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-age-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-age-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-age-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-age-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-age-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-gender-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-gender-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-gender-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-gender-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-gender-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-edu-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-edu-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-edu-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-edu-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-edu-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave1-mig-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave1-mig-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave1-mig-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave1-mig-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave1-mig-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r trans-wave2-overall-2}
# Transactional Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Transactional Skills",
  questions = c("Strans1", "Strans2", "Strans3", "Strans4", "Strans5"),
  question_labels = c("I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)", "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)", "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)", "I know how to apply for a DigID and how to use it", "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-age-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-age-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-age-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-age-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-age-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-gender-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-gender-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-gender-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-gender-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-gender-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-edu-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-edu-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-edu-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-edu-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-edu-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Strans5"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-wave2-mig-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-wave2-mig-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-wave2-mig-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-wave2-mig-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to apply for a DigID and how to use it",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-wave2-mig-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Strans5"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-overall-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-overall-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-overall-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-overall-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-overall-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage of Respondents",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-age-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-age-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-age-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-age-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-age-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-gender-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-gender-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-gender-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-gender-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-gender-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-edu-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-edu-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-edu-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-edu-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-edu-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans5",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r trans-overtime-mig-item1-2}
# I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)
result <- create_timeline(
  data = data,
  title = "I know how to handle things online for the tax authority ('belastingdienst') (for example file my tax returns or apply for a wage tax for my (part-time) job)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r trans-overtime-mig-item2-2}
# I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)
result <- create_timeline(
  data = data,
  title = "I know how to do digital payments on the computer or smartphone (for example online banking, online shopping, using iDeal)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r trans-overtime-mig-item3-2}
# I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)
result <- create_timeline(
  data = data,
  title = "I know how to arrange my healthcare online (for example take out a health insurance or make an online appointment with the general practitioner)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r trans-overtime-mig-item4-2}
# I know how to apply for a DigID and how to use it
result <- create_timeline(
  data = data,
  title = "I know how to apply for a DigID and how to use it",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r trans-overtime-mig-item5-2}
# I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)
result <- create_timeline(
  data = data,
  title = "I know how to upload documents and images when needed to arrange things online (for example when requesting an OV chip card)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "Strans5",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph book-open-fill >}} Transactional Knowledge


**Knowledge** measures what participants *know* about the digital world. These items test factual understanding by having respondents indicate whether statements are true or false.
[{{< iconify ph cards >}} See all Knowledge results](knowledge.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r ktrans-wave1-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "",
  questions = c("Ktrans2RC", "Ktrans3RC"),
  question_labels = c("In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)", "A webshop is trustworthy when you can pay with iDeal. (False Statement)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave1-age-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave1-age-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Ktrans3RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave1-gender-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave1-gender-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Ktrans3RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave1-edu-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave1-edu-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Ktrans3RC"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave1-mig-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave1-mig-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Ktrans3RC"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r ktrans-wave2-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "",
  questions = c("Ktrans2RC", "Ktrans3RC"),
  question_labels = c("In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)", "A webshop is trustworthy when you can pay with iDeal. (False Statement)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave2-age-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave2-age-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "Ktrans3RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave2-gender-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave2-gender-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "Ktrans3RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave2-edu-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave2-edu-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "Ktrans3RC"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-wave2-mig-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-wave2-mig-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Correctly Answered", "Incorrectly Answered", "Don't know/Understand"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "Ktrans3RC"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-overtime-overall-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_timeline(
  data = data,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "Ktrans2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-overtime-overall-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_timeline(
  data = data,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "Ktrans3RC"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-overtime-age-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_timeline(
  data = data,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans2RC",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-overtime-age-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_timeline(
  data = data,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans3RC",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-overtime-gender-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_timeline(
  data = data,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans2RC",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-overtime-gender-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_timeline(
  data = data,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans3RC",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-overtime-edu-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_timeline(
  data = data,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans2RC",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-overtime-edu-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_timeline(
  data = data,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans3RC",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r ktrans-overtime-mig-item1-2}
# In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)
result <- create_timeline(
  data = data,
  title = "In case of a medical emergency, you make an online appointment with your healthcare provider. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans2RC",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r ktrans-overtime-mig-item2-2}
# A webshop is trustworthy when you can pay with iDeal. (False Statement)
result <- create_timeline(
  data = data,
  title = "A webshop is trustworthy when you can pay with iDeal. (False Statement)",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "Ktrans3RC",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph clipboard-text >}} Transactional Performance


**Performance** measures participants' practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information.
[{{< iconify ph cards >}} See all Performance results](performance.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-trans-wave1-overall-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbars(
  data = data_filtered_984a0efe,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  questions = "PTS1R",
  question_labels = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-trans-wave1-age-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PTS1R"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-trans-wave1-gender-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PTS1R"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-trans-wave1-edu-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PTS1R"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-trans-wave1-mig-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_984a0efe,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PTS1R"
)

result
```


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-trans-wave2-overall-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbars(
  data = data_filtered_4af682fd,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  questions = "PTS1R",
  question_labels = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-trans-wave2-age-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "PTS1R"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-trans-wave2-gender-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "PTS1R"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-trans-wave2-edu-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "PTS1R"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-trans-wave2-mig-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_stackedbar(
  data = data_filtered_4af682fd,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Correct", "Incorrect"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "PTS1R"
)

result
```


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r perf-trans-overtime-overall-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_timeline(
  data = data,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  response_filter_label = "Percentage who selected/answered correctly",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  response_var = "PTS1R"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


```{r perf-trans-overtime-age-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_timeline(
  data = data,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PTS1R",
  group_var = "AgeGroup"
)

result
```


##### {{< iconify mdi gender-transgender >}} Gender


```{r perf-trans-overtime-gender-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_timeline(
  data = data,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PTS1R",
  group_var = "geslacht"
)

result
```


##### {{< iconify ph graduation-cap-fill >}} Education


```{r perf-trans-overtime-edu-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_timeline(
  data = data,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PTS1R",
  group_var = "Education"
)

result
```


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


```{r perf-trans-overtime-mig-2}
# Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?
result <- create_timeline(
  data = data,
  title = "Below you see 4 icons that can appear on a website. Which of the icons should you click on to know whether you can shop safely on an online webshop (for example with safe storage of personal data and a safe payment environment)?",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  y_min = 0,
  y_max = 100,
  x_label = "",
  y_label = "Percentage who selected/answered correctly",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PTS1R",
  group_var = "MigrationBackground"
)

result
```


:::


:::

