---
title: "{{< iconify ph number-circle-one-fill >}} Wave 1"
format: html
---

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
dashboardr::.page_config(accessibility = TRUE, crosstab_prefix = "wave_1")
```

<div style='text-align: justify;'>
# Wave 1

## Sample

Data from Wave 1 in this dashboard is based on the completed questionnaires of **2,417 participants**, of which 2,156 via an online panel and 261 via an address sample (paper-and-pencil questionnaire). Data collection took place in **December 2024**.

## Finding Highlights

Data from this first wave shows that Dutch people generally feel digitally skilled, and this often matches their knowledge, but not always their actual behavior and performance—especially in areas like online health and well-being and netiquette, where important "blind spots" emerge.

Skills and knowledge related to (gen)AI are particularly low: children, older adults, and lower-educated groups score poorly on understanding AI-driven personalization, privacy risks, and the reliability of AI-generated information, and are not well-equipped to use genAI effectively. Overall, differences in digital competence are mainly driven by age and education level rather than migration background.

## What to use this data for?

These findings underscore the need for targeted workshops, accessible training for vulnerable groups, and awareness campaigns, especially around genAI. Using the dashboard, policymakers and practitioners can zoom in on specific skills and see how different groups (e.g., by age or education level) score on their self-confidence, their actual knowledge of digital technology, and their performance and behaviors. They can explore all 11 measured areas—such as critical information skills, online security, online health and well-being, AI and genAI skills, and transactional skills—and identify where blind spots are largest (high confidence but low knowledge or performance). This enables them to prioritize which groups need support on which skills, design tailored interventions (e.g., focused workshops or campaigns), and monitor over time whether these efforts are closing digital competence gaps.
</div>

## Demographics

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Load styled table objects

table_obj_1 <- readRDS('table_obj_1.rds')
table_obj_2 <- readRDS('table_obj_2.rds')
table_obj_3 <- readRDS('table_obj_3.rds')
table_obj_4 <- readRDS('table_obj_4.rds')
table_obj_5 <- readRDS('table_obj_5.rds')
table_obj_6 <- readRDS('table_obj_6.rds')
table_obj_7 <- readRDS('table_obj_7.rds')
table_obj_8 <- readRDS('table_obj_8.rds')
table_obj_9 <- readRDS('table_obj_9.rds')
table_obj_10 <- readRDS('table_obj_10.rds')
table_obj_11 <- readRDS('table_obj_11.rds')
table_obj_12 <- readRDS('table_obj_12.rds')

# Load ggplot2 objects

ggplot_obj_1 <- readRDS('ggplot_obj_1.rds')

```


**N = 2,417 | Mean age: 45.2**


### Age Group


```{r}
#| echo: false

table_obj_1
```


### Gender


```{r}
#| echo: false

table_obj_2
```


### Education Level


```{r}
#| echo: false

table_obj_3
```


### Migration Background


```{r}
#| echo: false

table_obj_4
```


### Panel Type


```{r}
#| echo: false

table_obj_5
```


### Use of Devices: Computer


```{r}
#| echo: false

table_obj_6
```


### Use of Devices: Tablet


```{r}
#| echo: false

table_obj_7
```


### Use of Devices: Phone


```{r}
#| echo: false

table_obj_8
```


### General Literacy


```{r}
#| echo: false

table_obj_9
```


### Work Status


```{r}
#| echo: false

table_obj_10
```


### Hours of Work with Computer (Employed Only)


```{r}
#| echo: false

table_obj_11
```


### Financial Insecurity


```{r}
#| echo: false

table_obj_12
```


## Correlations with Skills Knowledge and Performance


```{r}
#| echo: false
#| fig-height: 12
#| fig-width: 14

ggplot_obj_1
```

