---
title: "HI"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

```{=html}
<style>
/* Ensure chart containers expand to fit content - aggressive overrides */
.cell-output-display,
.cell-output,
.panel-tabset-tabby > .tab-content,
.panel-tabset > .tab-content,
.tab-pane,
.tab-pane.active,
.card-body,
.quarto-figure,
section {
  overflow: visible !important;
  height: auto !important;
  max-height: none !important;
}
/* Ensure highcharts containers respect their set height */
.highcharts-container,
.html-widget,
.htmlwidget {
  overflow: visible !important;
}
</style>
<script>
// Aggressive reflow for Highcharts - multiple attempts to catch widget initialization
(function() {
  function reflowCharts() {
    if (typeof Highcharts !== 'undefined' && Highcharts.charts) {
      Highcharts.charts.forEach(function(chart) {
        if (chart) {
          try { chart.reflow(); } catch(e) {}
        }
      });
    }
  }
  
  // Try multiple times at different intervals
  [0, 100, 250, 500, 1000, 2000].forEach(function(delay) {
    setTimeout(function() {
      window.dispatchEvent(new Event('resize'));
      requestAnimationFrame(reflowCharts);
    }, delay);
  });
  
  // Also reflow on any tab click
  document.addEventListener('click', function(e) {
    if (e.target.matches('.nav-link, [data-bs-toggle="tab"]')) {
      setTimeout(reflowCharts, 50);
    }
  });
})();
</script>
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

# Helper: convert haven_labelled columns to factors for filtering
.convert_haven <- function(df) {
  if (requireNamespace('haven', quietly = TRUE)) {
    for (col in names(df)) {
      if (inherits(df[[col]], 'haven_labelled')) {
        df[[col]] <- haven::as_factor(df[[col]])
      }
    }
  }
  df
}

data_filtered_984a0efe <- .convert_haven(data) %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- .convert_haven(data) %>% dplyr::filter(wave == 2)

```

## green


**Sustainable/Green Digital Competence** focuses on environmentally conscious technology use: reducing energy consumption, buying sustainable devices, recycling electronics, and understanding the environmental impact of digital activities.
[{{< iconify ph cards >}} See all Green Digital results](green_digital.html)


::: {.panel-tabset}

### wave1


::: {.panel-tabset}

##### overall


```{r green-wave1-overall}
# Sustainable/Green Digital Skills
result <- viz_stackedbars(
  data = data_filtered_984a0efe,
  title = "Sustainable/Green Digital Skills",
  x_vars = c("SEnv1", "SEnv2", "SEnv3"),
  x_var_labels = c("I know how to reduce the battery use of a phone or computer", "I know how I can buy a phone or computer in a \"green\" or sustainable way", "I know how to have a phone or computer recycled"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### age


::: {.panel-tabset}

###### item1


```{r green-wave1-age-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave1-age-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave1-age-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SEnv3"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r green-wave1-gender-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave1-gender-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave1-gender-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SEnv3"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r green-wave1-edu-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave1-edu-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave1-edu-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SEnv3"
)

result
```


:::


##### mig


::: {.panel-tabset}

###### item1


```{r green-wave1-mig-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave1-mig-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave1-mig-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_984a0efe,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SEnv3"
)

result
```


:::


:::


### wave2


::: {.panel-tabset}

##### overall


```{r green-wave2-overall}
# Sustainable/Green Digital Skills
result <- viz_stackedbars(
  data = data_filtered_4af682fd,
  title = "Sustainable/Green Digital Skills",
  x_vars = c("SEnv1", "SEnv2", "SEnv3"),
  x_var_labels = c("I know how to reduce the battery use of a phone or computer", "I know how I can buy a phone or computer in a \"green\" or sustainable way", "I know how to have a phone or computer recycled"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### age


::: {.panel-tabset}

###### item1


```{r green-wave2-age-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave2-age-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave2-age-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  x_label = "Age",
  stack_var = "SEnv3"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r green-wave2-gender-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave2-gender-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave2-gender-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  x_label = "Gender",
  stack_var = "SEnv3"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r green-wave2-edu-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave2-edu-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave2-edu-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  x_label = "Education",
  stack_var = "SEnv3"
)

result
```


:::


##### mig


::: {.panel-tabset}

###### item1


```{r green-wave2-mig-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to reduce the battery use of a phone or computer",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SEnv1"
)

result
```


###### item2


```{r green-wave2-mig-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SEnv2"
)

result
```


###### item3


```{r green-wave2-mig-item3}
# I know how to have a phone or computer recycled
result <- viz_stackedbar(
  data = data_filtered_4af682fd,
  title = "I know how to have a phone or computer recycled",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) True (4-5)", "Not true and not untrue (3)", "(Completely) Untrue (1-2)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  x_label = "Migration Background",
  stack_var = "SEnv3"
)

result
```


:::


:::


### overtime


::: {.panel-tabset}

##### overall


::: {.panel-tabset}

###### item1


```{r green-overtime-overall-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv1"
)

result
```


###### item2


```{r green-overtime-overall-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv2"
)

result
```


###### item3


```{r green-overtime-overall-item3}
# I know how to have a phone or computer recycled
result <- viz_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  y_filter_label = "Percentage of Respondents",
  y_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv3"
)

result
```


:::


##### age


::: {.panel-tabset}

###### item1


```{r green-overtime-age-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv1",
  group_var = "AgeGroup"
)

result
```


###### item2


```{r green-overtime-age-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv2",
  group_var = "AgeGroup"
)

result
```


###### item3


```{r green-overtime-age-item3}
# I know how to have a phone or computer recycled
result <- viz_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv3",
  group_var = "AgeGroup"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r green-overtime-gender-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv1",
  group_var = "geslacht"
)

result
```


###### item2


```{r green-overtime-gender-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv2",
  group_var = "geslacht"
)

result
```


###### item3


```{r green-overtime-gender-item3}
# I know how to have a phone or computer recycled
result <- viz_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv3",
  group_var = "geslacht"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r green-overtime-edu-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv1",
  group_var = "Education"
)

result
```


###### item2


```{r green-overtime-edu-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv2",
  group_var = "Education"
)

result
```


###### item3


```{r green-overtime-edu-item3}
# I know how to have a phone or computer recycled
result <- viz_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv3",
  group_var = "Education"
)

result
```


:::


##### mig


::: {.panel-tabset}

###### item1


```{r green-overtime-mig-item1}
# I know how to reduce the battery use of a phone or computer
result <- viz_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv1",
  group_var = "MigrationBackground"
)

result
```


###### item2


```{r green-overtime-mig-item2}
# I know how I can buy a phone or computer in a "green" or sustainable way
result <- viz_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a \"green\" or sustainable way",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv2",
  group_var = "MigrationBackground"
)

result
```


###### item3


```{r green-overtime-mig-item3}
# I know how to have a phone or computer recycled
result <- viz_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled",
  time_var = "wave_time_label",
  chart_type = "line",
  y_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage of Respondents",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  y_var = "SEnv3",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

