---
title: "{{< iconify ph heart-fill >}} Digital Health"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

**Digital Health & Wellbeing** skills relate to managing healthy digital habits: controlling screen time, minimizing distractions, taking digital breaks, and understanding how technology affects sleep and wellbeing.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{=html}

<style>
/* Chart Lazy Loading Styles */
.chart-lazy {
  position: relative;
  min-height: 400px;
  margin: 1rem 0;
}

.chart-skeleton {
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  display: flex;
  align-items: center;
  justify-content: center;
  flex-direction: column;
  gap: 1rem;
  transition: opacity 0.3s ease;
}

.chart-spinner {
  width: 40px;
  height: 40px;
  border-radius: 50%;
  animation: spin 1s linear infinite;
}

@keyframes spin {
  to { transform: rotate(360deg); }
}

.chart-loading-text {
  font-size: 0.9rem;
  font-weight: 500;
  letter-spacing: 0.5px;
}

/* Theme: Light */
.chart-skeleton.theme-light {
  background: rgba(255, 255, 255, 0.95);
  border: 1px solid rgba(0, 0, 0, 0.05);
  border-radius: 12px;
  box-shadow: 0 4px 12px rgba(0, 0, 0, 0.05);
}

.chart-skeleton.theme-light .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.2);
  border-top-color: rgba(15, 23, 42, 0.8);
}

.chart-skeleton.theme-light .chart-loading-text {
  color: rgba(15, 23, 42, 0.7);
}

/* Theme: Glass */
.chart-skeleton.theme-glass {
  background: rgba(255, 255, 255, 0.25);
  backdrop-filter: blur(16px);
  border: 1px solid rgba(255, 255, 255, 0.4);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.08);
}

.chart-skeleton.theme-glass .chart-spinner {
  border: 3px solid rgba(255, 255, 255, 0.3);
  border-top-color: rgba(15, 23, 42, 0.7);
}

.chart-skeleton.theme-glass .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}

/* Theme: Dark */
.chart-skeleton.theme-dark {
  background: rgba(15, 23, 42, 0.95);
  border: 1px solid rgba(255, 255, 255, 0.1);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.3);
}

.chart-skeleton.theme-dark .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.3);
  border-top-color: rgba(255, 255, 255, 0.9);
}

.chart-skeleton.theme-dark .chart-loading-text {
  color: rgba(255, 255, 255, 0.9);
}

/* Theme: Accent */
.chart-skeleton.theme-accent {
  background: rgba(255, 255, 255, 0.98);
  border: 1px solid rgba(59, 130, 246, 0.15);
  border-radius: 12px;
  box-shadow: 0 4px 20px rgba(59, 130, 246, 0.15);
}

.chart-skeleton.theme-accent .chart-spinner {
  border: 3px solid rgba(59, 130, 246, 0.2);
  border-top-color: rgba(59, 130, 246, 0.9);
}

.chart-skeleton.theme-accent .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}
</style>

<script>
// Chart Lazy Loading System
(function() {
  const THEME = 'light';
  const DEBUG = false;
  
  // Track which charts have been initialized
  const initializedCharts = new Set();
  
  // Queue of charts waiting to be initialized
  const chartQueue = [];
  let isProcessingQueue = false;
  
  // Performance tracking
  let totalChartsLoaded = 0;
  let totalLoadTime = 0;
  const chartTimings = [];
  
  // Create skeleton loader dynamically
  function createSkeleton(container) {
    const skeleton = document.createElement('div');
    skeleton.className = 'chart-skeleton theme-' + THEME;
    skeleton.innerHTML = `
      <div class="chart-spinner"></div>
      <div class="chart-loading-text">Loading visualization...</div>
    `;
    container.appendChild(skeleton);
    return skeleton;
  }
  
  // Initialize a single chart
  function initChart(container) {
    const chartId = container.id;
    if (initializedCharts.has(chartId)) return;
    
    const startTime = DEBUG ? performance.now() : 0;
    
    initializedCharts.add(chartId);
    container.dataset.loaded = 'true';
    
    // Remove skeleton loader
    const skeleton = container.querySelector('.chart-skeleton');
    if (skeleton) {
      skeleton.style.opacity = '0';
      setTimeout(() => skeleton.remove(), 300);
    }
    
    // Trigger Highcharts reflow if present
    setTimeout(() => {
      if (window.Highcharts) {
        Highcharts.charts.forEach(chart => {
          if (chart && chart.reflow) chart.reflow();
        });
      }
      
      // Debug logging
      if (DEBUG) {
        const loadTime = performance.now() - startTime;
        totalChartsLoaded++;
        totalLoadTime += loadTime;
        chartTimings.push({ id: chartId, time: loadTime });
        
        console.log(`📊 Chart loaded: ${chartId} (${loadTime.toFixed(2)}ms)`);
        console.log(`   Total: ${totalChartsLoaded} charts, Avg: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
      }
    }, 50);
  }
  
  // Process chart queue in batches
  function processQueue() {
    if (isProcessingQueue || chartQueue.length === 0) return;
    
    isProcessingQueue = true;
    const batchSize = 3;
    const batch = chartQueue.splice(0, batchSize);
    
    if (DEBUG) {
      console.log(`⚡ Processing batch of ${batch.length} charts (${chartQueue.length} remaining)`);
    }
    
    batch.forEach(container => initChart(container));
    
    if (chartQueue.length > 0) {
      requestIdleCallback(() => {
        isProcessingQueue = false;
        processQueue();
      }, { timeout: 2000 });
    } else {
      isProcessingQueue = false;
      
      if (DEBUG && totalChartsLoaded > 0) {
        console.log(`✅ All charts loaded! Summary:`);
        console.log(`   Total charts: ${totalChartsLoaded}`);
        console.log(`   Total time: ${totalLoadTime.toFixed(2)}ms`);
        console.log(`   Average time per chart: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
        console.log(`   Slowest chart: ${Math.max(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
        console.log(`   Fastest chart: ${Math.min(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
      }
    }
  }
  
  // Intersection Observer for scroll-based lazy loading
  const observer = new IntersectionObserver((entries) => {
    entries.forEach(entry => {
      if (entry.isIntersecting && entry.target.dataset.loaded === 'false') {
        chartQueue.push(entry.target);
        observer.unobserve(entry.target);
        processQueue();
      }
    });
  }, { rootMargin: '200px' });
  
  // Initialize observers when DOM is ready
  function initLazyLoading() {
    document.querySelectorAll('.chart-lazy[data-loaded="false"]').forEach(container => {
      // Create skeleton for each lazy chart
      createSkeleton(container);
      // Start observing
      observer.observe(container);
    });
  }
  
  // Tab-aware rendering: load charts when tab becomes visible
  function initTabAwareLoading() {
    document.querySelectorAll('.panel-tabset').forEach(tabset => {
      const tabs = tabset.querySelectorAll('[role="tab"]');
      
      tabs.forEach(tab => {
        tab.addEventListener('click', function() {
          setTimeout(() => {
            const targetId = this.getAttribute('aria-controls');
            if (!targetId) return;
            
            const targetPanel = document.getElementById(targetId);
            if (!targetPanel) return;
            
            // Initialize any lazy charts in this tab
            const lazyCharts = targetPanel.querySelectorAll('.chart-lazy[data-loaded="false"]');
            lazyCharts.forEach(chart => {
              chartQueue.push(chart);
              observer.unobserve(chart);
            });
            processQueue();
          }, 50);
        });
      });
    });
  }
  
  // Start lazy loading when document is ready
  if (document.readyState === 'loading') {
    document.addEventListener('DOMContentLoaded', function() {
      initLazyLoading();
      initTabAwareLoading();
    });
  } else {
    initLazyLoading();
    initTabAwareLoading();
  }
})();
</script>

```

## {{< iconify ph lightning-fill >}} Digital Health Skills


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r dhealth-wave1-overall-2}
# Digital Health and Wellbeing Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SHealth1, SHealth2_V2, SHealth3_V2),
  title = "Digital Health and Wellbeing Skills",
  questions = c("SHealth1", "SHealth2_V2", "SHealth3_V2"),
  question_labels = c("I know how to control how much time I spend on the internet.", "I know how to make sure my phone does not distract me.", "I know how I can stop using my phone and computer for a while, if I want to."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-age-item1-2}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-age-item2-2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-age-item3-2}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-gender-item1-2}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-gender-item2-2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-gender-item3-2}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-edu-item1-2}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-edu-item2-2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-edu-item3-2}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth3_V2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r dhealth-wave2-overall-2}
# Digital Health and Wellbeing Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SHealth1, SHealth2_V2, SHealth3_V2),
  title = "Digital Health and Wellbeing Skills",
  questions = c("SHealth1", "SHealth2_V2", "SHealth3_V2"),
  question_labels = c("I know how to control how much time I spend on the internet.", "I know how to make sure my phone does not distract me.", "I know how I can stop using my phone and computer for a while, if I want to."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-age-item1-2}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-age-item2-2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-age-item3-2}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-gender-item1-2}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-gender-item2-2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-gender-item3-2}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-edu-item1-2}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-edu-item2-2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-edu-item3-2}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth3_V2"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-overall-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-overall-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-overall-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-age-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-age-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth2_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-age-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth3_V2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-gender-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-gender-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth2_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-gender-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth3_V2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-edu-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-edu-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth2_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-edu-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SHealth3_V2",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph book-open-fill >}} Health Knowledge


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don't know, please choose 'I don't know'. You don't have to guess. If you don't understand the question, please choose 'I don't understand the question.' Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r khealth-wave1-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KHealth2RC, KHealth3RC),
  title = "",
  questions = c("KHealth2RC", "KHealth3RC"),
  question_labels = c("Platforms like YouTube or Netflix are designed to keep people watching as long as possible.", "You sleep worse if you use a smartphone or computer just before you go to bed."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-wave1-age-item1-2}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-wave1-age-item2-2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth3RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-wave1-gender-item1-2}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-wave1-gender-item2-2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth3RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-wave1-edu-item1-2}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-wave1-edu-item2-2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth3RC"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don't know, please choose 'I don't know'. You don't have to guess. If you don't understand the question, please choose 'I don't understand the question.' Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r khealth-wave2-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KHealth2RC, KHealth3RC),
  title = "",
  questions = c("KHealth2RC", "KHealth3RC"),
  question_labels = c("Platforms like YouTube or Netflix are designed to keep people watching as long as possible.", "You sleep worse if you use a smartphone or computer just before you go to bed."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-wave2-age-item1-2}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-wave2-age-item2-2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth3RC"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-wave2-gender-item1-2}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-wave2-gender-item2-2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth3RC"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-wave2-edu-item1-2}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-wave2-edu-item2-2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth3RC"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-overtime-overall-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-overtime-overall-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-overtime-age-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-overtime-age-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-overtime-gender-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-overtime-gender-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r khealth-overtime-edu-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r khealth-overtime-edu-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph clipboard-text >}} Health Performance


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r perf-health-wave1-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PDHWS1_1, PDHWS1_2, PDHWS1_3, PDHWS1_4, PDHWS1_5, PDHWS1_6, PDHWS1_7),
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-age-item1-2}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-age-item2-2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-age-item3-2}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-age-item4-2}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-age-item5-2}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-age-item6-2}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-age-item7-2}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-gender-item1-2}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-gender-item2-2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-gender-item3-2}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-gender-item4-2}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-gender-item5-2}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-gender-item6-2}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-gender-item7-2}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-edu-item1-2}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-edu-item2-2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-edu-item3-2}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-edu-item4-2}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-edu-item5-2}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-edu-item6-2}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-edu-item7-2}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_7"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r perf-health-wave2-overall-2}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PDHWS1_1, PDHWS1_2, PDHWS1_3, PDHWS1_4, PDHWS1_5, PDHWS1_6, PDHWS1_7),
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-age-item1-2}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-age-item2-2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-age-item3-2}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-age-item4-2}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-age-item5-2}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-age-item6-2}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-age-item7-2}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-gender-item1-2}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-gender-item2-2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-gender-item3-2}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-gender-item4-2}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-gender-item5-2}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-gender-item6-2}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-gender-item7-2}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-edu-item1-2}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-edu-item2-2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-edu-item3-2}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-edu-item4-2}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-edu-item5-2}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-edu-item6-2}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-edu-item7-2}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_7"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-overall-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-overall-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-overall-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-overall-item4-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-overall-item5-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-overall-item6-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-overall-item7-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-age-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-age-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-age-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-age-item4-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-age-item5-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-age-item6-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-age-item7-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-gender-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-gender-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-gender-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-gender-item4-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-gender-item5-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-gender-item6-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-gender-item7-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-edu-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-edu-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-edu-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-edu-item4-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-edu-item5-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-edu-item6-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-edu-item7-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

