---
title: "{{< iconify ph star-fill >}} Highlights"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

<div style='text-align: justify;'>
### Wave 1
Based on data from **2,417** Dutch people aged between **10 and 94**, we drew the following conclusions:

1. {{< iconify ph device-mobile-camera-fill >}} **People generally feel digitally skilled, and this largely corresponds with their knowledge, but not always with their performance.**
   For some skills, such as online health and well-being, or netiquette, there are discrepancies between people's high scores on trust in their own skills and low scores on performance and behavior.
   These findings may indicate that Dutch people have blind spots regarding (some) digital skills and are unaware of what is possible online and where they actually lack skills.

2. {{< iconify ph sparkles-fill >}} **Skills and knowledge in the field of (gen)AI are low.**
   Children, the elderly, and low-educated Dutch people score low on knowledge about the privacy, validity, and reliability of genAI and the personalization of news and entertainment by AI, and are not well-equipped to create prompts that leverage the benefits of genAI.
   People perform poorly in recognizing and using genAI, and, aside from social media, don't always know which apps or websites use AI to tailor content to them.

3. {{< iconify ph users-three-fill >}} **Differences among Dutch people can be distinguished based on age and education level, not on migration background.**
   Children (10–14 years old), the elderly (66+), and the less educated score lower on digital skills and knowledge.
</div>

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```

## genai


**Generative AI Skills** measure competencies with AI tools like ChatGPT: knowing how to verify AI-generated information, writing effective prompts, detecting AI-generated content, and understanding GenAI's capabilities and limitations.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Gen AI results](gen_ai.html)


::: {.panel-tabset}

### wave1


::: {.panel-tabset}

##### overall


```{r genai-wave1-overall-2}
# GenAI Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SGAI1, SGAI2, SGAI3),
  title = "GenAI Skills",
  questions = c("SGAI1", "SGAI2", "SGAI3"),
  question_labels = c("I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.", "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.", "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### age


::: {.panel-tabset}

###### item1


```{r genai-wave1-age-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave1-age-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave1-age-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI3"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r genai-wave1-gender-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave1-gender-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave1-gender-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI3"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r genai-wave1-edu-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave1-edu-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave1-edu-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI3"
)

result
```


:::


##### mig


::: {.panel-tabset}

###### item1


```{r genai-wave1-mig-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave1-mig-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave1-mig-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SGAI3"
)

result
```


:::


:::


### wave2


::: {.panel-tabset}

##### overall


```{r genai-wave2-overall-2}
# GenAI Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SGAI1, SGAI2, SGAI3),
  title = "GenAI Skills",
  questions = c("SGAI1", "SGAI2", "SGAI3"),
  question_labels = c("I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.", "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.", "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### age


::: {.panel-tabset}

###### item1


```{r genai-wave2-age-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave2-age-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave2-age-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI3"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r genai-wave2-gender-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave2-gender-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave2-gender-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI3"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r genai-wave2-edu-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave2-edu-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave2-edu-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI3"
)

result
```


:::


##### mig


::: {.panel-tabset}

###### item1


```{r genai-wave2-mig-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave2-mig-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SGAI2),
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave2-mig-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SGAI3"
)

result
```


:::


:::


### overtime


::: {.panel-tabset}

##### overall


::: {.panel-tabset}

###### item1


```{r genai-overtime-overall-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_timeline(
  data = data,
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SGAI1"
)

result
```


###### item2


```{r genai-overtime-overall-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_timeline(
  data = data,
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SGAI2"
)

result
```


###### item3


```{r genai-overtime-overall-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_timeline(
  data = data,
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SGAI3"
)

result
```


:::


##### age


::: {.panel-tabset}

###### item1


```{r genai-overtime-age-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_timeline(
  data = data,
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI1",
  group_var = "AgeGroup"
)

result
```


###### item2


```{r genai-overtime-age-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_timeline(
  data = data,
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI2",
  group_var = "AgeGroup"
)

result
```


###### item3


```{r genai-overtime-age-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_timeline(
  data = data,
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI3",
  group_var = "AgeGroup"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r genai-overtime-gender-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_timeline(
  data = data,
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI1",
  group_var = "geslacht"
)

result
```


###### item2


```{r genai-overtime-gender-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_timeline(
  data = data,
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI2",
  group_var = "geslacht"
)

result
```


###### item3


```{r genai-overtime-gender-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_timeline(
  data = data,
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI3",
  group_var = "geslacht"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r genai-overtime-edu-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_timeline(
  data = data,
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI1",
  group_var = "Education"
)

result
```


###### item2


```{r genai-overtime-edu-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_timeline(
  data = data,
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI2",
  group_var = "Education"
)

result
```


###### item3


```{r genai-overtime-edu-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_timeline(
  data = data,
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI3",
  group_var = "Education"
)

result
```


:::


##### mig


::: {.panel-tabset}

###### item1


```{r genai-overtime-mig-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_timeline(
  data = data,
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI1",
  group_var = "MigrationBackground"
)

result
```


###### item2


```{r genai-overtime-mig-item2-2}
# I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_timeline(
  data = data,
  title = "I know which questions (or 'prompts') I should ask GenAI, such as ChatGPT, to receive a useful result.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI2",
  group_var = "MigrationBackground"
)

result
```


###### item3


```{r genai-overtime-mig-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_timeline(
  data = data,
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SGAI3",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

