---
title: "{{< iconify ph target >}} Highlights"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

If you’ve spent time around anyone under 25 lately, you’ve probably heard phrases like “I’ll just ask Chat” or “ChatGPT can do that faster.” Generative AI tools have quickly become part of everyday life for young people in the Netherlands. Whether for homework, social media posts, or just curiosity, Gen Z and even Gen Alpha are driving the adoption of these technologies at an astonishing pace.

The flood of AI-generated images, videos, and memes means it’s almost impossible to grow up today without encountering artificial intelligence. For many, AI isn’t a futuristic concept: it’s a daily companion. Young people now turn to tools like ChatGPT for information, writing help, and even casual conversation. This has been documented in the [Dutch AI Opinion Monitor](https://monitor.algosoc.nl/engagement.html), which shows that young people are the fastest adopters of this technology.


## The Confidence Boom
Our latest survey reflects this cultural shift. When asked how confident they felt using prompts to get useful responses from ChatGPT, a striking **71.2% of 16–25-year-olds** said they were confident. Even among those aged **10–15**, more than **half (54.4%)** expressed confidence in their ability to prompt AI effectively.

In other words, pre-teens today feel just as capable of “talking to AI” as many highly educated professionals in their thirties and forties. This growing sense of mastery highlights how intuitively young people adapt to new technologies. But confidence isn’t the same as competence.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4268obs.rds
data <- readRDS('dataset_4268obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{=html}

<style>
/* Chart Lazy Loading Styles */
.chart-lazy {
  position: relative;
  min-height: 400px;
  margin: 1rem 0;
}

.chart-skeleton {
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  display: flex;
  align-items: center;
  justify-content: center;
  flex-direction: column;
  gap: 1rem;
  transition: opacity 0.3s ease;
}

.chart-spinner {
  width: 40px;
  height: 40px;
  border-radius: 50%;
  animation: spin 1s linear infinite;
}

@keyframes spin {
  to { transform: rotate(360deg); }
}

.chart-loading-text {
  font-size: 0.9rem;
  font-weight: 500;
  letter-spacing: 0.5px;
}

/* Theme: Light */
.chart-skeleton.theme-light {
  background: rgba(255, 255, 255, 0.95);
  border: 1px solid rgba(0, 0, 0, 0.05);
  border-radius: 12px;
  box-shadow: 0 4px 12px rgba(0, 0, 0, 0.05);
}

.chart-skeleton.theme-light .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.2);
  border-top-color: rgba(15, 23, 42, 0.8);
}

.chart-skeleton.theme-light .chart-loading-text {
  color: rgba(15, 23, 42, 0.7);
}

/* Theme: Glass */
.chart-skeleton.theme-glass {
  background: rgba(255, 255, 255, 0.25);
  backdrop-filter: blur(16px);
  border: 1px solid rgba(255, 255, 255, 0.4);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.08);
}

.chart-skeleton.theme-glass .chart-spinner {
  border: 3px solid rgba(255, 255, 255, 0.3);
  border-top-color: rgba(15, 23, 42, 0.7);
}

.chart-skeleton.theme-glass .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}

/* Theme: Dark */
.chart-skeleton.theme-dark {
  background: rgba(15, 23, 42, 0.95);
  border: 1px solid rgba(255, 255, 255, 0.1);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.3);
}

.chart-skeleton.theme-dark .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.3);
  border-top-color: rgba(255, 255, 255, 0.9);
}

.chart-skeleton.theme-dark .chart-loading-text {
  color: rgba(255, 255, 255, 0.9);
}

/* Theme: Accent */
.chart-skeleton.theme-accent {
  background: rgba(255, 255, 255, 0.98);
  border: 1px solid rgba(59, 130, 246, 0.15);
  border-radius: 12px;
  box-shadow: 0 4px 20px rgba(59, 130, 246, 0.15);
}

.chart-skeleton.theme-accent .chart-spinner {
  border: 3px solid rgba(59, 130, 246, 0.2);
  border-top-color: rgba(59, 130, 246, 0.9);
}

.chart-skeleton.theme-accent .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}
</style>

<script>
// Chart Lazy Loading System
(function() {
  const THEME = 'light';
  const DEBUG = true;
  
  // Track which charts have been initialized
  const initializedCharts = new Set();
  
  // Queue of charts waiting to be initialized
  const chartQueue = [];
  let isProcessingQueue = false;
  
  // Performance tracking
  let totalChartsLoaded = 0;
  let totalLoadTime = 0;
  const chartTimings = [];
  
  // Create skeleton loader dynamically
  function createSkeleton(container) {
    const skeleton = document.createElement('div');
    skeleton.className = 'chart-skeleton theme-' + THEME;
    skeleton.innerHTML = `
      <div class="chart-spinner"></div>
      <div class="chart-loading-text">Loading visualization...</div>
    `;
    container.appendChild(skeleton);
    return skeleton;
  }
  
  // Initialize a single chart
  function initChart(container) {
    const chartId = container.id;
    if (initializedCharts.has(chartId)) return;
    
    const startTime = DEBUG ? performance.now() : 0;
    
    initializedCharts.add(chartId);
    container.dataset.loaded = 'true';
    
    // Remove skeleton loader
    const skeleton = container.querySelector('.chart-skeleton');
    if (skeleton) {
      skeleton.style.opacity = '0';
      setTimeout(() => skeleton.remove(), 300);
    }
    
    // Trigger Highcharts reflow if present
    setTimeout(() => {
      if (window.Highcharts) {
        Highcharts.charts.forEach(chart => {
          if (chart && chart.reflow) chart.reflow();
        });
      }
      
      // Debug logging
      if (DEBUG) {
        const loadTime = performance.now() - startTime;
        totalChartsLoaded++;
        totalLoadTime += loadTime;
        chartTimings.push({ id: chartId, time: loadTime });
        
        console.log(`📊 Chart loaded: ${chartId} (${loadTime.toFixed(2)}ms)`);
        console.log(`   Total: ${totalChartsLoaded} charts, Avg: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
      }
    }, 50);
  }
  
  // Process chart queue in batches
  function processQueue() {
    if (isProcessingQueue || chartQueue.length === 0) return;
    
    isProcessingQueue = true;
    const batchSize = 3;
    const batch = chartQueue.splice(0, batchSize);
    
    if (DEBUG) {
      console.log(`⚡ Processing batch of ${batch.length} charts (${chartQueue.length} remaining)`);
    }
    
    batch.forEach(container => initChart(container));
    
    if (chartQueue.length > 0) {
      requestIdleCallback(() => {
        isProcessingQueue = false;
        processQueue();
      }, { timeout: 2000 });
    } else {
      isProcessingQueue = false;
      
      if (DEBUG && totalChartsLoaded > 0) {
        console.log(`✅ All charts loaded! Summary:`);
        console.log(`   Total charts: ${totalChartsLoaded}`);
        console.log(`   Total time: ${totalLoadTime.toFixed(2)}ms`);
        console.log(`   Average time per chart: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
        console.log(`   Slowest chart: ${Math.max(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
        console.log(`   Fastest chart: ${Math.min(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
      }
    }
  }
  
  // Intersection Observer for scroll-based lazy loading
  const observer = new IntersectionObserver((entries) => {
    entries.forEach(entry => {
      if (entry.isIntersecting && entry.target.dataset.loaded === 'false') {
        chartQueue.push(entry.target);
        observer.unobserve(entry.target);
        processQueue();
      }
    });
  }, { rootMargin: '300px' });
  
  // Initialize observers when DOM is ready
  function initLazyLoading() {
    document.querySelectorAll('.chart-lazy[data-loaded="false"]').forEach(container => {
      // Create skeleton for each lazy chart
      createSkeleton(container);
      // Start observing
      observer.observe(container);
    });
  }
  
  // Tab-aware rendering: load charts when tab becomes visible
  function initTabAwareLoading() {
    document.querySelectorAll('.panel-tabset').forEach(tabset => {
      const tabs = tabset.querySelectorAll('[role="tab"]');
      
      tabs.forEach(tab => {
        tab.addEventListener('click', function() {
          setTimeout(() => {
            const targetId = this.getAttribute('aria-controls');
            if (!targetId) return;
            
            const targetPanel = document.getElementById(targetId);
            if (!targetPanel) return;
            
            // Initialize any lazy charts in this tab
            const lazyCharts = targetPanel.querySelectorAll('.chart-lazy[data-loaded="false"]');
            lazyCharts.forEach(chart => {
              chartQueue.push(chart);
              observer.unobserve(chart);
            });
            processQueue();
          }, 50);
        });
      });
    });
  }
  
  // Start lazy loading when document is ready
  if (document.readyState === 'loading') {
    document.addEventListener('DOMContentLoaded', function() {
      initLazyLoading();
      initTabAwareLoading();
    });
  } else {
    initLazyLoading();
    initTabAwareLoading();
  }
})();
</script>

```

## genai


::: {.panel-tabset}

### wave1


::: {.panel-tabset}

##### overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We’d like to know this. If you don’t understand what the question means, please choose ‘I don’t understand the question.’ Do you recognize yourself in the following statements?", preset = "question")
```

```{r genai-wave1-overall-2}
# GenAI Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SGAI1, SGAI2, SGAI3),
  title = "GenAI Skills",
  questions = c("SGAI1", "SGAI2", "SGAI3"),
  question_labels = c("I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.", "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.", "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### age


::: {.panel-tabset}

###### item1


```{r genai-wave1-age-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave1-age-item2-2}
# I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SGAI2),
  title = "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave1-age-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI3"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r genai-wave1-gender-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave1-gender-item2-2}
# I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SGAI2),
  title = "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave1-gender-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI3"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r genai-wave1-edu-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave1-edu-item2-2}
# I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SGAI2),
  title = "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave1-edu-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI3"
)

result
```


:::


:::


### wave2


::: {.panel-tabset}

##### overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We’d like to know this. If you don’t understand what the question means, please choose ‘I don’t understand the question.’ Do you recognize yourself in the following statements?", preset = "question")
```

```{r genai-wave2-overall-2}
# GenAI Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SGAI1, SGAI2, SGAI3),
  title = "GenAI Skills",
  questions = c("SGAI1", "SGAI2", "SGAI3"),
  question_labels = c("I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.", "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.", "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### age


::: {.panel-tabset}

###### item1


```{r genai-wave2-age-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave2-age-item2-2}
# I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SGAI2),
  title = "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave2-age-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SGAI3"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r genai-wave2-gender-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave2-gender-item2-2}
# I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SGAI2),
  title = "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave2-gender-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SGAI3"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r genai-wave2-edu-item1-2}
# I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SGAI1),
  title = "I usually know when the content created for me by GenAI, such as ChatGPT, contains correct information.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI1"
)

result
```


###### item2


```{r genai-wave2-edu-item2-2}
# I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SGAI2),
  title = "I know which questions (or “prompts”) I should ask GenAI, such as ChatGPT, to receive a useful result.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI2"
)

result
```


###### item3


```{r genai-wave2-edu-item3-2}
# I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SGAI3),
  title = "I know how to check whether a text or picture is created by GenAI, such as ChatGPT, instead of a person",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SGAI3"
)

result
```


:::


:::


### overtime


::: {.panel-tabset}

##### overall


::: {.panel-tabset}

###### item1


```{r genai-overtime-overall-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SGAI1"
)

result
```


###### item2


```{r genai-overtime-overall-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SGAI2"
)

result
```


###### item3


```{r genai-overtime-overall-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SGAI3"
)

result
```


:::


##### age


::: {.panel-tabset}

###### item1


```{r genai-overtime-age-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI1",
  group_var = "AgeGroup"
)

result
```


###### item2


```{r genai-overtime-age-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI2",
  group_var = "AgeGroup"
)

result
```


###### item3


```{r genai-overtime-age-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI3",
  group_var = "AgeGroup"
)

result
```


:::


##### gender


::: {.panel-tabset}

###### item1


```{r genai-overtime-gender-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI1",
  group_var = "geslacht"
)

result
```


###### item2


```{r genai-overtime-gender-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI2",
  group_var = "geslacht"
)

result
```


###### item3


```{r genai-overtime-gender-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI3",
  group_var = "geslacht"
)

result
```


:::


##### edu


::: {.panel-tabset}

###### item1


```{r genai-overtime-edu-item1-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI1",
  group_var = "Education"
)

result
```


###### item2


```{r genai-overtime-edu-item2-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI2",
  group_var = "Education"
)

result
```


###### item3


```{r genai-overtime-edu-item3-2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SGAI3",
  group_var = "Education"
)

result
```


:::


:::


:::

