---
title: "{{< iconify ph chart-line >}} Knowledge"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Knowledge** section measures what participants *know* about the digital world: how it works, what risks it involves, and how different technologies affect everyday life. These items test factual understanding across topics such as information reliability, communication and privacy, online safety, AI, and generative AI. Respondents indicate whether each statement is true or false (or if they don’t know), allowing us to assess their level of digital literacy and awareness beyond self-perceived skills.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4268obs.rds
data <- readRDS('dataset_4268obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify fluent-emoji-high-contrast detective >}} Creative Skills Knowledge


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r kcrea-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KCrea2RC, KCrea3RC),
  title = "",
  questions = c("KCrea2RC", "KCrea3RC"),
  question_labels = c("Some people are paid to use products in the videos they make.", "You can change and share existing videos, as long as you do not make money by doing it."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r kcrea-wave1-age-item1}
# Some people are paid to use products in the videos they make.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KCrea2RC),
  title = "Some people are paid to use products in the videos they make.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KCrea2RC"
)

result
```


###### Question 2


```{r kcrea-wave1-age-item2}
# You can change and share existing videos, as long as you do not make money by doing it.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KCrea3RC),
  title = "You can change and share existing videos, as long as you do not make money by doing it.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KCrea3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kcrea-wave1-gender-item1}
# Some people are paid to use products in the videos they make.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KCrea2RC),
  title = "Some people are paid to use products in the videos they make.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KCrea2RC"
)

result
```


###### Question 2


```{r kcrea-wave1-gender-item2}
# You can change and share existing videos, as long as you do not make money by doing it.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KCrea3RC),
  title = "You can change and share existing videos, as long as you do not make money by doing it.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KCrea3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kcrea-wave1-edu-item1}
# Some people are paid to use products in the videos they make.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KCrea2RC),
  title = "Some people are paid to use products in the videos they make.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KCrea2RC"
)

result
```


###### Question 2


```{r kcrea-wave1-edu-item2}
# You can change and share existing videos, as long as you do not make money by doing it.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KCrea3RC),
  title = "You can change and share existing videos, as long as you do not make money by doing it.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KCrea3RC"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r kcrea-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KCrea2RC, KCrea3RC),
  title = "",
  questions = c("KCrea2RC", "KCrea3RC"),
  question_labels = c("Some people are paid to use products in the videos they make.", "You can change and share existing videos, as long as you do not make money by doing it."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r kcrea-wave2-age-item1}
# Some people are paid to use products in the videos they make.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KCrea2RC),
  title = "Some people are paid to use products in the videos they make.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KCrea2RC"
)

result
```


###### Question 2


```{r kcrea-wave2-age-item2}
# You can change and share existing videos, as long as you do not make money by doing it.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KCrea3RC),
  title = "You can change and share existing videos, as long as you do not make money by doing it.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KCrea3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kcrea-wave2-gender-item1}
# Some people are paid to use products in the videos they make.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KCrea2RC),
  title = "Some people are paid to use products in the videos they make.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KCrea2RC"
)

result
```


###### Question 2


```{r kcrea-wave2-gender-item2}
# You can change and share existing videos, as long as you do not make money by doing it.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KCrea3RC),
  title = "You can change and share existing videos, as long as you do not make money by doing it.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KCrea3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kcrea-wave2-edu-item1}
# Some people are paid to use products in the videos they make.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KCrea2RC),
  title = "Some people are paid to use products in the videos they make.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KCrea2RC"
)

result
```


###### Question 2


```{r kcrea-wave2-edu-item2}
# You can change and share existing videos, as long as you do not make money by doing it.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KCrea3RC),
  title = "You can change and share existing videos, as long as you do not make money by doing it.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KCrea3RC"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r kcrea-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea2RC"
)

result
```


###### Question 2


```{r kcrea-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea3RC"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r kcrea-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea2RC",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r kcrea-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea3RC",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kcrea-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea2RC",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r kcrea-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea3RC",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kcrea-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea2RC",
  group_var = "Education"
)

result
```


###### Question 2


```{r kcrea-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCrea3RC",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Safety & Control of Devices Knowledge


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r ksafety-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KSafDev2RC, KPriv1RC, KPriv2RC),
  title = "",
  questions = c("KSafDev2RC", "KPriv1RC", "KPriv2RC"),
  question_labels = c("To keep your devices safer, you should always install updates immediately.", "It's best to have the same password for each account.", "What you do online is used by companies to advertise their products and services."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r ksafety-wave1-age-item1}
# To keep your devices safer, you should always install updates immediately.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KSafDev2RC),
  title = "To keep your devices safer, you should always install updates immediately.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KSafDev2RC"
)

result
```


###### Question 2


```{r ksafety-wave1-age-item2}
# It's best to have the same password for each account.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KPriv1RC),
  title = "It's best to have the same password for each account.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KPriv1RC"
)

result
```


###### Question 3


```{r ksafety-wave1-age-item3}
# What you do online is used by companies to advertise their products and services.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KPriv2RC),
  title = "What you do online is used by companies to advertise their products and services.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KPriv2RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r ksafety-wave1-gender-item1}
# To keep your devices safer, you should always install updates immediately.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KSafDev2RC),
  title = "To keep your devices safer, you should always install updates immediately.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KSafDev2RC"
)

result
```


###### Question 2


```{r ksafety-wave1-gender-item2}
# It's best to have the same password for each account.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KPriv1RC),
  title = "It's best to have the same password for each account.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KPriv1RC"
)

result
```


###### Question 3


```{r ksafety-wave1-gender-item3}
# What you do online is used by companies to advertise their products and services.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KPriv2RC),
  title = "What you do online is used by companies to advertise their products and services.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KPriv2RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r ksafety-wave1-edu-item1}
# To keep your devices safer, you should always install updates immediately.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KSafDev2RC),
  title = "To keep your devices safer, you should always install updates immediately.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KSafDev2RC"
)

result
```


###### Question 2


```{r ksafety-wave1-edu-item2}
# It's best to have the same password for each account.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KPriv1RC),
  title = "It's best to have the same password for each account.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KPriv1RC"
)

result
```


###### Question 3


```{r ksafety-wave1-edu-item3}
# What you do online is used by companies to advertise their products and services.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KPriv2RC),
  title = "What you do online is used by companies to advertise their products and services.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KPriv2RC"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r ksafety-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KSafDev2RC, KPriv1RC, KPriv2RC),
  title = "",
  questions = c("KSafDev2RC", "KPriv1RC", "KPriv2RC"),
  question_labels = c("To keep your devices safer, you should always install updates immediately.", "It's best to have the same password for each account.", "What you do online is used by companies to advertise their products and services."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r ksafety-wave2-age-item1}
# To keep your devices safer, you should always install updates immediately.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KSafDev2RC),
  title = "To keep your devices safer, you should always install updates immediately.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KSafDev2RC"
)

result
```


###### Question 2


```{r ksafety-wave2-age-item2}
# It's best to have the same password for each account.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KPriv1RC),
  title = "It's best to have the same password for each account.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KPriv1RC"
)

result
```


###### Question 3


```{r ksafety-wave2-age-item3}
# What you do online is used by companies to advertise their products and services.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KPriv2RC),
  title = "What you do online is used by companies to advertise their products and services.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KPriv2RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r ksafety-wave2-gender-item1}
# To keep your devices safer, you should always install updates immediately.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KSafDev2RC),
  title = "To keep your devices safer, you should always install updates immediately.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KSafDev2RC"
)

result
```


###### Question 2


```{r ksafety-wave2-gender-item2}
# It's best to have the same password for each account.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KPriv1RC),
  title = "It's best to have the same password for each account.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KPriv1RC"
)

result
```


###### Question 3


```{r ksafety-wave2-gender-item3}
# What you do online is used by companies to advertise their products and services.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KPriv2RC),
  title = "What you do online is used by companies to advertise their products and services.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KPriv2RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r ksafety-wave2-edu-item1}
# To keep your devices safer, you should always install updates immediately.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KSafDev2RC),
  title = "To keep your devices safer, you should always install updates immediately.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KSafDev2RC"
)

result
```


###### Question 2


```{r ksafety-wave2-edu-item2}
# It's best to have the same password for each account.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KPriv1RC),
  title = "It's best to have the same password for each account.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KPriv1RC"
)

result
```


###### Question 3


```{r ksafety-wave2-edu-item3}
# What you do online is used by companies to advertise their products and services.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KPriv2RC),
  title = "What you do online is used by companies to advertise their products and services.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KPriv2RC"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r ksafety-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC"
)

result
```


###### Question 2


```{r ksafety-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC"
)

result
```


###### Question 3


```{r ksafety-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r ksafety-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r ksafety-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC",
  group_var = "AgeGroup"
)

result
```


###### Question 3


```{r ksafety-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r ksafety-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r ksafety-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC",
  group_var = "geslacht"
)

result
```


###### Question 3


```{r ksafety-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r ksafety-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KSafDev2RC",
  group_var = "Education"
)

result
```


###### Question 2


```{r ksafety-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv1RC",
  group_var = "Education"
)

result
```


###### Question 3


```{r ksafety-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KPriv2RC",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Health & Wellbeing Knowledge


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r khealth-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KHealth2RC, KHealth3RC),
  title = "",
  questions = c("KHealth2RC", "KHealth3RC"),
  question_labels = c("Platforms like YouTube or Netflix are designed to keep people watching as long as possible.", "You sleep worse if you use a smartphone or computer just before you go to bed."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r khealth-wave1-age-item1}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth2RC"
)

result
```


###### Question 2


```{r khealth-wave1-age-item2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r khealth-wave1-gender-item1}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth2RC"
)

result
```


###### Question 2


```{r khealth-wave1-gender-item2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r khealth-wave1-edu-item1}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth2RC"
)

result
```


###### Question 2


```{r khealth-wave1-edu-item2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth3RC"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r khealth-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KHealth2RC, KHealth3RC),
  title = "",
  questions = c("KHealth2RC", "KHealth3RC"),
  question_labels = c("Platforms like YouTube or Netflix are designed to keep people watching as long as possible.", "You sleep worse if you use a smartphone or computer just before you go to bed."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r khealth-wave2-age-item1}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth2RC"
)

result
```


###### Question 2


```{r khealth-wave2-age-item2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KHealth3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r khealth-wave2-gender-item1}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth2RC"
)

result
```


###### Question 2


```{r khealth-wave2-gender-item2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KHealth3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r khealth-wave2-edu-item1}
# Platforms like YouTube or Netflix are designed to keep people watching as long as possible.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KHealth2RC),
  title = "Platforms like YouTube or Netflix are designed to keep people watching as long as possible.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth2RC"
)

result
```


###### Question 2


```{r khealth-wave2-edu-item2}
# You sleep worse if you use a smartphone or computer just before you go to bed.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KHealth3RC),
  title = "You sleep worse if you use a smartphone or computer just before you go to bed.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KHealth3RC"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r khealth-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC"
)

result
```


###### Question 2


```{r khealth-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r khealth-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r khealth-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r khealth-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r khealth-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r khealth-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth2RC",
  group_var = "Education"
)

result
```


###### Question 2


```{r khealth-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KHealth3RC",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Green / Sustainable Digital Knowledge


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r kgreen-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KEnv2RC, KEnv3RC),
  title = "",
  questions = c("KEnv2RC", "KEnv3RC"),
  question_labels = c("Phones contain materials that mineworkers extract from mines.", "The amount of data and WiFi you use does not affect CO2-emissions or the climate."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r kgreen-wave1-age-item1}
# Phones contain materials that mineworkers extract from mines.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KEnv2RC),
  title = "Phones contain materials that mineworkers extract from mines.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KEnv2RC"
)

result
```


###### Question 2


```{r kgreen-wave1-age-item2}
# The amount of data and WiFi you use does not affect CO2-emissions or the climate.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KEnv3RC),
  title = "The amount of data and WiFi you use does not affect CO2-emissions or the climate.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KEnv3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kgreen-wave1-gender-item1}
# Phones contain materials that mineworkers extract from mines.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KEnv2RC),
  title = "Phones contain materials that mineworkers extract from mines.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KEnv2RC"
)

result
```


###### Question 2


```{r kgreen-wave1-gender-item2}
# The amount of data and WiFi you use does not affect CO2-emissions or the climate.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KEnv3RC),
  title = "The amount of data and WiFi you use does not affect CO2-emissions or the climate.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KEnv3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kgreen-wave1-edu-item1}
# Phones contain materials that mineworkers extract from mines.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KEnv2RC),
  title = "Phones contain materials that mineworkers extract from mines.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KEnv2RC"
)

result
```


###### Question 2


```{r kgreen-wave1-edu-item2}
# The amount of data and WiFi you use does not affect CO2-emissions or the climate.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KEnv3RC),
  title = "The amount of data and WiFi you use does not affect CO2-emissions or the climate.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KEnv3RC"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r kgreen-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KEnv2RC, KEnv3RC),
  title = "",
  questions = c("KEnv2RC", "KEnv3RC"),
  question_labels = c("Phones contain materials that mineworkers extract from mines.", "The amount of data and WiFi you use does not affect CO2-emissions or the climate."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r kgreen-wave2-age-item1}
# Phones contain materials that mineworkers extract from mines.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KEnv2RC),
  title = "Phones contain materials that mineworkers extract from mines.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KEnv2RC"
)

result
```


###### Question 2


```{r kgreen-wave2-age-item2}
# The amount of data and WiFi you use does not affect CO2-emissions or the climate.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KEnv3RC),
  title = "The amount of data and WiFi you use does not affect CO2-emissions or the climate.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KEnv3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kgreen-wave2-gender-item1}
# Phones contain materials that mineworkers extract from mines.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KEnv2RC),
  title = "Phones contain materials that mineworkers extract from mines.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KEnv2RC"
)

result
```


###### Question 2


```{r kgreen-wave2-gender-item2}
# The amount of data and WiFi you use does not affect CO2-emissions or the climate.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KEnv3RC),
  title = "The amount of data and WiFi you use does not affect CO2-emissions or the climate.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KEnv3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kgreen-wave2-edu-item1}
# Phones contain materials that mineworkers extract from mines.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KEnv2RC),
  title = "Phones contain materials that mineworkers extract from mines.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KEnv2RC"
)

result
```


###### Question 2


```{r kgreen-wave2-edu-item2}
# The amount of data and WiFi you use does not affect CO2-emissions or the climate.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KEnv3RC),
  title = "The amount of data and WiFi you use does not affect CO2-emissions or the climate.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KEnv3RC"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r kgreen-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv2RC"
)

result
```


###### Question 2


```{r kgreen-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv3RC"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r kgreen-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv2RC",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r kgreen-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv3RC",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kgreen-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv2RC",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r kgreen-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv3RC",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kgreen-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv2RC",
  group_var = "Education"
)

result
```


###### Question 2


```{r kgreen-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KEnv3RC",
  group_var = "Education"
)

result
```


:::


:::


:::



```{=html}
<nav class='pagination-nav' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <a href='knowledge.html' class='pagination-btn pagination-prev' aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
    <div class='pagination-info'>
      <input type='number' class='pagination-input' id='page-input' min='1' max='3' value='2' aria-label='Current page'>
      <span class='pagination-separator'>/ 3</span>
    </div>
    <a href='knowledge_p3.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["knowledge.html","knowledge_p2.html","knowledge_p3.html"];
  const pageInput = document.getElementById('page-input');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```


```{=html}
<style>
/* Ultra-Minimal Pagination Navigation */
.pagination-nav {
  position: sticky;
  bottom: 2rem;
  margin: 3rem auto 2rem auto;
  max-width: 240px;
  z-index: 100;
}

.pagination-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 1rem;
  padding: 0.5rem 1rem;
  background: transparent;
}

.pagination-btn {
  display: flex;
  align-items: center;
  justify-content: center;
  width: 32px;
  height: 32px;
  padding: 0;
  background: transparent;
  color: var(--bs-secondary, #6c757d);
  text-decoration: none;
  border-radius: 0.375rem;
  transition: all 0.15s ease;
  border: none;
  cursor: pointer;
}

.pagination-btn:hover:not(.pagination-disabled) {
  background: var(--bs-light, #f8f9fa);
  color: var(--bs-body-color, #212529);
}

.pagination-btn:active:not(.pagination-disabled) {
  background: var(--bs-gray-200, #e9ecef);
}

.pagination-btn.pagination-disabled {
  color: var(--bs-gray-300, #dee2e6);
  cursor: default;
}

.pagination-icon {
  flex-shrink: 0;
  opacity: 0.7;
}

.pagination-btn:hover:not(.pagination-disabled) .pagination-icon {
  opacity: 1;
}

.pagination-info {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  font-size: 0.875rem;
  color: var(--bs-secondary, #6c757d);
}

.pagination-input {
  width: 2.5rem;
  padding: 0.25rem 0.5rem;
  text-align: center;
  border: 1px solid transparent;
  border-radius: 0.25rem;
  font-size: 0.875rem;
  font-weight: 500;
  color: var(--bs-body-color, #212529);
  background: transparent;
  transition: all 0.15s ease;
}

.pagination-input:hover {
  background: var(--bs-light, #f8f9fa);
  border-color: var(--bs-border-color, #dee2e6);
}

.pagination-input:focus {
  outline: none;
  background: var(--bs-body-bg, #fff);
  border-color: var(--bs-primary, #0d6efd);
  box-shadow: 0 0 0 2px rgba(13, 110, 253, 0.1);
}

.pagination-input::-webkit-inner-spin-button,
.pagination-input::-webkit-outer-spin-button {
  opacity: 0;
}

.pagination-separator {
  color: var(--bs-secondary, #6c757d);
  font-weight: 400;
  font-size: 0.875rem;
}

/* Responsive */
@media (max-width: 768px) {
  .pagination-nav {
    max-width: 220px;
    bottom: 1.5rem;
  }
  
  .pagination-container {
    gap: 0.75rem;
    padding: 0.4rem 0.75rem;
  }
  
  .pagination-btn {
    width: 30px;
    height: 30px;
  }
  
  .pagination-icon {
    width: 16px;
    height: 16px;
  }
  
  .pagination-info {
    font-size: 0.8rem;
  }
  
  .pagination-input {
    width: 2.25rem;
    font-size: 0.8rem;
  }
}

@media (max-width: 480px) {
  .pagination-nav {
    max-width: 200px;
  }
  
  .pagination-btn {
    width: 28px;
    height: 28px;
  }
}

/* Dark mode support */
@media (prefers-color-scheme: dark) {
  .pagination-btn:hover:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.05);
  }
  
  .pagination-btn:active:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.1);
  }
  
  .pagination-input:hover {
    background: rgba(255, 255, 255, 0.05);
  }
}

/* Override Quarto's back-to-top button position */
.back-to-top {
  right: 2rem !important;
  left: auto !important;
}

@media (max-width: 768px) {
  .back-to-top {
    right: 1rem !important;
  }
}
</style>
```

