---
title: "{{< iconify ph chart-line >}} Knowledge"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Knowledge** section measures what participants *know* about the digital world: how it works, what risks it involves, and how different technologies affect everyday life. These items test factual understanding across topics such as information reliability, communication and privacy, online safety, AI, and generative AI. Respondents indicate whether each statement is true or false (or if they don’t know), allowing us to assess their level of digital literacy and awareness beyond self-perceived skills.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4268obs.rds
data <- readRDS('dataset_4268obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph chart-line >}} Knowledge Score


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r knowledge-wave1-overall}
# Knowledge Scores
result <- create_bar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MeanKnowledge),
  title = "Knowledge Scores",
  horizontal = TRUE,
  bar_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "MeanKnowledge",
  x_breaks = c(0, 10, 20, 30),
  x_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  x_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)")
)

result
```


##### Age


```{r knowledge-wave1-age}
# Knowledge Score
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, MeanKnowledge),
  title = "Knowledge Score",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  stack_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  weight_var = "weging_GAMO",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  x_var = "AgeGroup",
  stack_var = "MeanKnowledge"
)

result
```


##### Gender


```{r knowledge-wave1-gender}
# Knowledge Score
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, MeanKnowledge),
  title = "Knowledge Score",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  stack_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  weight_var = "weging_GAMO",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  x_var = "geslacht",
  stack_var = "MeanKnowledge"
)

result
```


##### Education


```{r knowledge-wave1-edu}
# Knowledge Score
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, MeanKnowledge),
  title = "Knowledge Score",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  stack_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  weight_var = "weging_GAMO",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  x_var = "Education",
  stack_var = "MeanKnowledge"
)

result
```


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r knowledge-wave2-overall}
# Knowledge Scores
result <- create_bar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MeanKnowledge),
  title = "Knowledge Scores",
  horizontal = TRUE,
  bar_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "MeanKnowledge",
  x_breaks = c(0, 10, 20, 30),
  x_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  x_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)")
)

result
```


##### Age


```{r knowledge-wave2-age}
# Knowledge Score
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, MeanKnowledge),
  title = "Knowledge Score",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  stack_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  weight_var = "weging_GAMO",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  x_var = "AgeGroup",
  stack_var = "MeanKnowledge"
)

result
```


##### Gender


```{r knowledge-wave2-gender}
# Knowledge Score
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, MeanKnowledge),
  title = "Knowledge Score",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  stack_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  weight_var = "weging_GAMO",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  x_var = "geslacht",
  stack_var = "MeanKnowledge"
)

result
```


##### Education


```{r knowledge-wave2-edu}
# Knowledge Score
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, MeanKnowledge),
  title = "Knowledge Score",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  stack_order = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  weight_var = "weging_GAMO",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  x_var = "Education",
  stack_var = "MeanKnowledge"
)

result
```


:::


### Over Time


::: {.panel-tabset}

##### Overall


```{r knowledge-overtime-overall}
# Knowledge Scores Over Time
result <- create_timeline(
  data = data %>% tidyr::drop_na(MeanKnowledge, wave_time_label),
  title = "Knowledge Scores Over Time",
  time_var = "wave_time_label",
  chart_type = "line",
  response_var = "MeanKnowledge",
  response_breaks = c(0, 10, 20, 30),
  response_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  weight_var = "weging_GAMO"
)

result
```


##### Age


```{r knowledge-overtime-age}
# timeline visualization
result <- create_timeline(
  data = data %>% tidyr::drop_na(MeanKnowledge, AgeGroup, wave_time_label),
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_var = "MeanKnowledge",
  response_breaks = c(0, 10, 20, 30),
  response_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  group_var = "AgeGroup"
)

result
```


##### Gender


```{r knowledge-overtime-gender}
# timeline visualization
result <- create_timeline(
  data = data %>% tidyr::drop_na(MeanKnowledge, geslacht, wave_time_label),
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_var = "MeanKnowledge",
  response_breaks = c(0, 10, 20, 30),
  response_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  group_var = "geslacht"
)

result
```


##### Education


```{r knowledge-overtime-edu}
# timeline visualization
result <- create_timeline(
  data = data %>% tidyr::drop_na(MeanKnowledge, Education, wave_time_label),
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_var = "MeanKnowledge",
  response_breaks = c(0, 10, 20, 30),
  response_bin_labels = c("Low (0-9)", "Middle (10-19)", "High (20-29)"),
  group_var = "Education"
)

result
```


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Strategic Information Knowledge


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r kinfo-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KInfo1RC, KInfo2RC),
  title = "",
  questions = c("KInfo1RC", "KInfo2RC"),
  question_labels = c("The first search result is always the best information source.", "Everyone gets the same information when they search for the same things online."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r kinfo-wave1-age-item1}
# The first search result is always the best information source.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KInfo1RC),
  title = "The first search result is always the best information source.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KInfo1RC"
)

result
```


###### Question 2


```{r kinfo-wave1-age-item2}
# Everyone gets the same information when they search for the same things online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KInfo2RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kinfo-wave1-gender-item1}
# The first search result is always the best information source.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KInfo1RC),
  title = "The first search result is always the best information source.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KInfo1RC"
)

result
```


###### Question 2


```{r kinfo-wave1-gender-item2}
# Everyone gets the same information when they search for the same things online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KInfo2RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kinfo-wave1-edu-item1}
# The first search result is always the best information source.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KInfo1RC),
  title = "The first search result is always the best information source.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KInfo1RC"
)

result
```


###### Question 2


```{r kinfo-wave1-edu-item2}
# Everyone gets the same information when they search for the same things online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KInfo2RC"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r kinfo-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KInfo1RC, KInfo2RC),
  title = "",
  questions = c("KInfo1RC", "KInfo2RC"),
  question_labels = c("The first search result is always the best information source.", "Everyone gets the same information when they search for the same things online."),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r kinfo-wave2-age-item1}
# The first search result is always the best information source.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KInfo1RC),
  title = "The first search result is always the best information source.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KInfo1RC"
)

result
```


###### Question 2


```{r kinfo-wave2-age-item2}
# Everyone gets the same information when they search for the same things online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KInfo2RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kinfo-wave2-gender-item1}
# The first search result is always the best information source.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KInfo1RC),
  title = "The first search result is always the best information source.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KInfo1RC"
)

result
```


###### Question 2


```{r kinfo-wave2-gender-item2}
# Everyone gets the same information when they search for the same things online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KInfo2RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kinfo-wave2-edu-item1}
# The first search result is always the best information source.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KInfo1RC),
  title = "The first search result is always the best information source.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KInfo1RC"
)

result
```


###### Question 2


```{r kinfo-wave2-edu-item2}
# Everyone gets the same information when they search for the same things online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KInfo2RC),
  title = "Everyone gets the same information when they search for the same things online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("X", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("X", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KInfo2RC"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r kinfo-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC"
)

result
```


###### Question 2


```{r kinfo-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r kinfo-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r kinfo-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r kinfo-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r kinfo-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r kinfo-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo1RC",
  group_var = "Education"
)

result
```


###### Question 2


```{r kinfo-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo2RC",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Critical Informational Knowledge


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r critinfo-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KInfo3RC),
  title = "",
  questions = "KInfo3RC",
  question_labels = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r critinfo-wave1-age-item1}
# Some people make money by spreading fake news on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KInfo3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r critinfo-wave1-gender-item1}
# Some people make money by spreading fake news on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KInfo3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r critinfo-wave1-edu-item1}
# Some people make money by spreading fake news on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KInfo3RC"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r critinfo-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KInfo3RC),
  title = "",
  questions = "KInfo3RC",
  question_labels = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r critinfo-wave2-age-item1}
# Some people make money by spreading fake news on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KInfo3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r critinfo-wave2-gender-item1}
# Some people make money by spreading fake news on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KInfo3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r critinfo-wave2-edu-item1}
# Some people make money by spreading fake news on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KInfo3RC),
  title = "Some people make money by spreading fake news on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KInfo3RC"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r critinfo-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r critinfo-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r critinfo-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r critinfo-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KInfo3RC",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Netiquette Knowledge


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r knet-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(KCom3RC),
  title = "",
  questions = "KCom3RC",
  question_labels = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r knet-wave1-age-item1}
# Negative comments hurt people less when you say them online than when you say them to their face.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KCom3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r knet-wave1-gender-item1}
# Negative comments hurt people less when you say them online than when you say them to their face.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KCom3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r knet-wave1-edu-item1}
# Negative comments hurt people less when you say them online than when you say them to their face.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KCom3RC"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("The following statements are about the internet. Please indicate if the sentence is true or untrue, according to you. If you don’t know, please choose ‘I don’t know’. You don’t have to guess. If you don’t understand the question, please choose ‘I don’t understand the question.’ Nearly everyone will not know or understand questions. This is normal and something that we want to know.", preset = "question")
```

```{r knet-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(KCom3RC),
  title = "",
  questions = "KCom3RC",
  question_labels = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r knet-wave2-age-item1}
# Negative comments hurt people less when you say them online than when you say them to their face.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "KCom3RC"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r knet-wave2-gender-item1}
# Negative comments hurt people less when you say them online than when you say them to their face.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "KCom3RC"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r knet-wave2-edu-item1}
# Negative comments hurt people less when you say them online than when you say them to their face.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, KCom3RC),
  title = "Negative comments hurt people less when you say them online than when you say them to their face.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  stack_map_values = list("1" = "Correctly Answered", "0" = "Incorrectly Answered"),
  stack_order = c("Don't Know", "Correctly Answered", "Incorrectly Answered"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "KCom3RC"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r knet-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r knet-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r knet-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r knet-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "KCom3RC",
  group_var = "Education"
)

result
```


:::


:::


:::



```{=html}
<nav class='pagination-nav' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <input type='number' class='pagination-input' id='page-input' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'>/ 3</span>
    </div>
    <a href='knowledge_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["knowledge.html","knowledge_p2.html","knowledge_p3.html"];
  const pageInput = document.getElementById('page-input');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```


```{=html}
<style>
/* Ultra-Minimal Pagination Navigation */
.pagination-nav {
  position: sticky;
  bottom: 2rem;
  margin: 3rem auto 2rem auto;
  max-width: 240px;
  z-index: 100;
}

.pagination-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 1rem;
  padding: 0.5rem 1rem;
  background: transparent;
}

.pagination-btn {
  display: flex;
  align-items: center;
  justify-content: center;
  width: 32px;
  height: 32px;
  padding: 0;
  background: transparent;
  color: var(--bs-secondary, #6c757d);
  text-decoration: none;
  border-radius: 0.375rem;
  transition: all 0.15s ease;
  border: none;
  cursor: pointer;
}

.pagination-btn:hover:not(.pagination-disabled) {
  background: var(--bs-light, #f8f9fa);
  color: var(--bs-body-color, #212529);
}

.pagination-btn:active:not(.pagination-disabled) {
  background: var(--bs-gray-200, #e9ecef);
}

.pagination-btn.pagination-disabled {
  color: var(--bs-gray-300, #dee2e6);
  cursor: default;
}

.pagination-icon {
  flex-shrink: 0;
  opacity: 0.7;
}

.pagination-btn:hover:not(.pagination-disabled) .pagination-icon {
  opacity: 1;
}

.pagination-info {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  font-size: 0.875rem;
  color: var(--bs-secondary, #6c757d);
}

.pagination-input {
  width: 2.5rem;
  padding: 0.25rem 0.5rem;
  text-align: center;
  border: 1px solid transparent;
  border-radius: 0.25rem;
  font-size: 0.875rem;
  font-weight: 500;
  color: var(--bs-body-color, #212529);
  background: transparent;
  transition: all 0.15s ease;
}

.pagination-input:hover {
  background: var(--bs-light, #f8f9fa);
  border-color: var(--bs-border-color, #dee2e6);
}

.pagination-input:focus {
  outline: none;
  background: var(--bs-body-bg, #fff);
  border-color: var(--bs-primary, #0d6efd);
  box-shadow: 0 0 0 2px rgba(13, 110, 253, 0.1);
}

.pagination-input::-webkit-inner-spin-button,
.pagination-input::-webkit-outer-spin-button {
  opacity: 0;
}

.pagination-separator {
  color: var(--bs-secondary, #6c757d);
  font-weight: 400;
  font-size: 0.875rem;
}

/* Responsive */
@media (max-width: 768px) {
  .pagination-nav {
    max-width: 220px;
    bottom: 1.5rem;
  }
  
  .pagination-container {
    gap: 0.75rem;
    padding: 0.4rem 0.75rem;
  }
  
  .pagination-btn {
    width: 30px;
    height: 30px;
  }
  
  .pagination-icon {
    width: 16px;
    height: 16px;
  }
  
  .pagination-info {
    font-size: 0.8rem;
  }
  
  .pagination-input {
    width: 2.25rem;
    font-size: 0.8rem;
  }
}

@media (max-width: 480px) {
  .pagination-nav {
    max-width: 200px;
  }
  
  .pagination-btn {
    width: 28px;
    height: 28px;
  }
}

/* Dark mode support */
@media (prefers-color-scheme: dark) {
  .pagination-btn:hover:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.05);
  }
  
  .pagination-btn:active:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.1);
  }
  
  .pagination-input:hover {
    background: rgba(255, 255, 255, 0.05);
  }
}

/* Override Quarto's back-to-top button position */
.back-to-top {
  right: 2rem !important;
  left: auto !important;
}

@media (max-width: 768px) {
  .back-to-top {
    right: 1rem !important;
  }
}
</style>
```

