---
title: "{{< iconify ph chart-line >}} Performance"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Performance** section measures participants’ practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information, recognizing AI-generated images, protecting their devices, or using AI tools effectively. The items cover ten areas of digital competence, from strategic and critical information skills to AI and generative AI skills, providing an overall picture of how well individuals can navigate today’s digital environment.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4268obs.rds
data <- readRDS('dataset_4268obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify fluent-emoji-high-contrast detective >}} Strategic Information Performance


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-sis-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PSIS2),
  title = "",
  questions = "PSIS2",
  question_labels = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-sis-wave1-age-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSIS2"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-sis-wave1-gender-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSIS2"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-sis-wave1-edu-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSIS2"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-sis-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PSIS2),
  title = "",
  questions = "PSIS2",
  question_labels = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-sis-wave2-age-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSIS2"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-sis-wave2-gender-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSIS2"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-sis-wave2-edu-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSIS2"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r perf-sis-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-sis-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-sis-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-sis-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Critical Information Performance


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-cis-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PCIS1, PCIS2),
  title = "",
  questions = c("PCIS1", "PCIS2"),
  question_labels = c("Classify a social media post (task 1)", "Classify a social media post (task 2)"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-cis-wave1-age-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS1"
)

result
```


###### Question 2


```{r perf-cis-wave1-age-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS2"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-cis-wave1-gender-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS1"
)

result
```


###### Question 2


```{r perf-cis-wave1-gender-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS2"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-cis-wave1-edu-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS1"
)

result
```


###### Question 2


```{r perf-cis-wave1-edu-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS2"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-cis-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PCIS1, PCIS2),
  title = "",
  questions = c("PCIS1", "PCIS2"),
  question_labels = c("Classify a social media post (task 1)", "Classify a social media post (task 2)"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-cis-wave2-age-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS1"
)

result
```


###### Question 2


```{r perf-cis-wave2-age-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS2"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-cis-wave2-gender-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS1"
)

result
```


###### Question 2


```{r perf-cis-wave2-gender-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS2"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-cis-wave2-edu-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS1"
)

result
```


###### Question 2


```{r perf-cis-wave2-edu-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS2"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r perf-cis-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1"
)

result
```


###### Question 2


```{r perf-cis-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-cis-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r perf-cis-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-cis-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r perf-cis-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-cis-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1",
  group_var = "Education"
)

result
```


###### Question 2


```{r perf-cis-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Digital Content Creation Performance


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-dccs-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PDCCS1),
  title = "",
  questions = "PDCCS1",
  question_labels = "Identify crop icon",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-wave1-age-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDCCS1"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-wave1-gender-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDCCS1"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-wave1-edu-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDCCS1"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-dccs-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PDCCS1),
  title = "",
  questions = "PDCCS1",
  question_labels = "Identify crop icon",
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-wave2-age-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDCCS1"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-wave2-gender-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDCCS1"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-wave2-edu-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDCCS1"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-dccs-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Safety & Control Performance


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-safety-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PSCS3_1, PSCS3_2, PSCS3_3, PSCS3_4, PSCS3_5, PSCS3_6, PSCS3_7, PSCS3_8, PSCS3_9),
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper (rev)", "Use passwords with ≥14 chars", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-safety-wave1-age-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_1"
)

result
```


###### Question 2


```{r perf-safety-wave1-age-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_2"
)

result
```


###### Question 3


```{r perf-safety-wave1-age-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_3"
)

result
```


###### Question 4


```{r perf-safety-wave1-age-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_4"
)

result
```


###### Question 5


```{r perf-safety-wave1-age-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_5"
)

result
```


###### Question 6


```{r perf-safety-wave1-age-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_6"
)

result
```


###### Question 7


```{r perf-safety-wave1-age-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_7"
)

result
```


###### Question 8


```{r perf-safety-wave1-age-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave1-age-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_9"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-safety-wave1-gender-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_1"
)

result
```


###### Question 2


```{r perf-safety-wave1-gender-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_2"
)

result
```


###### Question 3


```{r perf-safety-wave1-gender-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_3"
)

result
```


###### Question 4


```{r perf-safety-wave1-gender-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_4"
)

result
```


###### Question 5


```{r perf-safety-wave1-gender-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_5"
)

result
```


###### Question 6


```{r perf-safety-wave1-gender-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_6"
)

result
```


###### Question 7


```{r perf-safety-wave1-gender-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_7"
)

result
```


###### Question 8


```{r perf-safety-wave1-gender-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave1-gender-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_9"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-safety-wave1-edu-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### Question 2


```{r perf-safety-wave1-edu-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### Question 3


```{r perf-safety-wave1-edu-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### Question 4


```{r perf-safety-wave1-edu-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### Question 5


```{r perf-safety-wave1-edu-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### Question 6


```{r perf-safety-wave1-edu-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### Question 7


```{r perf-safety-wave1-edu-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### Question 8


```{r perf-safety-wave1-edu-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave1-edu-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_9"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-safety-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PSCS3_1, PSCS3_2, PSCS3_3, PSCS3_4, PSCS3_5, PSCS3_6, PSCS3_7, PSCS3_8, PSCS3_9),
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper (rev)", "Use passwords with ≥14 chars", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-safety-wave2-age-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_1"
)

result
```


###### Question 2


```{r perf-safety-wave2-age-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_2"
)

result
```


###### Question 3


```{r perf-safety-wave2-age-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_3"
)

result
```


###### Question 4


```{r perf-safety-wave2-age-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_4"
)

result
```


###### Question 5


```{r perf-safety-wave2-age-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_5"
)

result
```


###### Question 6


```{r perf-safety-wave2-age-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_6"
)

result
```


###### Question 7


```{r perf-safety-wave2-age-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_7"
)

result
```


###### Question 8


```{r perf-safety-wave2-age-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave2-age-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_9"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-safety-wave2-gender-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_1"
)

result
```


###### Question 2


```{r perf-safety-wave2-gender-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_2"
)

result
```


###### Question 3


```{r perf-safety-wave2-gender-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_3"
)

result
```


###### Question 4


```{r perf-safety-wave2-gender-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_4"
)

result
```


###### Question 5


```{r perf-safety-wave2-gender-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_5"
)

result
```


###### Question 6


```{r perf-safety-wave2-gender-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_6"
)

result
```


###### Question 7


```{r perf-safety-wave2-gender-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_7"
)

result
```


###### Question 8


```{r perf-safety-wave2-gender-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave2-gender-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_9"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-safety-wave2-edu-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### Question 2


```{r perf-safety-wave2-edu-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### Question 3


```{r perf-safety-wave2-edu-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### Question 4


```{r perf-safety-wave2-edu-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### Question 5


```{r perf-safety-wave2-edu-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### Question 6


```{r perf-safety-wave2-edu-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### Question 7


```{r perf-safety-wave2-edu-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### Question 8


```{r perf-safety-wave2-edu-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave2-edu-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_9"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r perf-safety-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1"
)

result
```


###### Question 2


```{r perf-safety-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2"
)

result
```


###### Question 3


```{r perf-safety-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3"
)

result
```


###### Question 4


```{r perf-safety-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4"
)

result
```


###### Question 5


```{r perf-safety-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5"
)

result
```


###### Question 6


```{r perf-safety-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6"
)

result
```


###### Question 7


```{r perf-safety-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7"
)

result
```


###### Question 8


```{r perf-safety-overtime-overall-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-overtime-overall-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-safety-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r perf-safety-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "AgeGroup"
)

result
```


###### Question 3


```{r perf-safety-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "AgeGroup"
)

result
```


###### Question 4


```{r perf-safety-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "AgeGroup"
)

result
```


###### Question 5


```{r perf-safety-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "AgeGroup"
)

result
```


###### Question 6


```{r perf-safety-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "AgeGroup"
)

result
```


###### Question 7


```{r perf-safety-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "AgeGroup"
)

result
```


###### Question 8


```{r perf-safety-overtime-age-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "AgeGroup"
)

result
```


###### item9


```{r perf-safety-overtime-age-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-safety-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r perf-safety-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "geslacht"
)

result
```


###### Question 3


```{r perf-safety-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "geslacht"
)

result
```


###### Question 4


```{r perf-safety-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "geslacht"
)

result
```


###### Question 5


```{r perf-safety-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "geslacht"
)

result
```


###### Question 6


```{r perf-safety-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "geslacht"
)

result
```


###### Question 7


```{r perf-safety-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "geslacht"
)

result
```


###### Question 8


```{r perf-safety-overtime-gender-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "geslacht"
)

result
```


###### item9


```{r perf-safety-overtime-gender-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-safety-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "Education"
)

result
```


###### Question 2


```{r perf-safety-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "Education"
)

result
```


###### Question 3


```{r perf-safety-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "Education"
)

result
```


###### Question 4


```{r perf-safety-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "Education"
)

result
```


###### Question 5


```{r perf-safety-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "Education"
)

result
```


###### Question 6


```{r perf-safety-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "Education"
)

result
```


###### Question 7


```{r perf-safety-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "Education"
)

result
```


###### Question 8


```{r perf-safety-overtime-edu-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "Education"
)

result
```


###### item9


```{r perf-safety-overtime-edu-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "Education"
)

result
```


:::


:::


:::



```{=html}
<nav class='pagination-nav' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <input type='number' class='pagination-input' id='page-input' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'>/ 3</span>
    </div>
    <a href='performance_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["performance.html","performance_p2.html","performance_p3.html"];
  const pageInput = document.getElementById('page-input');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```


```{=html}
<style>
/* Ultra-Minimal Pagination Navigation */
.pagination-nav {
  position: sticky;
  bottom: 2rem;
  margin: 3rem auto 2rem auto;
  max-width: 240px;
  z-index: 100;
}

.pagination-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 1rem;
  padding: 0.5rem 1rem;
  background: transparent;
}

.pagination-btn {
  display: flex;
  align-items: center;
  justify-content: center;
  width: 32px;
  height: 32px;
  padding: 0;
  background: transparent;
  color: var(--bs-secondary, #6c757d);
  text-decoration: none;
  border-radius: 0.375rem;
  transition: all 0.15s ease;
  border: none;
  cursor: pointer;
}

.pagination-btn:hover:not(.pagination-disabled) {
  background: var(--bs-light, #f8f9fa);
  color: var(--bs-body-color, #212529);
}

.pagination-btn:active:not(.pagination-disabled) {
  background: var(--bs-gray-200, #e9ecef);
}

.pagination-btn.pagination-disabled {
  color: var(--bs-gray-300, #dee2e6);
  cursor: default;
}

.pagination-icon {
  flex-shrink: 0;
  opacity: 0.7;
}

.pagination-btn:hover:not(.pagination-disabled) .pagination-icon {
  opacity: 1;
}

.pagination-info {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  font-size: 0.875rem;
  color: var(--bs-secondary, #6c757d);
}

.pagination-input {
  width: 2.5rem;
  padding: 0.25rem 0.5rem;
  text-align: center;
  border: 1px solid transparent;
  border-radius: 0.25rem;
  font-size: 0.875rem;
  font-weight: 500;
  color: var(--bs-body-color, #212529);
  background: transparent;
  transition: all 0.15s ease;
}

.pagination-input:hover {
  background: var(--bs-light, #f8f9fa);
  border-color: var(--bs-border-color, #dee2e6);
}

.pagination-input:focus {
  outline: none;
  background: var(--bs-body-bg, #fff);
  border-color: var(--bs-primary, #0d6efd);
  box-shadow: 0 0 0 2px rgba(13, 110, 253, 0.1);
}

.pagination-input::-webkit-inner-spin-button,
.pagination-input::-webkit-outer-spin-button {
  opacity: 0;
}

.pagination-separator {
  color: var(--bs-secondary, #6c757d);
  font-weight: 400;
  font-size: 0.875rem;
}

/* Responsive */
@media (max-width: 768px) {
  .pagination-nav {
    max-width: 220px;
    bottom: 1.5rem;
  }
  
  .pagination-container {
    gap: 0.75rem;
    padding: 0.4rem 0.75rem;
  }
  
  .pagination-btn {
    width: 30px;
    height: 30px;
  }
  
  .pagination-icon {
    width: 16px;
    height: 16px;
  }
  
  .pagination-info {
    font-size: 0.8rem;
  }
  
  .pagination-input {
    width: 2.25rem;
    font-size: 0.8rem;
  }
}

@media (max-width: 480px) {
  .pagination-nav {
    max-width: 200px;
  }
  
  .pagination-btn {
    width: 28px;
    height: 28px;
  }
}

/* Dark mode support */
@media (prefers-color-scheme: dark) {
  .pagination-btn:hover:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.05);
  }
  
  .pagination-btn:active:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.1);
  }
  
  .pagination-input:hover {
    background: rgba(255, 255, 255, 0.05);
  }
}

/* Override Quarto's back-to-top button position */
.back-to-top {
  right: 2rem !important;
  left: auto !important;
}

@media (max-width: 768px) {
  .back-to-top {
    right: 1rem !important;
  }
}
</style>
```

