---
title: "{{< iconify ph clipboard-text >}} Performance"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Performance** section measures participants' practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information, recognizing AI-generated images, protecting their devices, or using AI tools effectively. The items cover ten areas of digital competence, from strategic and critical information skills to AI and generative AI skills, providing an overall picture of how well individuals can navigate today's digital environment.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```


```{=html}

<style>
/* Chart Lazy Loading Styles */
.chart-lazy {
  position: relative;
  min-height: 400px;
  margin: 1rem 0;
}

.chart-skeleton {
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  display: flex;
  align-items: center;
  justify-content: center;
  flex-direction: column;
  gap: 1rem;
  transition: opacity 0.3s ease;
}

.chart-spinner {
  width: 40px;
  height: 40px;
  border-radius: 50%;
  animation: spin 1s linear infinite;
}

@keyframes spin {
  to { transform: rotate(360deg); }
}

.chart-loading-text {
  font-size: 0.9rem;
  font-weight: 500;
  letter-spacing: 0.5px;
}

/* Theme: Light */
.chart-skeleton.theme-light {
  background: rgba(255, 255, 255, 0.95);
  border: 1px solid rgba(0, 0, 0, 0.05);
  border-radius: 12px;
  box-shadow: 0 4px 12px rgba(0, 0, 0, 0.05);
}

.chart-skeleton.theme-light .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.2);
  border-top-color: rgba(15, 23, 42, 0.8);
}

.chart-skeleton.theme-light .chart-loading-text {
  color: rgba(15, 23, 42, 0.7);
}

/* Theme: Glass */
.chart-skeleton.theme-glass {
  background: rgba(255, 255, 255, 0.25);
  backdrop-filter: blur(16px);
  border: 1px solid rgba(255, 255, 255, 0.4);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.08);
}

.chart-skeleton.theme-glass .chart-spinner {
  border: 3px solid rgba(255, 255, 255, 0.3);
  border-top-color: rgba(15, 23, 42, 0.7);
}

.chart-skeleton.theme-glass .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}

/* Theme: Dark */
.chart-skeleton.theme-dark {
  background: rgba(15, 23, 42, 0.95);
  border: 1px solid rgba(255, 255, 255, 0.1);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.3);
}

.chart-skeleton.theme-dark .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.3);
  border-top-color: rgba(255, 255, 255, 0.9);
}

.chart-skeleton.theme-dark .chart-loading-text {
  color: rgba(255, 255, 255, 0.9);
}

/* Theme: Accent */
.chart-skeleton.theme-accent {
  background: rgba(255, 255, 255, 0.98);
  border: 1px solid rgba(59, 130, 246, 0.15);
  border-radius: 12px;
  box-shadow: 0 4px 20px rgba(59, 130, 246, 0.15);
}

.chart-skeleton.theme-accent .chart-spinner {
  border: 3px solid rgba(59, 130, 246, 0.2);
  border-top-color: rgba(59, 130, 246, 0.9);
}

.chart-skeleton.theme-accent .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}
</style>

<script>
// Chart Lazy Loading System
(function() {
  const THEME = 'light';
  const DEBUG = false;
  
  // Track which charts have been initialized
  const initializedCharts = new Set();
  
  // Queue of charts waiting to be initialized
  const chartQueue = [];
  let isProcessingQueue = false;
  
  // Performance tracking
  let totalChartsLoaded = 0;
  let totalLoadTime = 0;
  const chartTimings = [];
  
  // Create skeleton loader dynamically
  function createSkeleton(container) {
    const skeleton = document.createElement('div');
    skeleton.className = 'chart-skeleton theme-' + THEME;
    skeleton.innerHTML = `
      <div class="chart-spinner"></div>
      <div class="chart-loading-text">Loading visualization...</div>
    `;
    container.appendChild(skeleton);
    return skeleton;
  }
  
  // Initialize a single chart
  function initChart(container) {
    const chartId = container.id;
    if (initializedCharts.has(chartId)) return;
    
    const startTime = DEBUG ? performance.now() : 0;
    
    initializedCharts.add(chartId);
    container.dataset.loaded = 'true';
    
    // Remove skeleton loader
    const skeleton = container.querySelector('.chart-skeleton');
    if (skeleton) {
      skeleton.style.opacity = '0';
      setTimeout(() => skeleton.remove(), 300);
    }
    
    // Trigger Highcharts reflow if present
    setTimeout(() => {
      if (window.Highcharts) {
        Highcharts.charts.forEach(chart => {
          if (chart && chart.reflow) chart.reflow();
        });
      }
      
      // Debug logging
      if (DEBUG) {
        const loadTime = performance.now() - startTime;
        totalChartsLoaded++;
        totalLoadTime += loadTime;
        chartTimings.push({ id: chartId, time: loadTime });
        
        console.log(`📊 Chart loaded: ${chartId} (${loadTime.toFixed(2)}ms)`);
        console.log(`   Total: ${totalChartsLoaded} charts, Avg: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
      }
    }, 50);
  }
  
  // Process chart queue in batches
  function processQueue() {
    if (isProcessingQueue || chartQueue.length === 0) return;
    
    isProcessingQueue = true;
    const batchSize = 3;
    const batch = chartQueue.splice(0, batchSize);
    
    if (DEBUG) {
      console.log(`⚡ Processing batch of ${batch.length} charts (${chartQueue.length} remaining)`);
    }
    
    batch.forEach(container => initChart(container));
    
    if (chartQueue.length > 0) {
      requestIdleCallback(() => {
        isProcessingQueue = false;
        processQueue();
      }, { timeout: 2000 });
    } else {
      isProcessingQueue = false;
      
      if (DEBUG && totalChartsLoaded > 0) {
        console.log(`✅ All charts loaded! Summary:`);
        console.log(`   Total charts: ${totalChartsLoaded}`);
        console.log(`   Total time: ${totalLoadTime.toFixed(2)}ms`);
        console.log(`   Average time per chart: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
        console.log(`   Slowest chart: ${Math.max(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
        console.log(`   Fastest chart: ${Math.min(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
      }
    }
  }
  
  // Intersection Observer for scroll-based lazy loading
  const observer = new IntersectionObserver((entries) => {
    entries.forEach(entry => {
      if (entry.isIntersecting && entry.target.dataset.loaded === 'false') {
        chartQueue.push(entry.target);
        observer.unobserve(entry.target);
        processQueue();
      }
    });
  }, { rootMargin: '300px' });
  
  // Initialize observers when DOM is ready
  function initLazyLoading() {
    document.querySelectorAll('.chart-lazy[data-loaded="false"]').forEach(container => {
      // Create skeleton for each lazy chart
      createSkeleton(container);
      // Start observing
      observer.observe(container);
    });
  }
  
  // Tab-aware rendering: load charts when tab becomes visible
  function initTabAwareLoading() {
    document.querySelectorAll('.panel-tabset').forEach(tabset => {
      const tabs = tabset.querySelectorAll('[role="tab"]');
      
      tabs.forEach(tab => {
        tab.addEventListener('click', function() {
          setTimeout(() => {
            const targetId = this.getAttribute('aria-controls');
            if (!targetId) return;
            
            const targetPanel = document.getElementById(targetId);
            if (!targetPanel) return;
            
            // Initialize any lazy charts in this tab
            const lazyCharts = targetPanel.querySelectorAll('.chart-lazy[data-loaded="false"]');
            lazyCharts.forEach(chart => {
              chartQueue.push(chart);
              observer.unobserve(chart);
            });
            processQueue();
          }, 50);
        });
      });
    });
  }
  
  // Start lazy loading when document is ready
  if (document.readyState === 'loading') {
    document.addEventListener('DOMContentLoaded', function() {
      initLazyLoading();
      initTabAwareLoading();
    });
  } else {
    initLazyLoading();
    initTabAwareLoading();
  }
})();
</script>

```

## {{< iconify ph heart-fill >}} Digital Health


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r perf-health-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PDHWS1_1, PDHWS1_2, PDHWS1_3, PDHWS1_4, PDHWS1_5, PDHWS1_6, PDHWS1_7),
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-age-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-age-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-age-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-age-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-age-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-age-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-age-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-gender-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-gender-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-gender-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-gender-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-gender-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-gender-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-gender-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave1-edu-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave1-edu-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave1-edu-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave1-edu-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave1-edu-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave1-edu-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave1-edu-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_7"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)

```{r perf-health-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PDHWS1_1, PDHWS1_2, PDHWS1_3, PDHWS1_4, PDHWS1_5, PDHWS1_6, PDHWS1_7),
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-age-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-age-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-age-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-age-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-age-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-age-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-age-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-gender-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-gender-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-gender-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-gender-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-gender-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-gender-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-gender-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-wave2-edu-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-wave2-edu-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-wave2-edu-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-wave2-edu-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-wave2-edu-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-wave2-edu-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-wave2-edu-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_7"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-health-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-health-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-health-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-health-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-health-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-health-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-health-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph recycle-fill >}} Green Digital


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Green Digital results](green_digital.html)

```{r perf-green-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PSGDS1_1, PSGDS1_2, PSGDS1_3, PSGDS1_4, PSGDS1_5, PSGDS1_6, PSGDS1_7, PSGDS1_8),
  title = "",
  questions = c("PSGDS1_1", "PSGDS1_2", "PSGDS1_3", "PSGDS1_4", "PSGDS1_5", "PSGDS1_6", "PSGDS1_7", "PSGDS1_8"),
  question_labels = c("Clean mailbox", "Use sustainable search engines", "Avoid unnecessary Cloud storage", "Turn down screen brightness", "Use sleep mode", "Close unused phone apps", "Recycle devices", "Repair before replacing"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave1-age-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave1-age-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave1-age-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave1-age-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave1-age-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave1-age-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave1-age-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave1-age-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave1-gender-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave1-gender-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave1-gender-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave1-gender-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave1-gender-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave1-gender-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave1-gender-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave1-gender-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave1-edu-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave1-edu-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave1-edu-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave1-edu-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave1-edu-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave1-edu-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave1-edu-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave1-edu-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_8"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Green Digital results](green_digital.html)

```{r perf-green-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PSGDS1_1, PSGDS1_2, PSGDS1_3, PSGDS1_4, PSGDS1_5, PSGDS1_6, PSGDS1_7, PSGDS1_8),
  title = "",
  questions = c("PSGDS1_1", "PSGDS1_2", "PSGDS1_3", "PSGDS1_4", "PSGDS1_5", "PSGDS1_6", "PSGDS1_7", "PSGDS1_8"),
  question_labels = c("Clean mailbox", "Use sustainable search engines", "Avoid unnecessary Cloud storage", "Turn down screen brightness", "Use sleep mode", "Close unused phone apps", "Recycle devices", "Repair before replacing"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave2-age-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave2-age-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave2-age-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave2-age-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave2-age-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave2-age-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave2-age-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave2-age-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave2-gender-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave2-gender-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave2-gender-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave2-gender-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave2-gender-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave2-gender-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave2-gender-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave2-gender-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-wave2-edu-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-wave2-edu-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-wave2-edu-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-wave2-edu-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-wave2-edu-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-wave2-edu-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-wave2-edu-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-wave2-edu-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_8"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-overall-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-age-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-gender-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-green-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-green-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-green-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-green-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-green-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-green-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-green-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-green-overtime-edu-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph lightbulb-fill >}} Digital Problem Solving


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Problem Solving results](digital_problem_solving.html)

```{r perf-ps-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SourceHelp_1, SourceHelp_2, SourceHelp_3, SourceHelp_4, SourceHelp_5, SourceHelp_6, SourceHelp_7, SourceHelp_8, SourceHelp_9),
  title = "",
  questions = c("SourceHelp_1", "SourceHelp_2", "SourceHelp_3", "SourceHelp_4", "SourceHelp_5", "SourceHelp_6", "SourceHelp_7", "SourceHelp_8", "SourceHelp_9"),
  question_labels = c("I don't need help", "I don't know anyone", "Family", "Friends", "Colleagues/classmates", "Neighbors/acquaintances", "Help desk", "Library", "Telecom/online helpdesk"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave1-age-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave1-age-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave1-age-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave1-age-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave1-age-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave1-age-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave1-age-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave1-age-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave1-age-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave1-gender-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave1-gender-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave1-gender-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave1-gender-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave1-gender-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave1-gender-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave1-gender-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave1-gender-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave1-gender-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave1-edu-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave1-edu-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave1-edu-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave1-edu-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave1-edu-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave1-edu-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave1-edu-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave1-edu-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave1-edu-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_9"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Problem Solving results](digital_problem_solving.html)

```{r perf-ps-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SourceHelp_1, SourceHelp_2, SourceHelp_3, SourceHelp_4, SourceHelp_5, SourceHelp_6, SourceHelp_7, SourceHelp_8, SourceHelp_9),
  title = "",
  questions = c("SourceHelp_1", "SourceHelp_2", "SourceHelp_3", "SourceHelp_4", "SourceHelp_5", "SourceHelp_6", "SourceHelp_7", "SourceHelp_8", "SourceHelp_9"),
  question_labels = c("I don't need help", "I don't know anyone", "Family", "Friends", "Colleagues/classmates", "Neighbors/acquaintances", "Help desk", "Library", "Telecom/online helpdesk"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave2-age-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave2-age-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave2-age-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave2-age-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave2-age-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave2-age-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave2-age-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave2-age-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave2-age-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave2-gender-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave2-gender-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave2-gender-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave2-gender-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave2-gender-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave2-gender-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave2-gender-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave2-gender-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave2-gender-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-wave2-edu-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-wave2-edu-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-wave2-edu-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-wave2-edu-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-wave2-edu-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-wave2-edu-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-wave2-edu-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-wave2-edu-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave2-edu-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_9"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-overall-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-overtime-overall-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-age-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "AgeGroup"
)

result
```


###### item9


```{r perf-ps-overtime-age-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-gender-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "geslacht"
)

result
```


###### item9


```{r perf-ps-overtime-gender-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-ps-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-ps-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-ps-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-ps-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-ps-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-ps-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-ps-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-ps-overtime-edu-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "Education"
)

result
```


###### item9


```{r perf-ps-overtime-edu-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "Education"
)

result
```


:::


:::


:::


:::



```{=html}
<nav class='pagination-nav' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <a href='performance.html' class='pagination-btn pagination-prev' aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
    <div class='pagination-info'>
      <input type='number' class='pagination-input' id='page-input' min='1' max='3' value='2' aria-label='Current page'>
      <span class='pagination-separator'>/ 3</span>
    </div>
    <a href='performance_p3.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["performance.html","performance_p2.html","performance_p3.html"];
  const pageInput = document.getElementById('page-input');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```


```{=html}
<style>
/* Ultra-Minimal Pagination Navigation */
.pagination-nav {
  position: sticky;
  bottom: 2rem;
  margin: 3rem auto 2rem auto;
  max-width: 240px;
  z-index: 100;
}

.pagination-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 1rem;
  padding: 0.5rem 1rem;
  background: transparent;
}

.pagination-btn {
  display: flex;
  align-items: center;
  justify-content: center;
  width: 32px;
  height: 32px;
  padding: 0;
  background: transparent;
  color: var(--bs-secondary, #6c757d);
  text-decoration: none;
  border-radius: 0.375rem;
  transition: all 0.15s ease;
  border: none;
  cursor: pointer;
}

.pagination-btn:hover:not(.pagination-disabled) {
  background: var(--bs-light, #f8f9fa);
  color: var(--bs-body-color, #212529);
}

.pagination-btn:active:not(.pagination-disabled) {
  background: var(--bs-gray-200, #e9ecef);
}

.pagination-btn.pagination-disabled {
  color: var(--bs-gray-300, #dee2e6);
  cursor: default;
}

.pagination-icon {
  flex-shrink: 0;
  opacity: 0.7;
}

.pagination-btn:hover:not(.pagination-disabled) .pagination-icon {
  opacity: 1;
}

.pagination-info {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  font-size: 0.875rem;
  color: var(--bs-secondary, #6c757d);
}

.pagination-input {
  width: 2.5rem;
  padding: 0.25rem 0.5rem;
  text-align: center;
  border: 1px solid transparent;
  border-radius: 0.25rem;
  font-size: 0.875rem;
  font-weight: 500;
  color: var(--bs-body-color, #212529);
  background: transparent;
  transition: all 0.15s ease;
}

.pagination-input:hover {
  background: var(--bs-light, #f8f9fa);
  border-color: var(--bs-border-color, #dee2e6);
}

.pagination-input:focus {
  outline: none;
  background: var(--bs-body-bg, #fff);
  border-color: var(--bs-primary, #0d6efd);
  box-shadow: 0 0 0 2px rgba(13, 110, 253, 0.1);
}

.pagination-input::-webkit-inner-spin-button,
.pagination-input::-webkit-outer-spin-button {
  opacity: 0;
}

.pagination-separator {
  color: var(--bs-secondary, #6c757d);
  font-weight: 400;
  font-size: 0.875rem;
}

/* Responsive */
@media (max-width: 768px) {
  .pagination-nav {
    max-width: 220px;
    bottom: 1.5rem;
  }
  
  .pagination-container {
    gap: 0.75rem;
    padding: 0.4rem 0.75rem;
  }
  
  .pagination-btn {
    width: 30px;
    height: 30px;
  }
  
  .pagination-icon {
    width: 16px;
    height: 16px;
  }
  
  .pagination-info {
    font-size: 0.8rem;
  }
  
  .pagination-input {
    width: 2.25rem;
    font-size: 0.8rem;
  }
}

@media (max-width: 480px) {
  .pagination-nav {
    max-width: 200px;
  }
  
  .pagination-btn {
    width: 28px;
    height: 28px;
  }
}

/* Dark mode support */
@media (prefers-color-scheme: dark) {
  .pagination-btn:hover:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.05);
  }
  
  .pagination-btn:active:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.1);
  }
  
  .pagination-input:hover {
    background: rgba(255, 255, 255, 0.05);
  }
}

/* Override Quarto's back-to-top button position */
.back-to-top {
  right: 2rem !important;
  left: auto !important;
}

@media (max-width: 768px) {
  .back-to-top {
    right: 1rem !important;
  }
}
</style>
```

