---
title: "{{< iconify ph chart-line >}} Performance"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Performance** section measures participants’ practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information, recognizing AI-generated images, protecting their devices, or using AI tools effectively. The items cover ten areas of digital competence, from strategic and critical information skills to AI and generative AI skills, providing an overall picture of how well individuals can navigate today’s digital environment.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4268obs.rds
data <- readRDS('dataset_4268obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify fluent-emoji-high-contrast detective >}} Health & Wellbeing Performance


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-health-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PDHWS1_1, PDHWS1_2, PDHWS1_3, PDHWS1_4, PDHWS1_5, PDHWS1_6, PDHWS1_7),
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-health-wave1-age-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_1"
)

result
```


###### Question 2


```{r perf-health-wave1-age-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_2"
)

result
```


###### Question 3


```{r perf-health-wave1-age-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_3"
)

result
```


###### Question 4


```{r perf-health-wave1-age-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_4"
)

result
```


###### Question 5


```{r perf-health-wave1-age-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_5"
)

result
```


###### Question 6


```{r perf-health-wave1-age-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_6"
)

result
```


###### Question 7


```{r perf-health-wave1-age-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-health-wave1-gender-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_1"
)

result
```


###### Question 2


```{r perf-health-wave1-gender-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_2"
)

result
```


###### Question 3


```{r perf-health-wave1-gender-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_3"
)

result
```


###### Question 4


```{r perf-health-wave1-gender-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_4"
)

result
```


###### Question 5


```{r perf-health-wave1-gender-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_5"
)

result
```


###### Question 6


```{r perf-health-wave1-gender-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_6"
)

result
```


###### Question 7


```{r perf-health-wave1-gender-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-health-wave1-edu-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### Question 2


```{r perf-health-wave1-edu-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### Question 3


```{r perf-health-wave1-edu-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### Question 4


```{r perf-health-wave1-edu-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### Question 5


```{r perf-health-wave1-edu-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### Question 6


```{r perf-health-wave1-edu-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### Question 7


```{r perf-health-wave1-edu-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_7"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-health-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PDHWS1_1, PDHWS1_2, PDHWS1_3, PDHWS1_4, PDHWS1_5, PDHWS1_6, PDHWS1_7),
  title = "",
  questions = c("PDHWS1_1", "PDHWS1_2", "PDHWS1_3", "PDHWS1_4", "PDHWS1_5", "PDHWS1_6", "PDHWS1_7"),
  question_labels = c("Create digital detox moments", "Have rules limiting digital media", "Use screen-time limiter", "Temporarily switch off Internet", "Delete apps/programs", "Turn off notifications", "Reduce time without special approach"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-health-wave2-age-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_1"
)

result
```


###### Question 2


```{r perf-health-wave2-age-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_2"
)

result
```


###### Question 3


```{r perf-health-wave2-age-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_3"
)

result
```


###### Question 4


```{r perf-health-wave2-age-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_4"
)

result
```


###### Question 5


```{r perf-health-wave2-age-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_5"
)

result
```


###### Question 6


```{r perf-health-wave2-age-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_6"
)

result
```


###### Question 7


```{r perf-health-wave2-age-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-health-wave2-gender-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_1"
)

result
```


###### Question 2


```{r perf-health-wave2-gender-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_2"
)

result
```


###### Question 3


```{r perf-health-wave2-gender-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_3"
)

result
```


###### Question 4


```{r perf-health-wave2-gender-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_4"
)

result
```


###### Question 5


```{r perf-health-wave2-gender-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_5"
)

result
```


###### Question 6


```{r perf-health-wave2-gender-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_6"
)

result
```


###### Question 7


```{r perf-health-wave2-gender-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDHWS1_7"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-health-wave2-edu-item1}
# Create digital detox moments
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_1),
  title = "Create digital detox moments",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_1"
)

result
```


###### Question 2


```{r perf-health-wave2-edu-item2}
# Have rules limiting digital media
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_2),
  title = "Have rules limiting digital media",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_2"
)

result
```


###### Question 3


```{r perf-health-wave2-edu-item3}
# Use screen-time limiter
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_3),
  title = "Use screen-time limiter",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_3"
)

result
```


###### Question 4


```{r perf-health-wave2-edu-item4}
# Temporarily switch off Internet
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_4),
  title = "Temporarily switch off Internet",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_4"
)

result
```


###### Question 5


```{r perf-health-wave2-edu-item5}
# Delete apps/programs
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_5),
  title = "Delete apps/programs",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_5"
)

result
```


###### Question 6


```{r perf-health-wave2-edu-item6}
# Turn off notifications
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_6),
  title = "Turn off notifications",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_6"
)

result
```


###### Question 7


```{r perf-health-wave2-edu-item7}
# Reduce time without special approach
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDHWS1_7),
  title = "Reduce time without special approach",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDHWS1_7"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r perf-health-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1"
)

result
```


###### Question 2


```{r perf-health-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2"
)

result
```


###### Question 3


```{r perf-health-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3"
)

result
```


###### Question 4


```{r perf-health-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4"
)

result
```


###### Question 5


```{r perf-health-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5"
)

result
```


###### Question 6


```{r perf-health-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6"
)

result
```


###### Question 7


```{r perf-health-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-health-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r perf-health-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "AgeGroup"
)

result
```


###### Question 3


```{r perf-health-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "AgeGroup"
)

result
```


###### Question 4


```{r perf-health-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "AgeGroup"
)

result
```


###### Question 5


```{r perf-health-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "AgeGroup"
)

result
```


###### Question 6


```{r perf-health-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "AgeGroup"
)

result
```


###### Question 7


```{r perf-health-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-health-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r perf-health-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "geslacht"
)

result
```


###### Question 3


```{r perf-health-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "geslacht"
)

result
```


###### Question 4


```{r perf-health-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "geslacht"
)

result
```


###### Question 5


```{r perf-health-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "geslacht"
)

result
```


###### Question 6


```{r perf-health-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "geslacht"
)

result
```


###### Question 7


```{r perf-health-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-health-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_1",
  group_var = "Education"
)

result
```


###### Question 2


```{r perf-health-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_2",
  group_var = "Education"
)

result
```


###### Question 3


```{r perf-health-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_3",
  group_var = "Education"
)

result
```


###### Question 4


```{r perf-health-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_4",
  group_var = "Education"
)

result
```


###### Question 5


```{r perf-health-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_5",
  group_var = "Education"
)

result
```


###### Question 6


```{r perf-health-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_6",
  group_var = "Education"
)

result
```


###### Question 7


```{r perf-health-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDHWS1_7",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Green Performance


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-green-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PSGDS1_1, PSGDS1_2, PSGDS1_3, PSGDS1_4, PSGDS1_5, PSGDS1_6, PSGDS1_7, PSGDS1_8),
  title = "",
  questions = c("PSGDS1_1", "PSGDS1_2", "PSGDS1_3", "PSGDS1_4", "PSGDS1_5", "PSGDS1_6", "PSGDS1_7", "PSGDS1_8"),
  question_labels = c("Clean mailbox", "Use sustainable search engines", "Avoid unnecessary Cloud storage", "Turn down screen brightness", "Use sleep mode", "Close unused phone apps", "Recycle devices", "Repair before replacing"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-green-wave1-age-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_1"
)

result
```


###### Question 2


```{r perf-green-wave1-age-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_2"
)

result
```


###### Question 3


```{r perf-green-wave1-age-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_3"
)

result
```


###### Question 4


```{r perf-green-wave1-age-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_4"
)

result
```


###### Question 5


```{r perf-green-wave1-age-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_5"
)

result
```


###### Question 6


```{r perf-green-wave1-age-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_6"
)

result
```


###### Question 7


```{r perf-green-wave1-age-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_7"
)

result
```


###### Question 8


```{r perf-green-wave1-age-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-green-wave1-gender-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_1"
)

result
```


###### Question 2


```{r perf-green-wave1-gender-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_2"
)

result
```


###### Question 3


```{r perf-green-wave1-gender-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_3"
)

result
```


###### Question 4


```{r perf-green-wave1-gender-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_4"
)

result
```


###### Question 5


```{r perf-green-wave1-gender-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_5"
)

result
```


###### Question 6


```{r perf-green-wave1-gender-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_6"
)

result
```


###### Question 7


```{r perf-green-wave1-gender-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_7"
)

result
```


###### Question 8


```{r perf-green-wave1-gender-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-green-wave1-edu-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_1"
)

result
```


###### Question 2


```{r perf-green-wave1-edu-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_2"
)

result
```


###### Question 3


```{r perf-green-wave1-edu-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_3"
)

result
```


###### Question 4


```{r perf-green-wave1-edu-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_4"
)

result
```


###### Question 5


```{r perf-green-wave1-edu-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_5"
)

result
```


###### Question 6


```{r perf-green-wave1-edu-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_6"
)

result
```


###### Question 7


```{r perf-green-wave1-edu-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_7"
)

result
```


###### Question 8


```{r perf-green-wave1-edu-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_8"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-green-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PSGDS1_1, PSGDS1_2, PSGDS1_3, PSGDS1_4, PSGDS1_5, PSGDS1_6, PSGDS1_7, PSGDS1_8),
  title = "",
  questions = c("PSGDS1_1", "PSGDS1_2", "PSGDS1_3", "PSGDS1_4", "PSGDS1_5", "PSGDS1_6", "PSGDS1_7", "PSGDS1_8"),
  question_labels = c("Clean mailbox", "Use sustainable search engines", "Avoid unnecessary Cloud storage", "Turn down screen brightness", "Use sleep mode", "Close unused phone apps", "Recycle devices", "Repair before replacing"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-green-wave2-age-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_1"
)

result
```


###### Question 2


```{r perf-green-wave2-age-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_2"
)

result
```


###### Question 3


```{r perf-green-wave2-age-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_3"
)

result
```


###### Question 4


```{r perf-green-wave2-age-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_4"
)

result
```


###### Question 5


```{r perf-green-wave2-age-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_5"
)

result
```


###### Question 6


```{r perf-green-wave2-age-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_6"
)

result
```


###### Question 7


```{r perf-green-wave2-age-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_7"
)

result
```


###### Question 8


```{r perf-green-wave2-age-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-green-wave2-gender-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_1"
)

result
```


###### Question 2


```{r perf-green-wave2-gender-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_2"
)

result
```


###### Question 3


```{r perf-green-wave2-gender-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_3"
)

result
```


###### Question 4


```{r perf-green-wave2-gender-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_4"
)

result
```


###### Question 5


```{r perf-green-wave2-gender-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_5"
)

result
```


###### Question 6


```{r perf-green-wave2-gender-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_6"
)

result
```


###### Question 7


```{r perf-green-wave2-gender-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_7"
)

result
```


###### Question 8


```{r perf-green-wave2-gender-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSGDS1_8"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-green-wave2-edu-item1}
# Clean mailbox
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_1),
  title = "Clean mailbox",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_1"
)

result
```


###### Question 2


```{r perf-green-wave2-edu-item2}
# Use sustainable search engines
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_2),
  title = "Use sustainable search engines",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_2"
)

result
```


###### Question 3


```{r perf-green-wave2-edu-item3}
# Avoid unnecessary Cloud storage
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_3),
  title = "Avoid unnecessary Cloud storage",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_3"
)

result
```


###### Question 4


```{r perf-green-wave2-edu-item4}
# Turn down screen brightness
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_4),
  title = "Turn down screen brightness",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_4"
)

result
```


###### Question 5


```{r perf-green-wave2-edu-item5}
# Use sleep mode
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_5),
  title = "Use sleep mode",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_5"
)

result
```


###### Question 6


```{r perf-green-wave2-edu-item6}
# Close unused phone apps
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_6),
  title = "Close unused phone apps",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_6"
)

result
```


###### Question 7


```{r perf-green-wave2-edu-item7}
# Recycle devices
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_7),
  title = "Recycle devices",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_7"
)

result
```


###### Question 8


```{r perf-green-wave2-edu-item8}
# Repair before replacing
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSGDS1_8),
  title = "Repair before replacing",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSGDS1_8"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r perf-green-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1"
)

result
```


###### Question 2


```{r perf-green-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2"
)

result
```


###### Question 3


```{r perf-green-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3"
)

result
```


###### Question 4


```{r perf-green-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4"
)

result
```


###### Question 5


```{r perf-green-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5"
)

result
```


###### Question 6


```{r perf-green-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6"
)

result
```


###### Question 7


```{r perf-green-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7"
)

result
```


###### Question 8


```{r perf-green-overtime-overall-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-green-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r perf-green-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2",
  group_var = "AgeGroup"
)

result
```


###### Question 3


```{r perf-green-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3",
  group_var = "AgeGroup"
)

result
```


###### Question 4


```{r perf-green-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4",
  group_var = "AgeGroup"
)

result
```


###### Question 5


```{r perf-green-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5",
  group_var = "AgeGroup"
)

result
```


###### Question 6


```{r perf-green-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6",
  group_var = "AgeGroup"
)

result
```


###### Question 7


```{r perf-green-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7",
  group_var = "AgeGroup"
)

result
```


###### Question 8


```{r perf-green-overtime-age-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-green-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r perf-green-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2",
  group_var = "geslacht"
)

result
```


###### Question 3


```{r perf-green-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3",
  group_var = "geslacht"
)

result
```


###### Question 4


```{r perf-green-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4",
  group_var = "geslacht"
)

result
```


###### Question 5


```{r perf-green-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5",
  group_var = "geslacht"
)

result
```


###### Question 6


```{r perf-green-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6",
  group_var = "geslacht"
)

result
```


###### Question 7


```{r perf-green-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7",
  group_var = "geslacht"
)

result
```


###### Question 8


```{r perf-green-overtime-gender-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-green-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_1",
  group_var = "Education"
)

result
```


###### Question 2


```{r perf-green-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_2",
  group_var = "Education"
)

result
```


###### Question 3


```{r perf-green-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_3",
  group_var = "Education"
)

result
```


###### Question 4


```{r perf-green-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_4",
  group_var = "Education"
)

result
```


###### Question 5


```{r perf-green-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_5",
  group_var = "Education"
)

result
```


###### Question 6


```{r perf-green-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_6",
  group_var = "Education"
)

result
```


###### Question 7


```{r perf-green-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_7",
  group_var = "Education"
)

result
```


###### Question 8


```{r perf-green-overtime-edu-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSGDS1_8",
  group_var = "Education"
)

result
```


:::


:::


:::

## {{< iconify fluent-emoji-high-contrast detective >}} Problem Solving Performance


::: {.panel-tabset}

### Wave 1


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-ps-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SourceHelp_1, SourceHelp_2, SourceHelp_3, SourceHelp_4, SourceHelp_5, SourceHelp_6, SourceHelp_7, SourceHelp_8, SourceHelp_9),
  title = "",
  questions = c("SourceHelp_1", "SourceHelp_2", "SourceHelp_3", "SourceHelp_4", "SourceHelp_5", "SourceHelp_6", "SourceHelp_7", "SourceHelp_8", "SourceHelp_9"),
  question_labels = c("I don't need help", "I don't know anyone", "Family", "Friends", "Colleagues/classmates", "Neighbors/acquaintances", "Help desk", "Library", "Telecom/online helpdesk"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-ps-wave1-age-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_1"
)

result
```


###### Question 2


```{r perf-ps-wave1-age-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_2"
)

result
```


###### Question 3


```{r perf-ps-wave1-age-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_3"
)

result
```


###### Question 4


```{r perf-ps-wave1-age-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_4"
)

result
```


###### Question 5


```{r perf-ps-wave1-age-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_5"
)

result
```


###### Question 6


```{r perf-ps-wave1-age-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_6"
)

result
```


###### Question 7


```{r perf-ps-wave1-age-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_7"
)

result
```


###### Question 8


```{r perf-ps-wave1-age-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave1-age-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-ps-wave1-gender-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_1"
)

result
```


###### Question 2


```{r perf-ps-wave1-gender-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_2"
)

result
```


###### Question 3


```{r perf-ps-wave1-gender-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_3"
)

result
```


###### Question 4


```{r perf-ps-wave1-gender-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_4"
)

result
```


###### Question 5


```{r perf-ps-wave1-gender-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_5"
)

result
```


###### Question 6


```{r perf-ps-wave1-gender-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_6"
)

result
```


###### Question 7


```{r perf-ps-wave1-gender-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_7"
)

result
```


###### Question 8


```{r perf-ps-wave1-gender-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave1-gender-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-ps-wave1-edu-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_1"
)

result
```


###### Question 2


```{r perf-ps-wave1-edu-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_2"
)

result
```


###### Question 3


```{r perf-ps-wave1-edu-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_3"
)

result
```


###### Question 4


```{r perf-ps-wave1-edu-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_4"
)

result
```


###### Question 5


```{r perf-ps-wave1-edu-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_5"
)

result
```


###### Question 6


```{r perf-ps-wave1-edu-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_6"
)

result
```


###### Question 7


```{r perf-ps-wave1-edu-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_7"
)

result
```


###### Question 8


```{r perf-ps-wave1-edu-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave1-edu-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_9"
)

result
```


:::


:::


### Wave 2


::: {.panel-tabset}

##### Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```

```{r perf-ps-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SourceHelp_1, SourceHelp_2, SourceHelp_3, SourceHelp_4, SourceHelp_5, SourceHelp_6, SourceHelp_7, SourceHelp_8, SourceHelp_9),
  title = "",
  questions = c("SourceHelp_1", "SourceHelp_2", "SourceHelp_3", "SourceHelp_4", "SourceHelp_5", "SourceHelp_6", "SourceHelp_7", "SourceHelp_8", "SourceHelp_9"),
  question_labels = c("I don't need help", "I don't know anyone", "Family", "Friends", "Colleagues/classmates", "Neighbors/acquaintances", "Help desk", "Library", "Telecom/online helpdesk"),
  stacked_type = "percent",
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-ps-wave2-age-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_1"
)

result
```


###### Question 2


```{r perf-ps-wave2-age-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_2"
)

result
```


###### Question 3


```{r perf-ps-wave2-age-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_3"
)

result
```


###### Question 4


```{r perf-ps-wave2-age-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_4"
)

result
```


###### Question 5


```{r perf-ps-wave2-age-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_5"
)

result
```


###### Question 6


```{r perf-ps-wave2-age-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_6"
)

result
```


###### Question 7


```{r perf-ps-wave2-age-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_7"
)

result
```


###### Question 8


```{r perf-ps-wave2-age-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave2-age-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-ps-wave2-gender-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_1"
)

result
```


###### Question 2


```{r perf-ps-wave2-gender-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_2"
)

result
```


###### Question 3


```{r perf-ps-wave2-gender-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_3"
)

result
```


###### Question 4


```{r perf-ps-wave2-gender-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_4"
)

result
```


###### Question 5


```{r perf-ps-wave2-gender-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_5"
)

result
```


###### Question 6


```{r perf-ps-wave2-gender-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_6"
)

result
```


###### Question 7


```{r perf-ps-wave2-gender-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_7"
)

result
```


###### Question 8


```{r perf-ps-wave2-gender-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave2-gender-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SourceHelp_9"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-ps-wave2-edu-item1}
# I don't need help
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_1),
  title = "I don't need help",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_1"
)

result
```


###### Question 2


```{r perf-ps-wave2-edu-item2}
# I don't know anyone
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_2),
  title = "I don't know anyone",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_2"
)

result
```


###### Question 3


```{r perf-ps-wave2-edu-item3}
# Family
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_3),
  title = "Family",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_3"
)

result
```


###### Question 4


```{r perf-ps-wave2-edu-item4}
# Friends
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_4),
  title = "Friends",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_4"
)

result
```


###### Question 5


```{r perf-ps-wave2-edu-item5}
# Colleagues/classmates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_5),
  title = "Colleagues/classmates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_5"
)

result
```


###### Question 6


```{r perf-ps-wave2-edu-item6}
# Neighbors/acquaintances
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_6),
  title = "Neighbors/acquaintances",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_6"
)

result
```


###### Question 7


```{r perf-ps-wave2-edu-item7}
# Help desk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_7),
  title = "Help desk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_7"
)

result
```


###### Question 8


```{r perf-ps-wave2-edu-item8}
# Library
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_8),
  title = "Library",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-wave2-edu-item9}
# Telecom/online helpdesk
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SourceHelp_9),
  title = "Telecom/online helpdesk",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#d7191c", "#fdae61", "#2b83ba", "#ffffbf", "#abdda4"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SourceHelp_9"
)

result
```


:::


:::


### Over Time


::: {.panel-tabset}

##### Overall


::: {.panel-tabset}

###### Question 1


```{r perf-ps-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1"
)

result
```


###### Question 2


```{r perf-ps-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2"
)

result
```


###### Question 3


```{r perf-ps-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3"
)

result
```


###### Question 4


```{r perf-ps-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4"
)

result
```


###### Question 5


```{r perf-ps-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5"
)

result
```


###### Question 6


```{r perf-ps-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6"
)

result
```


###### Question 7


```{r perf-ps-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7"
)

result
```


###### Question 8


```{r perf-ps-overtime-overall-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8"
)

result
```


###### item9


```{r perf-ps-overtime-overall-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9"
)

result
```


:::


##### Age


::: {.panel-tabset}

###### Question 1


```{r perf-ps-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "AgeGroup"
)

result
```


###### Question 2


```{r perf-ps-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "AgeGroup"
)

result
```


###### Question 3


```{r perf-ps-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "AgeGroup"
)

result
```


###### Question 4


```{r perf-ps-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "AgeGroup"
)

result
```


###### Question 5


```{r perf-ps-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "AgeGroup"
)

result
```


###### Question 6


```{r perf-ps-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "AgeGroup"
)

result
```


###### Question 7


```{r perf-ps-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "AgeGroup"
)

result
```


###### Question 8


```{r perf-ps-overtime-age-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "AgeGroup"
)

result
```


###### item9


```{r perf-ps-overtime-age-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "AgeGroup"
)

result
```


:::


##### Gender


::: {.panel-tabset}

###### Question 1


```{r perf-ps-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "geslacht"
)

result
```


###### Question 2


```{r perf-ps-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "geslacht"
)

result
```


###### Question 3


```{r perf-ps-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "geslacht"
)

result
```


###### Question 4


```{r perf-ps-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "geslacht"
)

result
```


###### Question 5


```{r perf-ps-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "geslacht"
)

result
```


###### Question 6


```{r perf-ps-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "geslacht"
)

result
```


###### Question 7


```{r perf-ps-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "geslacht"
)

result
```


###### Question 8


```{r perf-ps-overtime-gender-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "geslacht"
)

result
```


###### item9


```{r perf-ps-overtime-gender-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "geslacht"
)

result
```


:::


##### Education


::: {.panel-tabset}

###### Question 1


```{r perf-ps-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_1",
  group_var = "Education"
)

result
```


###### Question 2


```{r perf-ps-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_2",
  group_var = "Education"
)

result
```


###### Question 3


```{r perf-ps-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_3",
  group_var = "Education"
)

result
```


###### Question 4


```{r perf-ps-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_4",
  group_var = "Education"
)

result
```


###### Question 5


```{r perf-ps-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_5",
  group_var = "Education"
)

result
```


###### Question 6


```{r perf-ps-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_6",
  group_var = "Education"
)

result
```


###### Question 7


```{r perf-ps-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_7",
  group_var = "Education"
)

result
```


###### Question 8


```{r perf-ps-overtime-edu-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_8",
  group_var = "Education"
)

result
```


###### item9


```{r perf-ps-overtime-edu-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SourceHelp_9",
  group_var = "Education"
)

result
```


:::


:::


:::



```{=html}
<nav class='pagination-nav' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <a href='performance.html' class='pagination-btn pagination-prev' aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
    <div class='pagination-info'>
      <input type='number' class='pagination-input' id='page-input' min='1' max='3' value='2' aria-label='Current page'>
      <span class='pagination-separator'>/ 3</span>
    </div>
    <a href='performance_p3.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["performance.html","performance_p2.html","performance_p3.html"];
  const pageInput = document.getElementById('page-input');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```


```{=html}
<style>
/* Ultra-Minimal Pagination Navigation */
.pagination-nav {
  position: sticky;
  bottom: 2rem;
  margin: 3rem auto 2rem auto;
  max-width: 240px;
  z-index: 100;
}

.pagination-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 1rem;
  padding: 0.5rem 1rem;
  background: transparent;
}

.pagination-btn {
  display: flex;
  align-items: center;
  justify-content: center;
  width: 32px;
  height: 32px;
  padding: 0;
  background: transparent;
  color: var(--bs-secondary, #6c757d);
  text-decoration: none;
  border-radius: 0.375rem;
  transition: all 0.15s ease;
  border: none;
  cursor: pointer;
}

.pagination-btn:hover:not(.pagination-disabled) {
  background: var(--bs-light, #f8f9fa);
  color: var(--bs-body-color, #212529);
}

.pagination-btn:active:not(.pagination-disabled) {
  background: var(--bs-gray-200, #e9ecef);
}

.pagination-btn.pagination-disabled {
  color: var(--bs-gray-300, #dee2e6);
  cursor: default;
}

.pagination-icon {
  flex-shrink: 0;
  opacity: 0.7;
}

.pagination-btn:hover:not(.pagination-disabled) .pagination-icon {
  opacity: 1;
}

.pagination-info {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  font-size: 0.875rem;
  color: var(--bs-secondary, #6c757d);
}

.pagination-input {
  width: 2.5rem;
  padding: 0.25rem 0.5rem;
  text-align: center;
  border: 1px solid transparent;
  border-radius: 0.25rem;
  font-size: 0.875rem;
  font-weight: 500;
  color: var(--bs-body-color, #212529);
  background: transparent;
  transition: all 0.15s ease;
}

.pagination-input:hover {
  background: var(--bs-light, #f8f9fa);
  border-color: var(--bs-border-color, #dee2e6);
}

.pagination-input:focus {
  outline: none;
  background: var(--bs-body-bg, #fff);
  border-color: var(--bs-primary, #0d6efd);
  box-shadow: 0 0 0 2px rgba(13, 110, 253, 0.1);
}

.pagination-input::-webkit-inner-spin-button,
.pagination-input::-webkit-outer-spin-button {
  opacity: 0;
}

.pagination-separator {
  color: var(--bs-secondary, #6c757d);
  font-weight: 400;
  font-size: 0.875rem;
}

/* Responsive */
@media (max-width: 768px) {
  .pagination-nav {
    max-width: 220px;
    bottom: 1.5rem;
  }
  
  .pagination-container {
    gap: 0.75rem;
    padding: 0.4rem 0.75rem;
  }
  
  .pagination-btn {
    width: 30px;
    height: 30px;
  }
  
  .pagination-icon {
    width: 16px;
    height: 16px;
  }
  
  .pagination-info {
    font-size: 0.8rem;
  }
  
  .pagination-input {
    width: 2.25rem;
    font-size: 0.8rem;
  }
}

@media (max-width: 480px) {
  .pagination-nav {
    max-width: 200px;
  }
  
  .pagination-btn {
    width: 28px;
    height: 28px;
  }
}

/* Dark mode support */
@media (prefers-color-scheme: dark) {
  .pagination-btn:hover:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.05);
  }
  
  .pagination-btn:active:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.1);
  }
  
  .pagination-input:hover {
    background: rgba(255, 255, 255, 0.05);
  }
}

/* Override Quarto's back-to-top button position */
.back-to-top {
  right: 2rem !important;
  left: auto !important;
}

@media (max-width: 768px) {
  .back-to-top {
    right: 1rem !important;
  }
}
</style>
```

