---
title: "{{< iconify ph clipboard-text >}} Performance"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Performance** section measures participants' practical digital skills across a range of real-life tasks. Instead of self-reports, these items test what people *can actually do*: for example, searching for reliable information, recognizing AI-generated images, protecting their devices, or using AI tools effectively. The items cover ten areas of digital competence, from strategic and critical information skills to AI and generative AI skills, providing an overall picture of how well individuals can navigate today's digital environment.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4268obs.rds
data <- readRDS('dataset_4268obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```


```{=html}

<style>
/* Chart Lazy Loading Styles */
.chart-lazy {
  position: relative;
  min-height: 400px;
  margin: 1rem 0;
}

.chart-skeleton {
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  display: flex;
  align-items: center;
  justify-content: center;
  flex-direction: column;
  gap: 1rem;
  transition: opacity 0.3s ease;
}

.chart-spinner {
  width: 40px;
  height: 40px;
  border-radius: 50%;
  animation: spin 1s linear infinite;
}

@keyframes spin {
  to { transform: rotate(360deg); }
}

.chart-loading-text {
  font-size: 0.9rem;
  font-weight: 500;
  letter-spacing: 0.5px;
}

/* Theme: Light */
.chart-skeleton.theme-light {
  background: rgba(255, 255, 255, 0.95);
  border: 1px solid rgba(0, 0, 0, 0.05);
  border-radius: 12px;
  box-shadow: 0 4px 12px rgba(0, 0, 0, 0.05);
}

.chart-skeleton.theme-light .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.2);
  border-top-color: rgba(15, 23, 42, 0.8);
}

.chart-skeleton.theme-light .chart-loading-text {
  color: rgba(15, 23, 42, 0.7);
}

/* Theme: Glass */
.chart-skeleton.theme-glass {
  background: rgba(255, 255, 255, 0.25);
  backdrop-filter: blur(16px);
  border: 1px solid rgba(255, 255, 255, 0.4);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.08);
}

.chart-skeleton.theme-glass .chart-spinner {
  border: 3px solid rgba(255, 255, 255, 0.3);
  border-top-color: rgba(15, 23, 42, 0.7);
}

.chart-skeleton.theme-glass .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}

/* Theme: Dark */
.chart-skeleton.theme-dark {
  background: rgba(15, 23, 42, 0.95);
  border: 1px solid rgba(255, 255, 255, 0.1);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.3);
}

.chart-skeleton.theme-dark .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.3);
  border-top-color: rgba(255, 255, 255, 0.9);
}

.chart-skeleton.theme-dark .chart-loading-text {
  color: rgba(255, 255, 255, 0.9);
}

/* Theme: Accent */
.chart-skeleton.theme-accent {
  background: rgba(255, 255, 255, 0.98);
  border: 1px solid rgba(59, 130, 246, 0.15);
  border-radius: 12px;
  box-shadow: 0 4px 20px rgba(59, 130, 246, 0.15);
}

.chart-skeleton.theme-accent .chart-spinner {
  border: 3px solid rgba(59, 130, 246, 0.2);
  border-top-color: rgba(59, 130, 246, 0.9);
}

.chart-skeleton.theme-accent .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}
</style>

<script>
// Chart Lazy Loading System
(function() {
  const THEME = 'light';
  const DEBUG = false;
  
  // Track which charts have been initialized
  const initializedCharts = new Set();
  
  // Queue of charts waiting to be initialized
  const chartQueue = [];
  let isProcessingQueue = false;
  
  // Performance tracking
  let totalChartsLoaded = 0;
  let totalLoadTime = 0;
  const chartTimings = [];
  
  // Create skeleton loader dynamically
  function createSkeleton(container) {
    const skeleton = document.createElement('div');
    skeleton.className = 'chart-skeleton theme-' + THEME;
    skeleton.innerHTML = `
      <div class="chart-spinner"></div>
      <div class="chart-loading-text">Loading visualization...</div>
    `;
    container.appendChild(skeleton);
    return skeleton;
  }
  
  // Initialize a single chart
  function initChart(container) {
    const chartId = container.id;
    if (initializedCharts.has(chartId)) return;
    
    const startTime = DEBUG ? performance.now() : 0;
    
    initializedCharts.add(chartId);
    container.dataset.loaded = 'true';
    
    // Remove skeleton loader
    const skeleton = container.querySelector('.chart-skeleton');
    if (skeleton) {
      skeleton.style.opacity = '0';
      setTimeout(() => skeleton.remove(), 300);
    }
    
    // Trigger Highcharts reflow if present
    setTimeout(() => {
      if (window.Highcharts) {
        Highcharts.charts.forEach(chart => {
          if (chart && chart.reflow) chart.reflow();
        });
      }
      
      // Debug logging
      if (DEBUG) {
        const loadTime = performance.now() - startTime;
        totalChartsLoaded++;
        totalLoadTime += loadTime;
        chartTimings.push({ id: chartId, time: loadTime });
        
        console.log(`📊 Chart loaded: ${chartId} (${loadTime.toFixed(2)}ms)`);
        console.log(`   Total: ${totalChartsLoaded} charts, Avg: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
      }
    }, 50);
  }
  
  // Process chart queue in batches
  function processQueue() {
    if (isProcessingQueue || chartQueue.length === 0) return;
    
    isProcessingQueue = true;
    const batchSize = 3;
    const batch = chartQueue.splice(0, batchSize);
    
    if (DEBUG) {
      console.log(`⚡ Processing batch of ${batch.length} charts (${chartQueue.length} remaining)`);
    }
    
    batch.forEach(container => initChart(container));
    
    if (chartQueue.length > 0) {
      requestIdleCallback(() => {
        isProcessingQueue = false;
        processQueue();
      }, { timeout: 2000 });
    } else {
      isProcessingQueue = false;
      
      if (DEBUG && totalChartsLoaded > 0) {
        console.log(`✅ All charts loaded! Summary:`);
        console.log(`   Total charts: ${totalChartsLoaded}`);
        console.log(`   Total time: ${totalLoadTime.toFixed(2)}ms`);
        console.log(`   Average time per chart: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
        console.log(`   Slowest chart: ${Math.max(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
        console.log(`   Fastest chart: ${Math.min(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
      }
    }
  }
  
  // Intersection Observer for scroll-based lazy loading
  const observer = new IntersectionObserver((entries) => {
    entries.forEach(entry => {
      if (entry.isIntersecting && entry.target.dataset.loaded === 'false') {
        chartQueue.push(entry.target);
        observer.unobserve(entry.target);
        processQueue();
      }
    });
  }, { rootMargin: '300px' });
  
  // Initialize observers when DOM is ready
  function initLazyLoading() {
    document.querySelectorAll('.chart-lazy[data-loaded="false"]').forEach(container => {
      // Create skeleton for each lazy chart
      createSkeleton(container);
      // Start observing
      observer.observe(container);
    });
  }
  
  // Tab-aware rendering: load charts when tab becomes visible
  function initTabAwareLoading() {
    document.querySelectorAll('.panel-tabset').forEach(tabset => {
      const tabs = tabset.querySelectorAll('[role="tab"]');
      
      tabs.forEach(tab => {
        tab.addEventListener('click', function() {
          setTimeout(() => {
            const targetId = this.getAttribute('aria-controls');
            if (!targetId) return;
            
            const targetPanel = document.getElementById(targetId);
            if (!targetPanel) return;
            
            // Initialize any lazy charts in this tab
            const lazyCharts = targetPanel.querySelectorAll('.chart-lazy[data-loaded="false"]');
            lazyCharts.forEach(chart => {
              chartQueue.push(chart);
              observer.unobserve(chart);
            });
            processQueue();
          }, 50);
        });
      });
    });
  }
  
  // Start lazy loading when document is ready
  if (document.readyState === 'loading') {
    document.addEventListener('DOMContentLoaded', function() {
      initLazyLoading();
      initTabAwareLoading();
    });
  } else {
    initLazyLoading();
    initTabAwareLoading();
  }
})();
</script>

```

## {{< iconify ph magnifying-glass >}} Strategic Information


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Strategic Information results](strategic_information.html)

```{r perf-sis-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PSIS2),
  title = "",
  questions = "PSIS2",
  question_labels = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-wave1-age-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSIS2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-wave1-gender-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSIS2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-wave1-edu-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSIS2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Strategic Information results](strategic_information.html)

```{r perf-sis-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PSIS2),
  title = "",
  questions = "PSIS2",
  question_labels = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-wave2-age-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSIS2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-wave2-gender-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSIS2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-wave2-edu-item1}
# Restrict Google to Dutch sources (correct/incorrect)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSIS2),
  title = "Restrict Google to Dutch sources (correct/incorrect)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSIS2"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-sis-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSIS2",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph detective-fill >}} Critical Information


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Critical Information results](critical_information.html)

```{r perf-cis-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PCIS1, PCIS2),
  title = "",
  questions = c("PCIS1", "PCIS2"),
  question_labels = c("Classify a social media post (task 1)", "Classify a social media post (task 2)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-wave1-age-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-wave1-age-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-wave1-gender-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-wave1-gender-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-wave1-edu-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-wave1-edu-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Critical Information results](critical_information.html)

```{r perf-cis-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PCIS1, PCIS2),
  title = "",
  questions = c("PCIS1", "PCIS2"),
  question_labels = c("Classify a social media post (task 1)", "Classify a social media post (task 2)"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-wave2-age-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-wave2-age-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PCIS2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-wave2-gender-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-wave2-gender-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PCIS2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-wave2-edu-item1}
# Classify a social media post (task 1)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PCIS1),
  title = "Classify a social media post (task 1)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-wave2-edu-item2}
# Classify a social media post (task 2)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PCIS2),
  title = "Classify a social media post (task 2)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PCIS2"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-cis-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-cis-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PCIS2",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph palette-fill >}} Digital Content Creation


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Content Creation results](digital_content_creation.html)

```{r perf-dccs-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PDCCS1),
  title = "",
  questions = "PDCCS1",
  question_labels = "Identify crop icon",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-wave1-age-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDCCS1"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-wave1-gender-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDCCS1"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-wave1-edu-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDCCS1"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Content Creation results](digital_content_creation.html)

```{r perf-dccs-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PDCCS1),
  title = "",
  questions = "PDCCS1",
  question_labels = "Identify crop icon",
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-wave2-age-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PDCCS1"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-wave2-gender-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PDCCS1"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-wave2-edu-item1}
# Identify crop icon
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PDCCS1),
  title = "Identify crop icon",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Incorrect", "Correct"),
  stack_map_values = list("1" = "Correct", "0" = "Incorrect"),
  stack_order = c("Incorrect", "Correct"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PDCCS1"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-dccs-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PDCCS1",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph shield-check-fill >}} Safety


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Safety results](safety.html)

```{r perf-safety-wave1-overall}
# 
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(PSCS3_1, PSCS3_2, PSCS3_3, PSCS3_4, PSCS3_5, PSCS3_6, PSCS3_7, PSCS3_8, PSCS3_9),
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper (rev)", "Use passwords with ≥14 chars", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-age-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-age-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-age-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-age-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-age-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-age-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-age-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-age-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave1-age-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-gender-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-gender-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-gender-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-gender-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-gender-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-gender-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-gender-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-gender-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave1-gender-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave1-edu-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave1-edu-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave1-edu-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave1-edu-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave1-edu-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave1-edu-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave1-edu-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave1-edu-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave1-edu-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_9"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Performance tasks: proportion correct or selected. Where items are multi-select, we show the share selecting each action.", preset = "question")
```
[{{< iconify ph cards >}} See all Safety results](safety.html)

```{r perf-safety-wave2-overall}
# 
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(PSCS3_1, PSCS3_2, PSCS3_3, PSCS3_4, PSCS3_5, PSCS3_6, PSCS3_7, PSCS3_8, PSCS3_9),
  title = "",
  questions = c("PSCS3_1", "PSCS3_2", "PSCS3_3", "PSCS3_4", "PSCS3_5", "PSCS3_6", "PSCS3_7", "PSCS3_8", "PSCS3_9"),
  question_labels = c("Keep passwords in a password safe", "Save passwords on paper (rev)", "Use passwords with ≥14 chars", "Different passwords per account", "Use passkey (finger/face)", "Two-step verification", "Install software updates", "Use adblocker", "Make backups"),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-age-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-age-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-age-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-age-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-age-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-age-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-age-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-age-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave2-age-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "PSCS3_9"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-gender-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-gender-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-gender-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-gender-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-gender-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-gender-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-gender-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-gender-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave2-gender-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "PSCS3_9"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-wave2-edu-item1}
# Keep passwords in a password safe
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_1),
  title = "Keep passwords in a password safe",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-wave2-edu-item2}
# Save passwords on paper (rev)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_2),
  title = "Save passwords on paper (rev)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-wave2-edu-item3}
# Use passwords with ≥14 chars
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_3),
  title = "Use passwords with ≥14 chars",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-wave2-edu-item4}
# Different passwords per account
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_4),
  title = "Different passwords per account",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-wave2-edu-item5}
# Use passkey (finger/face)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_5),
  title = "Use passkey (finger/face)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-wave2-edu-item6}
# Two-step verification
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_6),
  title = "Two-step verification",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-wave2-edu-item7}
# Install software updates
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_7),
  title = "Install software updates",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-wave2-edu-item8}
# Use adblocker
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_8),
  title = "Use adblocker",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-wave2-edu-item9}
# Make backups
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, PSCS3_9),
  title = "Make backups",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0, 10, 20, 30),
  stack_bin_labels = c("Not selected", "Selected"),
  stack_map_values = list("1" = "Selected", "0" = "Not selected"),
  stack_order = c("Not selected", "Selected"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "PSCS3_9"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-overall-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-overall-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-overall-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-overall-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8"
)

result
```


###### item9


```{r perf-safety-overtime-overall-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-age-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-age-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-age-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-age-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "AgeGroup"
)

result
```


###### item9


```{r perf-safety-overtime-age-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-gender-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-gender-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-gender-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-gender-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "geslacht"
)

result
```


###### item9


```{r perf-safety-overtime-gender-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r perf-safety-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r perf-safety-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r perf-safety-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r perf-safety-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r perf-safety-overtime-edu-item5}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r perf-safety-overtime-edu-item6}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r perf-safety-overtime-edu-item7}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_7",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 8


```{r perf-safety-overtime-edu-item8}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_8",
  group_var = "Education"
)

result
```


###### item9


```{r perf-safety-overtime-edu-item9}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = 1,
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "PSCS3_9",
  group_var = "Education"
)

result
```


:::


:::


:::


:::



```{=html}
<nav class='pagination-nav' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <input type='number' class='pagination-input' id='page-input' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'>/ 3</span>
    </div>
    <a href='performance_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["performance.html","performance_p2.html","performance_p3.html"];
  const pageInput = document.getElementById('page-input');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```


```{=html}
<style>
/* Ultra-Minimal Pagination Navigation */
.pagination-nav {
  position: sticky;
  bottom: 2rem;
  margin: 3rem auto 2rem auto;
  max-width: 240px;
  z-index: 100;
}

.pagination-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 1rem;
  padding: 0.5rem 1rem;
  background: transparent;
}

.pagination-btn {
  display: flex;
  align-items: center;
  justify-content: center;
  width: 32px;
  height: 32px;
  padding: 0;
  background: transparent;
  color: var(--bs-secondary, #6c757d);
  text-decoration: none;
  border-radius: 0.375rem;
  transition: all 0.15s ease;
  border: none;
  cursor: pointer;
}

.pagination-btn:hover:not(.pagination-disabled) {
  background: var(--bs-light, #f8f9fa);
  color: var(--bs-body-color, #212529);
}

.pagination-btn:active:not(.pagination-disabled) {
  background: var(--bs-gray-200, #e9ecef);
}

.pagination-btn.pagination-disabled {
  color: var(--bs-gray-300, #dee2e6);
  cursor: default;
}

.pagination-icon {
  flex-shrink: 0;
  opacity: 0.7;
}

.pagination-btn:hover:not(.pagination-disabled) .pagination-icon {
  opacity: 1;
}

.pagination-info {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  font-size: 0.875rem;
  color: var(--bs-secondary, #6c757d);
}

.pagination-input {
  width: 2.5rem;
  padding: 0.25rem 0.5rem;
  text-align: center;
  border: 1px solid transparent;
  border-radius: 0.25rem;
  font-size: 0.875rem;
  font-weight: 500;
  color: var(--bs-body-color, #212529);
  background: transparent;
  transition: all 0.15s ease;
}

.pagination-input:hover {
  background: var(--bs-light, #f8f9fa);
  border-color: var(--bs-border-color, #dee2e6);
}

.pagination-input:focus {
  outline: none;
  background: var(--bs-body-bg, #fff);
  border-color: var(--bs-primary, #0d6efd);
  box-shadow: 0 0 0 2px rgba(13, 110, 253, 0.1);
}

.pagination-input::-webkit-inner-spin-button,
.pagination-input::-webkit-outer-spin-button {
  opacity: 0;
}

.pagination-separator {
  color: var(--bs-secondary, #6c757d);
  font-weight: 400;
  font-size: 0.875rem;
}

/* Responsive */
@media (max-width: 768px) {
  .pagination-nav {
    max-width: 220px;
    bottom: 1.5rem;
  }
  
  .pagination-container {
    gap: 0.75rem;
    padding: 0.4rem 0.75rem;
  }
  
  .pagination-btn {
    width: 30px;
    height: 30px;
  }
  
  .pagination-icon {
    width: 16px;
    height: 16px;
  }
  
  .pagination-info {
    font-size: 0.8rem;
  }
  
  .pagination-input {
    width: 2.25rem;
    font-size: 0.8rem;
  }
}

@media (max-width: 480px) {
  .pagination-nav {
    max-width: 200px;
  }
  
  .pagination-btn {
    width: 28px;
    height: 28px;
  }
}

/* Dark mode support */
@media (prefers-color-scheme: dark) {
  .pagination-btn:hover:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.05);
  }
  
  .pagination-btn:active:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.1);
  }
  
  .pagination-input:hover {
    background: rgba(255, 255, 255, 0.05);
  }
}

/* Override Quarto's back-to-top button position */
.back-to-top {
  right: 2rem !important;
  left: auto !important;
}

@media (max-width: 768px) {
  .back-to-top {
    right: 1rem !important;
  }
}
</style>
```

