---
title: "{{< iconify ph lightning-fill >}} Skills"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Skills** section measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information, creating content, protecting their privacy, or recognizing when AI is being used. The questions cover different domains of digital competence, from information and communication skills to AI and generative AI skills, and together provide insight into participants’ everyday digital capabilities and confidence levels.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```


```{=html}

<style>
/* Chart Lazy Loading Styles */
.chart-lazy {
  position: relative;
  min-height: 400px;
  margin: 1rem 0;
}

.chart-skeleton {
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  display: flex;
  align-items: center;
  justify-content: center;
  flex-direction: column;
  gap: 1rem;
  transition: opacity 0.3s ease;
}

.chart-spinner {
  width: 40px;
  height: 40px;
  border-radius: 50%;
  animation: spin 1s linear infinite;
}

@keyframes spin {
  to { transform: rotate(360deg); }
}

.chart-loading-text {
  font-size: 0.9rem;
  font-weight: 500;
  letter-spacing: 0.5px;
}

/* Theme: Light */
.chart-skeleton.theme-light {
  background: rgba(255, 255, 255, 0.95);
  border: 1px solid rgba(0, 0, 0, 0.05);
  border-radius: 12px;
  box-shadow: 0 4px 12px rgba(0, 0, 0, 0.05);
}

.chart-skeleton.theme-light .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.2);
  border-top-color: rgba(15, 23, 42, 0.8);
}

.chart-skeleton.theme-light .chart-loading-text {
  color: rgba(15, 23, 42, 0.7);
}

/* Theme: Glass */
.chart-skeleton.theme-glass {
  background: rgba(255, 255, 255, 0.25);
  backdrop-filter: blur(16px);
  border: 1px solid rgba(255, 255, 255, 0.4);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.08);
}

.chart-skeleton.theme-glass .chart-spinner {
  border: 3px solid rgba(255, 255, 255, 0.3);
  border-top-color: rgba(15, 23, 42, 0.7);
}

.chart-skeleton.theme-glass .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}

/* Theme: Dark */
.chart-skeleton.theme-dark {
  background: rgba(15, 23, 42, 0.95);
  border: 1px solid rgba(255, 255, 255, 0.1);
  border-radius: 12px;
  box-shadow: 0 8px 32px rgba(0, 0, 0, 0.3);
}

.chart-skeleton.theme-dark .chart-spinner {
  border: 3px solid rgba(148, 163, 184, 0.3);
  border-top-color: rgba(255, 255, 255, 0.9);
}

.chart-skeleton.theme-dark .chart-loading-text {
  color: rgba(255, 255, 255, 0.9);
}

/* Theme: Accent */
.chart-skeleton.theme-accent {
  background: rgba(255, 255, 255, 0.98);
  border: 1px solid rgba(59, 130, 246, 0.15);
  border-radius: 12px;
  box-shadow: 0 4px 20px rgba(59, 130, 246, 0.15);
}

.chart-skeleton.theme-accent .chart-spinner {
  border: 3px solid rgba(59, 130, 246, 0.2);
  border-top-color: rgba(59, 130, 246, 0.9);
}

.chart-skeleton.theme-accent .chart-loading-text {
  color: rgba(15, 23, 42, 0.8);
}
</style>

<script>
// Chart Lazy Loading System
(function() {
  const THEME = 'light';
  const DEBUG = false;
  
  // Track which charts have been initialized
  const initializedCharts = new Set();
  
  // Queue of charts waiting to be initialized
  const chartQueue = [];
  let isProcessingQueue = false;
  
  // Performance tracking
  let totalChartsLoaded = 0;
  let totalLoadTime = 0;
  const chartTimings = [];
  
  // Create skeleton loader dynamically
  function createSkeleton(container) {
    const skeleton = document.createElement('div');
    skeleton.className = 'chart-skeleton theme-' + THEME;
    skeleton.innerHTML = `
      <div class="chart-spinner"></div>
      <div class="chart-loading-text">Loading visualization...</div>
    `;
    container.appendChild(skeleton);
    return skeleton;
  }
  
  // Initialize a single chart
  function initChart(container) {
    const chartId = container.id;
    if (initializedCharts.has(chartId)) return;
    
    const startTime = DEBUG ? performance.now() : 0;
    
    initializedCharts.add(chartId);
    container.dataset.loaded = 'true';
    
    // Remove skeleton loader
    const skeleton = container.querySelector('.chart-skeleton');
    if (skeleton) {
      skeleton.style.opacity = '0';
      setTimeout(() => skeleton.remove(), 300);
    }
    
    // Trigger Highcharts reflow if present
    setTimeout(() => {
      if (window.Highcharts) {
        Highcharts.charts.forEach(chart => {
          if (chart && chart.reflow) chart.reflow();
        });
      }
      
      // Debug logging
      if (DEBUG) {
        const loadTime = performance.now() - startTime;
        totalChartsLoaded++;
        totalLoadTime += loadTime;
        chartTimings.push({ id: chartId, time: loadTime });
        
        console.log(`📊 Chart loaded: ${chartId} (${loadTime.toFixed(2)}ms)`);
        console.log(`   Total: ${totalChartsLoaded} charts, Avg: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
      }
    }, 50);
  }
  
  // Process chart queue in batches
  function processQueue() {
    if (isProcessingQueue || chartQueue.length === 0) return;
    
    isProcessingQueue = true;
    const batchSize = 3;
    const batch = chartQueue.splice(0, batchSize);
    
    if (DEBUG) {
      console.log(`⚡ Processing batch of ${batch.length} charts (${chartQueue.length} remaining)`);
    }
    
    batch.forEach(container => initChart(container));
    
    if (chartQueue.length > 0) {
      requestIdleCallback(() => {
        isProcessingQueue = false;
        processQueue();
      }, { timeout: 2000 });
    } else {
      isProcessingQueue = false;
      
      if (DEBUG && totalChartsLoaded > 0) {
        console.log(`✅ All charts loaded! Summary:`);
        console.log(`   Total charts: ${totalChartsLoaded}`);
        console.log(`   Total time: ${totalLoadTime.toFixed(2)}ms`);
        console.log(`   Average time per chart: ${(totalLoadTime/totalChartsLoaded).toFixed(2)}ms`);
        console.log(`   Slowest chart: ${Math.max(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
        console.log(`   Fastest chart: ${Math.min(...chartTimings.map(t => t.time)).toFixed(2)}ms`);
      }
    }
  }
  
  // Intersection Observer for scroll-based lazy loading
  const observer = new IntersectionObserver((entries) => {
    entries.forEach(entry => {
      if (entry.isIntersecting && entry.target.dataset.loaded === 'false') {
        chartQueue.push(entry.target);
        observer.unobserve(entry.target);
        processQueue();
      }
    });
  }, { rootMargin: '300px' });
  
  // Initialize observers when DOM is ready
  function initLazyLoading() {
    document.querySelectorAll('.chart-lazy[data-loaded="false"]').forEach(container => {
      // Create skeleton for each lazy chart
      createSkeleton(container);
      // Start observing
      observer.observe(container);
    });
  }
  
  // Tab-aware rendering: load charts when tab becomes visible
  function initTabAwareLoading() {
    document.querySelectorAll('.panel-tabset').forEach(tabset => {
      const tabs = tabset.querySelectorAll('[role="tab"]');
      
      tabs.forEach(tab => {
        tab.addEventListener('click', function() {
          setTimeout(() => {
            const targetId = this.getAttribute('aria-controls');
            if (!targetId) return;
            
            const targetPanel = document.getElementById(targetId);
            if (!targetPanel) return;
            
            // Initialize any lazy charts in this tab
            const lazyCharts = targetPanel.querySelectorAll('.chart-lazy[data-loaded="false"]');
            lazyCharts.forEach(chart => {
              chartQueue.push(chart);
              observer.unobserve(chart);
            });
            processQueue();
          }, 50);
        });
      });
    });
  }
  
  // Start lazy loading when document is ready
  if (document.readyState === 'loading') {
    document.addEventListener('DOMContentLoaded', function() {
      initLazyLoading();
      initTabAwareLoading();
    });
  } else {
    initLazyLoading();
    initTabAwareLoading();
  }
})();
</script>

```

## {{< iconify ph magnifying-glass >}} Strategic Information


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Strategic Information results](strategic_information.html)

```{r sis-wave1-overall}
# Strategic Information Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SInfo1, SInfo3_V2, SInfo4),
  title = "Strategic Information Skills",
  questions = c("SInfo1", "SInfo3_V2", "SInfo4"),
  question_labels = c("I know how to choose good keywords for online searches (for example with Google).", "I know how I can find answers to my questions on the internet.", "I know how I can use search functions in search engines (for example with Google)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-age-item1}
# I know how to choose good keywords for online searches (for example with Google).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SInfo1),
  title = "I know how to choose good keywords for online searches (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-age-item2}
# I know how I can find answers to my questions on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SInfo3_V2),
  title = "I know how I can find answers to my questions on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-age-item3}
# I know how I can use search functions in search engines (for example with Google).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SInfo4),
  title = "I know how I can use search functions in search engines (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-gender-item1}
# I know how to choose good keywords for online searches (for example with Google).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SInfo1),
  title = "I know how to choose good keywords for online searches (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-gender-item2}
# I know how I can find answers to my questions on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SInfo3_V2),
  title = "I know how I can find answers to my questions on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-gender-item3}
# I know how I can use search functions in search engines (for example with Google).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SInfo4),
  title = "I know how I can use search functions in search engines (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave1-edu-item1}
# I know how to choose good keywords for online searches (for example with Google).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SInfo1),
  title = "I know how to choose good keywords for online searches (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave1-edu-item2}
# I know how I can find answers to my questions on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SInfo3_V2),
  title = "I know how I can find answers to my questions on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave1-edu-item3}
# I know how I can use search functions in search engines (for example with Google).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SInfo4),
  title = "I know how I can use search functions in search engines (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo4"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Strategic Information results](strategic_information.html)

```{r sis-wave2-overall}
# Strategic Information Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SInfo1, SInfo3_V2, SInfo4),
  title = "Strategic Information Skills",
  questions = c("SInfo1", "SInfo3_V2", "SInfo4"),
  question_labels = c("I know how to choose good keywords for online searches (for example with Google).", "I know how I can find answers to my questions on the internet.", "I know how I can use search functions in search engines (for example with Google)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-age-item1}
# I know how to choose good keywords for online searches (for example with Google).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SInfo1),
  title = "I know how to choose good keywords for online searches (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-age-item2}
# I know how I can find answers to my questions on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SInfo3_V2),
  title = "I know how I can find answers to my questions on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-age-item3}
# I know how I can use search functions in search engines (for example with Google).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SInfo4),
  title = "I know how I can use search functions in search engines (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-gender-item1}
# I know how to choose good keywords for online searches (for example with Google).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SInfo1),
  title = "I know how to choose good keywords for online searches (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-gender-item2}
# I know how I can find answers to my questions on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SInfo3_V2),
  title = "I know how I can find answers to my questions on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-gender-item3}
# I know how I can use search functions in search engines (for example with Google).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SInfo4),
  title = "I know how I can use search functions in search engines (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo4"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-wave2-edu-item1}
# I know how to choose good keywords for online searches (for example with Google).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SInfo1),
  title = "I know how to choose good keywords for online searches (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-wave2-edu-item2}
# I know how I can find answers to my questions on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SInfo3_V2),
  title = "I know how I can find answers to my questions on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-wave2-edu-item3}
# I know how I can use search functions in search engines (for example with Google).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SInfo4),
  title = "I know how I can use search functions in search engines (for example with Google).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo4"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SInfo1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SInfo3_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SInfo4"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo4",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo4",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r sis-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r sis-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo3_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r sis-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo4",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph detective-fill >}} Critical Information


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Critical Information results](critical_information.html)

```{r cis-wave1-overall}
# Critical Information Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SInfo5, SInfo6, SInfo7),
  title = "Critical Information Skills",
  questions = c("SInfo5", "SInfo6", "SInfo7"),
  question_labels = c("I know how I can check if the information I find on the internet is true.", "I know how I can check if a website is reliable.", "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-age-item1}
# I know how I can check if the information I find on the internet is true.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SInfo5),
  title = "I know how I can check if the information I find on the internet is true.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-age-item2}
# I know how I can check if a website is reliable.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SInfo6),
  title = "I know how I can check if a website is reliable.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SInfo7),
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-gender-item1}
# I know how I can check if the information I find on the internet is true.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SInfo5),
  title = "I know how I can check if the information I find on the internet is true.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-gender-item2}
# I know how I can check if a website is reliable.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SInfo6),
  title = "I know how I can check if a website is reliable.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SInfo7),
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave1-edu-item1}
# I know how I can check if the information I find on the internet is true.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SInfo5),
  title = "I know how I can check if the information I find on the internet is true.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave1-edu-item2}
# I know how I can check if a website is reliable.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SInfo6),
  title = "I know how I can check if a website is reliable.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave1-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SInfo7),
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo7"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Critical Information results](critical_information.html)

```{r cis-wave2-overall}
# Critical Information Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SInfo5, SInfo6, SInfo7),
  title = "Critical Information Skills",
  questions = c("SInfo5", "SInfo6", "SInfo7"),
  question_labels = c("I know how I can check if the information I find on the internet is true.", "I know how I can check if a website is reliable.", "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-age-item1}
# I know how I can check if the information I find on the internet is true.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SInfo5),
  title = "I know how I can check if the information I find on the internet is true.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-age-item2}
# I know how I can check if a website is reliable.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SInfo6),
  title = "I know how I can check if a website is reliable.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-age-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SInfo7),
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-gender-item1}
# I know how I can check if the information I find on the internet is true.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SInfo5),
  title = "I know how I can check if the information I find on the internet is true.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-gender-item2}
# I know how I can check if a website is reliable.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SInfo6),
  title = "I know how I can check if a website is reliable.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-gender-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SInfo7),
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SInfo7"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-wave2-edu-item1}
# I know how I can check if the information I find on the internet is true.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SInfo5),
  title = "I know how I can check if the information I find on the internet is true.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-wave2-edu-item2}
# I know how I can check if a website is reliable.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SInfo6),
  title = "I know how I can check if a website is reliable.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-wave2-edu-item3}
# I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SInfo7),
  title = "I can assess what the goal of online information is (e.g., to inform, influence, entertain or sell).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SInfo7"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SInfo5"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SInfo6"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SInfo7"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo5",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo6",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo7",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo5",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo6",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo7",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r cis-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo5",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r cis-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo6",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r cis-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SInfo7",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph chats-fill >}} Netiquette


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Netiquette results](netiquette.html)

```{r nskills-wave1-overall}
# Netiquette Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SCom1_V2, SCom2, SCom4_V2, SCom5),
  title = "Netiquette Skills",
  questions = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  question_labels = c("I know when I should ask for permission to share something online.", "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).", "I know which things I should not share online.", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-age-item1}
# I know when I should ask for permission to share something online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCom1_V2),
  title = "I know when I should ask for permission to share something online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-age-item2}
# I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCom2),
  title = "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-age-item3}
# I know which things I should not share online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCom4_V2),
  title = "I know which things I should not share online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCom5),
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-gender-item1}
# I know when I should ask for permission to share something online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCom1_V2),
  title = "I know when I should ask for permission to share something online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-gender-item2}
# I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCom2),
  title = "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-gender-item3}
# I know which things I should not share online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCom4_V2),
  title = "I know which things I should not share online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCom5),
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave1-edu-item1}
# I know when I should ask for permission to share something online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCom1_V2),
  title = "I know when I should ask for permission to share something online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave1-edu-item2}
# I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCom2),
  title = "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave1-edu-item3}
# I know which things I should not share online.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCom4_V2),
  title = "I know which things I should not share online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave1-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCom5),
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Netiquette results](netiquette.html)

```{r nskills-wave2-overall}
# Netiquette Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SCom1_V2, SCom2, SCom4_V2, SCom5),
  title = "Netiquette Skills",
  questions = c("SCom1_V2", "SCom2", "SCom4_V2", "SCom5"),
  question_labels = c("I know when I should ask for permission to share something online.", "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).", "I know which things I should not share online.", "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-age-item1}
# I know when I should ask for permission to share something online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCom1_V2),
  title = "I know when I should ask for permission to share something online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-age-item2}
# I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCom2),
  title = "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-age-item3}
# I know which things I should not share online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCom4_V2),
  title = "I know which things I should not share online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-age-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCom5),
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-gender-item1}
# I know when I should ask for permission to share something online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCom1_V2),
  title = "I know when I should ask for permission to share something online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-gender-item2}
# I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCom2),
  title = "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-gender-item3}
# I know which things I should not share online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCom4_V2),
  title = "I know which things I should not share online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-gender-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCom5),
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-wave2-edu-item1}
# I know when I should ask for permission to share something online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCom1_V2),
  title = "I know when I should ask for permission to share something online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-wave2-edu-item2}
# I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCom2),
  title = "I know which communication tool best fits which situation  (for example: call, send a WhatsApp-message, send an e-mail).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-wave2-edu-item3}
# I know which things I should not share online.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCom4_V2),
  title = "I know which things I should not share online.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-wave2-edu-item4}
# I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCom5),
  title = "I know when it is appropriate and when it is not appropriate to use emoticons (for example smileys ☺ or emoji's).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom5"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCom1_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCom2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCom4_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCom5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r nskills-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom1_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r nskills-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r nskills-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom4_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r nskills-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCom5",
  group_var = "Education"
)

result
```


:::


:::


:::


:::

## {{< iconify ph palette-fill >}} Digital Content Creation


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Content Creation results](digital_content_creation.html)

```{r dccs-wave1-overall}
# Digital Content Creation Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SCrea2, SCrea3, SCrea4, SCrea5),
  title = "Digital Content Creation Skills",
  questions = c("SCrea2", "SCrea3", "SCrea4", "SCrea5"),
  question_labels = c("I can make a presentation on the computer (for example in Powerpoint)", "I can make something that combines different digital media (for example a movie with music).", "I can change existing digital images, music, and video.", "I can make a photo or video more attractive (for example with a filter or Photoshop)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCrea2),
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-age-item2}
# I can make something that combines different digital media (for example a movie with music).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCrea3),
  title = "I can make something that combines different digital media (for example a movie with music).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-age-item3}
# I can change existing digital images, music, and video.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCrea4),
  title = "I can change existing digital images, music, and video.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCrea5),
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCrea2),
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-gender-item2}
# I can make something that combines different digital media (for example a movie with music).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCrea3),
  title = "I can make something that combines different digital media (for example a movie with music).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-gender-item3}
# I can change existing digital images, music, and video.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCrea4),
  title = "I can change existing digital images, music, and video.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCrea5),
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave1-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCrea2),
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave1-edu-item2}
# I can make something that combines different digital media (for example a movie with music).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCrea3),
  title = "I can make something that combines different digital media (for example a movie with music).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave1-edu-item3}
# I can change existing digital images, music, and video.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCrea4),
  title = "I can change existing digital images, music, and video.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave1-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCrea5),
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea5"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {#chart-nested-wave2 .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall



```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Content Creation results](digital_content_creation.html)

```{r dccs-wave2-overall}
# Digital Content Creation Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SCrea2, SCrea3, SCrea4, SCrea5),
  title = "Digital Content Creation Skills",
  questions = c("SCrea2", "SCrea3", "SCrea4", "SCrea5"),
  question_labels = c("I can make a presentation on the computer (for example in Powerpoint)", "I can make something that combines different digital media (for example a movie with music).", "I can change existing digital images, music, and video.", "I can make a photo or video more attractive (for example with a filter or Photoshop)."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-age-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCrea2),
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-age-item2}
# I can make something that combines different digital media (for example a movie with music).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCrea3),
  title = "I can make something that combines different digital media (for example a movie with music).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-age-item3}
# I can change existing digital images, music, and video.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCrea4),
  title = "I can change existing digital images, music, and video.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-age-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCrea5),
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-gender-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCrea2),
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-gender-item2}
# I can make something that combines different digital media (for example a movie with music).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCrea3),
  title = "I can make something that combines different digital media (for example a movie with music).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-gender-item3}
# I can change existing digital images, music, and video.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCrea4),
  title = "I can change existing digital images, music, and video.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-gender-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCrea5),
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCrea5"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-wave2-edu-item1}
# I can make a presentation on the computer (for example in Powerpoint)
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCrea2),
  title = "I can make a presentation on the computer (for example in Powerpoint)",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-wave2-edu-item2}
# I can make something that combines different digital media (for example a movie with music).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCrea3),
  title = "I can make something that combines different digital media (for example a movie with music).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-wave2-edu-item3}
# I can change existing digital images, music, and video.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCrea4),
  title = "I can change existing digital images, music, and video.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-wave2-edu-item4}
# I can make a photo or video more attractive (for example with a filter or Photoshop).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCrea5),
  title = "I can make a photo or video more attractive (for example with a filter or Photoshop).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCrea5"
)

result
```


:::


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {#chart-nested-overtime .chart-lazy data-loaded='false'}


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-overall-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCrea2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-overall-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCrea3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-overall-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCrea4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-overall-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  response_var = "SCrea5"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-age-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-age-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-age-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-age-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea5",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-gender-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-gender-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-gender-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-gender-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea5",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dccs-overtime-edu-item1}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dccs-overtime-edu-item2}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dccs-overtime-edu-item3}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r dccs-overtime-edu-item4}
# timeline visualization
result <- create_timeline(
  data = data,
  title = NULL,
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = NULL,
  weight_var = "weging_GAMO",
  response_var = "SCrea5",
  group_var = "Education"
)

result
```


:::


:::


:::


:::



```{=html}
<nav class='pagination-nav' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <button class='pagination-btn pagination-prev pagination-disabled' disabled aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </button>
    <div class='pagination-info'>
      <input type='number' class='pagination-input' id='page-input' min='1' max='3' value='1' aria-label='Current page'>
      <span class='pagination-separator'>/ 3</span>
    </div>
    <a href='skills_p2.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["skills.html","skills_p2.html","skills_p3.html"];
  const pageInput = document.getElementById('page-input');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```


```{=html}
<style>
/* Ultra-Minimal Pagination Navigation */
.pagination-nav {
  position: sticky;
  bottom: 2rem;
  margin: 3rem auto 2rem auto;
  max-width: 240px;
  z-index: 100;
}

.pagination-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 1rem;
  padding: 0.5rem 1rem;
  background: transparent;
}

.pagination-btn {
  display: flex;
  align-items: center;
  justify-content: center;
  width: 32px;
  height: 32px;
  padding: 0;
  background: transparent;
  color: var(--bs-secondary, #6c757d);
  text-decoration: none;
  border-radius: 0.375rem;
  transition: all 0.15s ease;
  border: none;
  cursor: pointer;
}

.pagination-btn:hover:not(.pagination-disabled) {
  background: var(--bs-light, #f8f9fa);
  color: var(--bs-body-color, #212529);
}

.pagination-btn:active:not(.pagination-disabled) {
  background: var(--bs-gray-200, #e9ecef);
}

.pagination-btn.pagination-disabled {
  color: var(--bs-gray-300, #dee2e6);
  cursor: default;
}

.pagination-icon {
  flex-shrink: 0;
  opacity: 0.7;
}

.pagination-btn:hover:not(.pagination-disabled) .pagination-icon {
  opacity: 1;
}

.pagination-info {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  font-size: 0.875rem;
  color: var(--bs-secondary, #6c757d);
}

.pagination-input {
  width: 2.5rem;
  padding: 0.25rem 0.5rem;
  text-align: center;
  border: 1px solid transparent;
  border-radius: 0.25rem;
  font-size: 0.875rem;
  font-weight: 500;
  color: var(--bs-body-color, #212529);
  background: transparent;
  transition: all 0.15s ease;
}

.pagination-input:hover {
  background: var(--bs-light, #f8f9fa);
  border-color: var(--bs-border-color, #dee2e6);
}

.pagination-input:focus {
  outline: none;
  background: var(--bs-body-bg, #fff);
  border-color: var(--bs-primary, #0d6efd);
  box-shadow: 0 0 0 2px rgba(13, 110, 253, 0.1);
}

.pagination-input::-webkit-inner-spin-button,
.pagination-input::-webkit-outer-spin-button {
  opacity: 0;
}

.pagination-separator {
  color: var(--bs-secondary, #6c757d);
  font-weight: 400;
  font-size: 0.875rem;
}

/* Responsive */
@media (max-width: 768px) {
  .pagination-nav {
    max-width: 220px;
    bottom: 1.5rem;
  }
  
  .pagination-container {
    gap: 0.75rem;
    padding: 0.4rem 0.75rem;
  }
  
  .pagination-btn {
    width: 30px;
    height: 30px;
  }
  
  .pagination-icon {
    width: 16px;
    height: 16px;
  }
  
  .pagination-info {
    font-size: 0.8rem;
  }
  
  .pagination-input {
    width: 2.25rem;
    font-size: 0.8rem;
  }
}

@media (max-width: 480px) {
  .pagination-nav {
    max-width: 200px;
  }
  
  .pagination-btn {
    width: 28px;
    height: 28px;
  }
}

/* Dark mode support */
@media (prefers-color-scheme: dark) {
  .pagination-btn:hover:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.05);
  }
  
  .pagination-btn:active:not(.pagination-disabled) {
    background: rgba(255, 255, 255, 0.1);
  }
  
  .pagination-input:hover {
    background: rgba(255, 255, 255, 0.05);
  }
}

/* Override Quarto's back-to-top button position */
.back-to-top {
  right: 2rem !important;
  left: auto !important;
}

@media (max-width: 768px) {
  .back-to-top {
    right: 1rem !important;
  }
}
</style>
```

