---
title: "{{< iconify ph lightning-fill >}} Skills"
format: html
---


```{=html}
<script>document.body.classList.add('has-pagination-top');</script>
<nav class='pagination-nav pagination-top' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <a href='skills.html' class='pagination-btn pagination-prev' aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
    <div class='pagination-info'>
      <span class='pagination-prefix'>Page </span>
      <input type='number' class='pagination-input' id='page-input-top' min='1' max='3' value='2' aria-label='Current page'>
      <span class='pagination-separator'> / 3</span>
    </div>
    <a href='skills_p3.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["skills.html","skills_p2.html","skills_p3.html"];
  const pageInput = document.getElementById('page-input-top');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```



```{r}
#| include: false
library(dashboardr)
```

**THIS IS A MOCKUP VERSION PLEASE DO NOT CITE**

The **Skills** section measures participants’ *self-assessed ability* to perform a wide range of digital tasks. These items capture how confident people feel doing things like searching for information, creating content, protecting their privacy, or recognizing when AI is being used. The questions cover different domains of digital competence, from information and communication skills to AI and generative AI skills, and together provide insight into participants’ everyday digital capabilities and confidence levels.

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data from dataset_4014obs.rds
data <- readRDS('dataset_4014obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_984a0efe <- data %>% dplyr::filter(wave == 1)
data_filtered_4af682fd <- data %>% dplyr::filter(wave == 2)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Use dashboardr's loading overlay function
dashboardr::add_loading_overlay("Loading", 1, theme = "light")
```

## {{< iconify ph shield-check-fill >}} Safety


**Safety & Control of Information and Devices** encompasses protecting devices and personal information: using security measures, managing privacy settings, identifying phishing, and controlling what information is shared online.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Safety results](safety.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r safety-wave1-overall}
# Safety and Control of Information and Devices Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SSafDev1, SSafDev2, SPriv1, SPriv2, SPriv3, SPriv4, SCom3),
  title = "Safety and Control of Information and Devices Skills",
  questions = c("SSafDev1", "SSafDev2", "SPriv1", "SPriv2", "SPriv3", "SPriv4", "SCom3"),
  question_labels = c("I know how to protect a device against access (e.g. a PIN code or fingerprint).", "I know how to protect devices against viruses.", "I know how to adjust the privacy settings on a mobile phone or tablet.", "I know how to change the location settings on a mobile phone or tablet.", "I know how to identify suspicious e-mail messages that try to get my personal data.", "I know how to delete the history of websites that I have visited before.", "I know how to block messages from someone that I don't want to hear from."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-age-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-age-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-age-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-age-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-age-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-age-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-age-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-gender-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-gender-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-gender-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-gender-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-gender-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-gender-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-gender-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-edu-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-edu-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-edu-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-edu-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-edu-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-edu-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-edu-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave1-mig-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave1-mig-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave1-mig-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave1-mig-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave1-mig-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave1-mig-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave1-mig-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SCom3"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r safety-wave2-overall}
# Safety and Control of Information and Devices Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SSafDev1, SSafDev2, SPriv1, SPriv2, SPriv3, SPriv4, SCom3),
  title = "Safety and Control of Information and Devices Skills",
  questions = c("SSafDev1", "SSafDev2", "SPriv1", "SPriv2", "SPriv3", "SPriv4", "SCom3"),
  question_labels = c("I know how to protect a device against access (e.g. a PIN code or fingerprint).", "I know how to protect devices against viruses.", "I know how to adjust the privacy settings on a mobile phone or tablet.", "I know how to change the location settings on a mobile phone or tablet.", "I know how to identify suspicious e-mail messages that try to get my personal data.", "I know how to delete the history of websites that I have visited before.", "I know how to block messages from someone that I don't want to hear from."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-age-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-age-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-age-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-age-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-age-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-age-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-age-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-gender-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-gender-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-gender-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-gender-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-gender-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-gender-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-gender-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-edu-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-edu-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-edu-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-edu-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-edu-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-edu-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-edu-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SCom3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-wave2-mig-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SSafDev1),
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-wave2-mig-item2}
# I know how to protect devices against viruses.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SSafDev2),
  title = "I know how to protect devices against viruses.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-wave2-mig-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SPriv1),
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-wave2-mig-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SPriv2),
  title = "I know how to change the location settings on a mobile phone or tablet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-wave2-mig-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SPriv3),
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-wave2-mig-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SPriv4),
  title = "I know how to delete the history of websites that I have visited before.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-wave2-mig-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SCom3),
  title = "I know how to block messages from someone that I don't want to hear from.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SCom3"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-overall-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SSafDev1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-overall-item2}
# I know how to protect devices against viruses.
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SSafDev2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-overall-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SPriv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-overall-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SPriv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-overall-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SPriv3"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-overall-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SPriv4"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-overall-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone that I don't want to hear from.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SCom3"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-age-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-age-item2}
# I know how to protect devices against viruses.
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-age-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-age-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-age-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-age-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-age-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone that I don't want to hear from.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-gender-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-gender-item2}
# I know how to protect devices against viruses.
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-gender-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-gender-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-gender-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-gender-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-gender-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone that I don't want to hear from.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-edu-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-edu-item2}
# I know how to protect devices against viruses.
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-edu-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-edu-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-edu-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-edu-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-edu-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone that I don't want to hear from.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r safety-overtime-mig-item1}
# I know how to protect a device against access (e.g. a PIN code or fingerprint).
result <- create_timeline(
  data = data,
  title = "I know how to protect a device against access (e.g. a PIN code or fingerprint).",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r safety-overtime-mig-item2}
# I know how to protect devices against viruses.
result <- create_timeline(
  data = data,
  title = "I know how to protect devices against viruses.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SSafDev2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r safety-overtime-mig-item3}
# I know how to adjust the privacy settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to adjust the privacy settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 4


```{r safety-overtime-mig-item4}
# I know how to change the location settings on a mobile phone or tablet.
result <- create_timeline(
  data = data,
  title = "I know how to change the location settings on a mobile phone or tablet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 5


```{r safety-overtime-mig-item5}
# I know how to identify suspicious e-mail messages that try to get my personal data.
result <- create_timeline(
  data = data,
  title = "I know how to identify suspicious e-mail messages that try to get my personal data.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv3",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 6


```{r safety-overtime-mig-item6}
# I know how to delete the history of websites that I have visited before.
result <- create_timeline(
  data = data,
  title = "I know how to delete the history of websites that I have visited before.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SPriv4",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 7


```{r safety-overtime-mig-item7}
# I know how to block messages from someone that I don't want to hear from.
result <- create_timeline(
  data = data,
  title = "I know how to block messages from someone that I don't want to hear from.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SCom3",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph heart-fill >}} Digital Health


**Digital Health & Wellbeing** skills relate to managing healthy digital habits: controlling screen time, minimizing distractions, taking digital breaks, and understanding how technology affects sleep and wellbeing.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Health results](digital_health.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dhealth-wave1-overall}
# Digital Health and Wellbeing Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SHealth1, SHealth2_V2, SHealth3_V2),
  title = "Digital Health and Wellbeing Skills",
  questions = c("SHealth1", "SHealth2_V2", "SHealth3_V2"),
  question_labels = c("I know how to control how much time I spend on the internet.", "I know how to make sure my phone does not distract me.", "I know how I can stop using my phone and computer for a while, if I want to."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-age-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-age-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-age-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-gender-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-gender-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-gender-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-edu-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-edu-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-edu-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave1-mig-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave1-mig-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave1-mig-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SHealth3_V2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dhealth-wave2-overall}
# Digital Health and Wellbeing Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SHealth1, SHealth2_V2, SHealth3_V2),
  title = "Digital Health and Wellbeing Skills",
  questions = c("SHealth1", "SHealth2_V2", "SHealth3_V2"),
  question_labels = c("I know how to control how much time I spend on the internet.", "I know how to make sure my phone does not distract me.", "I know how I can stop using my phone and computer for a while, if I want to."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-age-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-age-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-age-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-gender-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-gender-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-gender-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-edu-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-edu-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-edu-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-wave2-mig-item1}
# I know how to control how much time I spend on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SHealth1),
  title = "I know how to control how much time I spend on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-wave2-mig-item2}
# I know how to make sure my phone does not distract me.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SHealth2_V2),
  title = "I know how to make sure my phone does not distract me.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-wave2-mig-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SHealth3_V2),
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SHealth3_V2"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-overall-item1}
# I know how to control how much time I spend on the internet.
result <- create_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SHealth1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-overall-item2}
# I know how to make sure my phone does not distract me.
result <- create_timeline(
  data = data,
  title = "I know how to make sure my phone does not distract me.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SHealth2_V2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-overall-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SHealth3_V2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-age-item1}
# I know how to control how much time I spend on the internet.
result <- create_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-age-item2}
# I know how to make sure my phone does not distract me.
result <- create_timeline(
  data = data,
  title = "I know how to make sure my phone does not distract me.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth2_V2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-age-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth3_V2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-gender-item1}
# I know how to control how much time I spend on the internet.
result <- create_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-gender-item2}
# I know how to make sure my phone does not distract me.
result <- create_timeline(
  data = data,
  title = "I know how to make sure my phone does not distract me.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth2_V2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-gender-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth3_V2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-edu-item1}
# I know how to control how much time I spend on the internet.
result <- create_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-edu-item2}
# I know how to make sure my phone does not distract me.
result <- create_timeline(
  data = data,
  title = "I know how to make sure my phone does not distract me.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth2_V2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-edu-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth3_V2",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dhealth-overtime-mig-item1}
# I know how to control how much time I spend on the internet.
result <- create_timeline(
  data = data,
  title = "I know how to control how much time I spend on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dhealth-overtime-mig-item2}
# I know how to make sure my phone does not distract me.
result <- create_timeline(
  data = data,
  title = "I know how to make sure my phone does not distract me.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth2_V2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r dhealth-overtime-mig-item3}
# I know how I can stop using my phone and computer for a while, if I want to.
result <- create_timeline(
  data = data,
  title = "I know how I can stop using my phone and computer for a while, if I want to.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SHealth3_V2",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph recycle-fill >}} Green Digital


**Sustainable/Green Digital Skills** focus on environmentally conscious technology use: reducing energy consumption, buying sustainable devices, recycling electronics, and understanding the environmental impact of digital activities.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Green Digital results](green_digital.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r green-wave1-overall}
# Sustainable/Green Digital Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SEnv1, SEnv2, SEnv3),
  title = "Sustainable/Green Digital Skills",
  questions = c("SEnv1", "SEnv2", "SEnv3"),
  question_labels = c("I know how to reduce the battery use of a phone or computer.", "I know how I can buy a phone or computer in a 'green' or sustainable way.", "I know how to have a phone or computer recycled."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave1-age-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave1-age-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave1-age-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SEnv3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave1-gender-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave1-gender-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave1-gender-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SEnv3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave1-edu-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave1-edu-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave1-edu-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SEnv3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave1-mig-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave1-mig-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave1-mig-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SEnv3"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r green-wave2-overall}
# Sustainable/Green Digital Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SEnv1, SEnv2, SEnv3),
  title = "Sustainable/Green Digital Skills",
  questions = c("SEnv1", "SEnv2", "SEnv3"),
  question_labels = c("I know how to reduce the battery use of a phone or computer.", "I know how I can buy a phone or computer in a 'green' or sustainable way.", "I know how to have a phone or computer recycled."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave2-age-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave2-age-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave2-age-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SEnv3"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave2-gender-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave2-gender-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave2-gender-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SEnv3"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave2-edu-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave2-edu-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave2-edu-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SEnv3"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-wave2-mig-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SEnv1),
  title = "I know how to reduce the battery use of a phone or computer.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-wave2-mig-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SEnv2),
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-wave2-mig-item3}
# I know how to have a phone or computer recycled.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SEnv3),
  title = "I know how to have a phone or computer recycled.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SEnv3"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-overtime-overall-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SEnv1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-overtime-overall-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SEnv2"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-overtime-overall-item3}
# I know how to have a phone or computer recycled.
result <- create_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SEnv3"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-overtime-age-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-overtime-age-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv2",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-overtime-age-item3}
# I know how to have a phone or computer recycled.
result <- create_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv3",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-overtime-gender-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-overtime-gender-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv2",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-overtime-gender-item3}
# I know how to have a phone or computer recycled.
result <- create_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv3",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-overtime-edu-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-overtime-edu-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv2",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-overtime-edu-item3}
# I know how to have a phone or computer recycled.
result <- create_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv3",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r green-overtime-mig-item1}
# I know how to reduce the battery use of a phone or computer.
result <- create_timeline(
  data = data,
  title = "I know how to reduce the battery use of a phone or computer.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r green-overtime-mig-item2}
# I know how I can buy a phone or computer in a 'green' or sustainable way.
result <- create_timeline(
  data = data,
  title = "I know how I can buy a phone or computer in a 'green' or sustainable way.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv2",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 3


```{r green-overtime-mig-item3}
# I know how to have a phone or computer recycled.
result <- create_timeline(
  data = data,
  title = "I know how to have a phone or computer recycled.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SEnv3",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::

## {{< iconify ph lightbulb-fill >}} Digital Problem Solving


**Digital Problem Solving** measures the ability to find help and solutions for digital challenges: knowing where to get help to improve digital skills and who to turn to when facing technical difficulties.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
create_blockquote("Think about the extent to which each sentence applies to you, if you would have to do this activity now and without help. Please be honest. It is very normal that you never do some things. We'd like to know this. If you don't understand what the question means, please choose 'I don't understand the question.' Do you recognize yourself in the following statements?", preset = "question")
```
[{{< iconify ph cards >}} See all Digital Problem Solving results](digital_problem_solving.html)


::: {.panel-tabset}

### {{< iconify ph number-circle-one-fill >}} Wave 1


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dprob-wave1-overall}
# Digital Problem Solving Skills
result <- create_stackedbars(
  data = data_filtered_984a0efe %>% tidyr::drop_na(SProbl1, SProbl2),
  title = "Digital Problem Solving Skills",
  questions = c("SProbl1", "SProbl2"),
  question_labels = c("I know where or from whom I can get help to improve my digital skills.", "I know where or from whom I can get help if I'm unable to do something on the internet."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-age-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-age-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(AgeGroup, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-gender-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-gender-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(geslacht, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-edu-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-edu-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(Education, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave1-mig-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave1-mig-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_984a0efe %>% tidyr::drop_na(MigrationBackground, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl2"
)

result
```


:::


:::


### {{< iconify ph number-circle-two-fill >}} Wave 2


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


```{r dprob-wave2-overall}
# Digital Problem Solving Skills
result <- create_stackedbars(
  data = data_filtered_4af682fd %>% tidyr::drop_na(SProbl1, SProbl2),
  title = "Digital Problem Solving Skills",
  questions = c("SProbl1", "SProbl2"),
  question_labels = c("I know where or from whom I can get help to improve my digital skills.", "I know where or from whom I can get help if I'm unable to do something on the internet."),
  stacked_type = "percent",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  horizontal = TRUE,
  x_label = "",
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_label = NULL,
  weight_var = "weging_GAMO"
)

result
```


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-age-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-age-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(AgeGroup, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "AgeGroup",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-gender-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-gender-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(geslacht, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "geslacht",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-edu-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-edu-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(Education, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "Education",
  stack_var = "SProbl2"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-wave2-mig-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SProbl1),
  title = "I know where or from whom I can get help to improve my digital skills.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-wave2-mig-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_stackedbar(
  data = data_filtered_4af682fd %>% tidyr::drop_na(MigrationBackground, SProbl2),
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  stacked_type = "percent",
  horizontal = TRUE,
  stack_breaks = c(0.5, 2.5, 3.5, 5.5),
  stack_bin_labels = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  stack_order = c("(Completely) Untrue (1-2)", "Not true and not untrue (3)", "(Completely) True (4-5)"),
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  weight_var = "weging_GAMO",
  x_var = "MigrationBackground",
  stack_var = "SProbl2"
)

result
```


:::


:::


### {{< iconify ph chart-line-fill >}} Over Time


::: {.panel-tabset}

##### {{< iconify ph users-fill >}} Overall


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-overall-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SProbl1"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-overall-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  response_filter_label = "Percentage who answered (Completely) True (4-5)",
  response_filter_combine = TRUE,
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  response_var = "SProbl2"
)

result
```


:::


##### {{< iconify mdi:human-male-male-child >}} Age


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-age-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "AgeGroup"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-age-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "AgeGroup"
)

result
```


:::


##### {{< iconify mdi gender-transgender >}} Gender


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-gender-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "geslacht"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-gender-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "geslacht"
)

result
```


:::


##### {{< iconify ph graduation-cap-fill >}} Education


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-edu-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "Education"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-edu-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "Education"
)

result
```


:::


##### {{< iconify ph globe-hemisphere-east >}} Migration Background


::: {.panel-tabset}

###### {{< iconify ph chat-circle-fill >}} Question 1


```{r dprob-overtime-mig-item1}
# I know where or from whom I can get help to improve my digital skills.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help to improve my digital skills.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl1",
  group_var = "MigrationBackground"
)

result
```


###### {{< iconify ph chat-circle-fill >}} Question 2


```{r dprob-overtime-mig-item2}
# I know where or from whom I can get help if I'm unable to do something on the internet.
result <- create_timeline(
  data = data,
  title = "I know where or from whom I can get help if I'm unable to do something on the internet.",
  time_var = "wave_time_label",
  chart_type = "line",
  response_filter = c(4, 5),
  x_label = "",
  y_label = "Percentage who answered (Completely) True (4-5)",
  color_palette = c("#3D7271", "#E28D50", "#F5D76E", "#C7E6D5", "#0F6B5A", "#BABACD"),
  y_min = 0,
  y_max = 100,
  weight_var = "weging_GAMO",
  response_var = "SProbl2",
  group_var = "MigrationBackground"
)

result
```


:::


:::


:::



```{=html}
<nav class='pagination-nav pagination-bottom' role='navigation' aria-label='Page navigation'>
  <div class='pagination-container'>
    <a href='skills.html' class='pagination-btn pagination-prev' aria-label='Previous page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M12 16L6 10L12 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
    <div class='pagination-info'>
      <span class='pagination-prefix'></span>
      <input type='number' class='pagination-input' id='page-input-bottom' min='1' max='3' value='2' aria-label='Current page'>
      <span class='pagination-separator'> / 3</span>
    </div>
    <a href='skills_p3.html' class='pagination-btn pagination-next' aria-label='Next page'>
      <svg class='pagination-icon' width='18' height='18' viewBox='0 0 20 20' fill='none' xmlns='http://www.w3.org/2000/svg'>
        <path d='M8 16L14 10L8 4' stroke='currentColor' stroke-width='2' stroke-linecap='round' stroke-linejoin='round'/>
      </svg>
    </a>
  </div>
</nav>

<!-- Pagination Navigation Script -->
<script>
(function() {
  const pageUrls = ["skills.html","skills_p2.html","skills_p3.html"];
  const pageInput = document.getElementById('page-input-bottom');
  
  if (pageInput) {
    pageInput.addEventListener('change', function() {
      const pageNum = parseInt(this.value);
      if (pageNum >= 1 && pageNum <= pageUrls.length) {
        window.location.href = pageUrls[pageNum - 1];
      } else {
        this.value = this.getAttribute('value');
      }
    });
    
    pageInput.addEventListener('keypress', function(e) {
      if (e.key === 'Enter') {
        this.blur();
      }
    });
  }
})();
</script>
```

